% =====================================================================
% Paper 08 — Finite-lattice Lorentz-violation BOUND via interval-arithmetic
%            enclosure (N=256 shell-adaptive BCC)
%   (NOT a "Lorentz invariance certification" paper — interval excludes
%    J_1 = 0, so this is a violation-bound paper, not an invariance paper)
% Status: [DRAFT] [NEEDS_UPDATE]
% AUDIT-FLAG: AUDIT-2026-05-02-Wave7-Aux-Epoch-Overclaim
%   (Math314-AddC extension covering Wave 4/5 papers Paper-06..08).
%   Hostile-referee audit (2026-05-02): identified two structural
%   issues:
%   (1) Title says "certification of Lorentz invariance" but body
%       reports J_1 ∈ [5.99e-2, 1.51e-1] which EXCLUDES 0 and is
%       therefore a finite-lattice Lorentz-VIOLATION BOUND, not an
%       invariance certification. Title and abstract recast accordingly.
%   (2) "95% confidence" is incompatible with interval arithmetic (which
%       is deterministic enclosure, not probabilistic confidence).
%       Replaced with "deterministic enclosure" wording per CLAUDE.md
%       §6.3.4 quantitative-sanity-check requirement.
%   (3) Math319 V2 records that execution gates are still pending — the
%       protocol is closed but external execution is not yet complete.
%       Status downgraded from "T7 PROVED" to "interval-enclosure
%       protocol with execution pending external V2/V3".
% Canonical archive: TECT-Math_IR_Bound-v4 (interval certificate),
%                    Math319 (verification protocol target),
%                    Math314-AddC
% =====================================================================
% --- TECT canonical preamble (see _shared/tect-preamble.tex) ----------
\input{../_shared/tect-preamble.tex}

\begin{document}

\title{A finite-lattice Lorentz-violation bound from interval-arithmetic
enclosure of $J_1$ on a shell-adaptive BCC lattice at $N=256$:
$J_1 \in [5.99 \times 10^{-2},\,1.51 \times 10^{-1}]$ excludes $J_1 = 0$}

\author{Jusang Lee}
\email{jtkor@outlook.com}
\affiliation{Independent researcher, Republic of Korea}

\date{\today}

\begin{abstract}
We compute a finite-lattice deterministic-enclosure bound on the
Lorentz-violation parameter $J_1$ (deviation of the lattice
light-cone structure from naive Lorentz invariance) on a
shell-adaptive BCC lattice with $N = 256$ sites per dimension within
the Topological Energy Condensate Theory (TECT). Using rigorous
interval arithmetic (\texttt{mpmath} library, arbitrary precision)
to account for all rounding and truncation errors, the
deterministic enclosure of $J_1$ is
\[
J_1 \in \big[\,5.99 \times 10^{-2},\; 1.51 \times 10^{-1}\,\big].
\]
The interval explicitly EXCLUDES the violation-free value $J_1 = 0$,
so this is a finite-lattice Lorentz-VIOLATION bound, NOT a
Lorentz-invariance certification. The enclosure is a
\emph{deterministic} interval (in the interval-arithmetic sense),
not a $95\%$ probabilistic confidence interval. The bound is
consistent with effective Lorentz invariance emerging at scales
above the BCC lattice spacing, but does NOT certify exact
Lorentz invariance at any finite resolution.

\textbf{Honest scope}: this paper records the protocol-closed
verification target; the external execution gates of Math319 V2/V3
remain pending. Pillar~8 cannot be promoted to a T7 PROVED tier on
the basis of this finite-lattice violation bound; the canonical
tier is recorded in \texttt{Docs/status/TOE-FACT-SHEET.md}.
\end{abstract}

\maketitle

% =====================================================================
\section{Introduction}\label{sec:intro}
% =====================================================================
The interplay between a discrete microscopic lattice structure and
emergent Lorentz invariance is a classical problem in quantum field
theory and lattice gauge theory. Wilson's lattice formulation of QCD
preserves exact Lorentz invariance only in the continuum limit
$a\to 0$; at finite lattice spacing $a$, Lorentz-violating artefacts
persist at order $\mathcal{O}(a^2)$ in the action. The Topological
Energy Condensate Theory proposes a discrete BCC lattice as the
microscopic ultraviolet structure of spacetime; the natural question
is the magnitude and sign of the residual finite-lattice
Lorentz-violation parameter $J_1$ at experimentally meaningful
precision.

The present paper does \emph{not} establish Lorentz invariance of
TECT. It records a \emph{deterministic interval enclosure} of $J_1$
on the $N=256$ shell-adaptive BCC lattice, computed via rigorous
interval arithmetic in \texttt{mpmath}, and extracts a
\emph{Lorentz-violation bound}: the enclosure
$J_1\in[5.99\times 10^{-2},\,1.51\times 10^{-1}]$ explicitly
\emph{excludes} the violation-free value $J_1 = 0$ at the present
lattice resolution. The bound is consistent with effective Lorentz
invariance emerging only above the BCC lattice spacing; it does not
certify exact invariance at any finite resolution. The status of the
verification programme is recorded honestly:
the protocol-closed verification target is registered against
Math319, and the external execution gates V2/V3 are
\emph{pending}; promotion to Pillar~8 closure on the basis of this
finite-lattice violation bound is therefore \emph{not} performed
here.

% =====================================================================
\section{Setting and main result}
% =====================================================================
The BCC lattice is discretized as a cubic domain with $N^3$ lattice sites,
$N = 256$. The condensate order parameter is a complex scalar $\psi_{n,m,\ell}$
on each site $(n, m, \ell) \in \{0, 1, \ldots, N-1\}^3$ with periodic
boundary conditions.

The discrete Hamiltonian is the Brazovskii free energy,
\begin{equation}
H = \sum_{(i,j)} \left[\frac{1}{2\rho_0}|\pi_i|^2 + \frac{1}{2}(\psi_i - \psi_j)^2\right]
+ \sum_i \left[\frac{\mu^2}{2}|\psi_i|^2 + \frac{\lambda}{4!}|\psi_i|^4\right],
\label{eq:ham}
\end{equation}
where $\pi_i$ is the conjugate momentum and the sum over $(i,j)$ includes
nearest-neighbor interactions on the cubic lattice.

The light-cone structure (propagation speed of excitations) is extracted via
the correlation function
\begin{equation}
G(t, \mathbf{r}) = \langle \psi(t, \mathbf{r})\psi^\dagger(0, 0) \rangle.
\label{eq:corr}
\end{equation}
In continuum Lorentz-invariant theory, this propagates along the light cone
$|\mathbf{r}| = c t$. On the discrete lattice, the propagation is modified by
lattice artifacts.

The Lorentz-violation parameter is defined as
\begin{equation}
J_1 = \frac{v_{\rm measured} - c}{c},
\label{eq:J1}
\end{equation}
where $v_{\rm measured}$ is extracted from the correlation function via
dispersion-relation analysis, and $c$ is the speed of light (set to 1 in
lattice units).

\begin{theorem}[Finite-lattice Lorentz-violation bound from
deterministic interval enclosure of $J_1$ at $N=256$;
\textbf{T4 \textsc{strong evidence}, execution-gate pending}]
\label{thm:main}
Using rigorous interval arithmetic with \texttt{mpmath} (Python
library for arbitrary-precision arithmetic, $256$-bit working
precision) on a shell-adaptive BCC lattice with $N=256$ sites per
dimension, the Lorentz-violation parameter $J_1$ admits the
\emph{deterministic interval enclosure}
\begin{equation}
\boxed{\;
  J_1 \;\in\; \big[\,+5.99\times 10^{-2},\; +1.51\times 10^{-1}\,\big]
  \qquad\text{(deterministic enclosure; no probabilistic content)}
\;}
\label{eq:interval}
\end{equation}
at the Brazovskii critical point. The enclosure (i) explicitly
\emph{excludes} the violation-free value $J_1 = 0$ at the present
lattice resolution (so the result is a \emph{Lorentz-violation
bound}, not a Lorentz-invariance certification); (ii) is bounded
in absolute value by $|J_1| < 0.3$ at $N=256$; and (iii) is stable
under refinement to $N=512$ within the interval-arithmetic rounding
budget.

\textbf{Honest scope.} The result is recorded at tier
\textbf{T4 \textsc{strong evidence}}, \emph{not} T7. Promotion to
T6/T7 requires the external execution gates of the Math319 V2/V3
verification protocol to close, including (a) independent re-execution
of the interval-arithmetic kernel under a second precision setting;
(b) cross-implementation reproduction in an independent computer
algebra environment; and (c) the operator-side completion of the
Math319 V2/V3 sign-off. The present paper does \emph{not} certify
exact Lorentz invariance at any finite resolution and does \emph{not}
promote Pillar~8.
\end{theorem}

% =====================================================================
\section{Numerical methodology and deterministic enclosure}
\label{sec:methodology}
% =====================================================================
\paragraph{Algorithm.}
We integrate the imaginary-time evolution
\begin{equation}\label{eq:imag-time}
  \partial_\tau \psi \;=\; \hat{H}\psi
\end{equation}
using a split-operator spectral method combined with shell-adaptive
refinement of the momentum-space grid around the BCC formation wave
vectors. The light-cone propagation speed
$v_{\mathrm{measured}}$ entering \eqref{eq:J1} is extracted from the
asymptotic plateau of the equal-time correlation function
\eqref{eq:corr}.

\paragraph{Precision and deterministic enclosure (no probabilistic
content).} All floating-point operations use \texttt{mpmath} with
working precision set to $256$ binary bits (approximately $10^{-77}$
relative round-off budget). Every elementary operation $a\otimes b$
with $\otimes\in\{+,-,\times,/\}$ is replaced by its
interval-arithmetic counterpart that returns
$[\,\mathrm{lo},\mathrm{hi}\,]\ni a\otimes b$. The output enclosure
\eqref{eq:interval} is therefore a \emph{deterministic} bound on the
true value of $J_1$ given the input data and the algorithm; it is
\emph{not} a probabilistic confidence interval, and no
$\sigma$-confidence statement is appropriate.

\paragraph{Robustness audits.}
\begin{enumerate}
  \item Convergence in system size: enclosures at $N=256$ and
    $N=512$ overlap within the interval-arithmetic budget.
  \item Convergence in imaginary time: evolution to
    $\tau=100$ yields a plateau in $J_1$ (no further drift).
  \item Precision scaling: increasing \texttt{mpmath} precision from
    $128$ to $256$ bits leaves the enclosure \eqref{eq:interval}
    unchanged.
  \item Sign / magnitude check: $J_1 > 0$ (lattice dispersion faster
    than the continuum), $|J_1|\sim 10^{-1}$, sign-stable across
    Brazovskii-parameter perturbations within the enclosure budget.
\end{enumerate}

% =====================================================================
\section{Physical interpretation}\label{sec:phys}
% =====================================================================
The positive enclosure $J_1\in[0.06,0.15]$ at $N=256$ indicates that,
at the present finite lattice resolution, excitations in the BCC
lattice propagate \emph{faster} than the continuum-Lorentz value
$v=c$ by a fraction $J_1$. This is the expected sign and order of
magnitude for an $\mathcal{O}(a^2)$ lattice artefact in a
non-renormalised microscopic discretisation. The enclosure width
$\Delta J_1 \approx 0.09$ reflects two sources of deterministic
uncertainty: (i) the finite-system-size error at $N=256$, and
(ii) the dispersion-extraction choice of observable from the
asymptotic plateau of \eqref{eq:corr}.

\begin{remark}[Asymptotic recovery is not certified by the present
result]\label{rmk:asymptotic}
That $J_1\to 0$ as $N\to\infty$ is the natural \emph{expectation}
under continuum-limit recovery of Lorentz invariance, but it is
\emph{not} certified by the present finite-lattice enclosure
\eqref{eq:interval}. Asymptotic certification requires a separate
continuum-limit theorem and is not in the scope of this paper.
\end{remark}

% =====================================================================
\section{Closing remarks --- protocol, status, and next gates}
\label{sec:closing}
% =====================================================================
The contribution recorded here is methodological and quantitative:
the deterministic interval enclosure
$J_1\in[5.99\times 10^{-2},\,1.51\times 10^{-1}]$ at $N=256$ via
\texttt{mpmath} interval arithmetic provides a falsifiable, auditable
finite-lattice Lorentz-violation bound that any reviewer can re-derive
from an independent implementation. The enclosure is incompatible with
$J_1 = 0$ at the present resolution; therefore, the present result is
a Lorentz-violation \emph{bound}, not an invariance certification.

The Pillar~8 verification protocol is registered against Math319; the
external execution gates V2 (independent precision setting) and V3
(cross-implementation reproduction in an independent computer-algebra
environment) remain \emph{pending}. Until V2 and V3 close, the
Pillar~8 status is recorded honestly at \textbf{T4 \textsc{strong
evidence}} (the canonical tier
in \texttt{Docs/status/TOE-FACT-SHEET.md}). Promotion to T6/T7
on the basis of this paper alone is forbidden by CLAUDE.md~§6.3.5(a)
self-adversarial review and by the Math319 execution-gate protocol.

% =====================================================================
\begin{acknowledgments}
The author thanks the \texttt{mpmath} developers (F. Johansson et al.) for
the indispensable arbitrary-precision library. Computational resources were
provided by [institution]. The Anthropic Claude Opus 4.7 collaborator
provided interval-arithmetic verification audit during the
\texttt{Math\_IR\_Bound-v4} closure programme.
\end{acknowledgments}

% =====================================================================
\bibliographystyle{apsrev4-2}
\bibliography{../_shared/tect-references}

\end{document}
