% =====================================================================
% Paper 11 — Λ cancellation PROGRAMME note (NOT a Pillar-11 closure paper)
% Status: [DRAFT] [NEEDS_UPDATE] [INTERNAL_INCONSISTENCY_REPAIRED]
%   2026-05-02: paper internally inconsistent --- abstract claimed
%   "verification within F-GAP gate |Lambda|/M_P^4 < 10^{-120}", but
%   §Numerical-result body computes Lambda/M_P^4 ~ 10^{-118}..10^{-119},
%   which DOES NOT PASS the stated gate. The paper failed its own
%   pre-registered falsification gate per CLAUDE.md §6.3.4 quantitative
%   sanity check. Abstract and Numerical-result section now flag this
%   internal inconsistency explicitly; Pillar-11 closure claim retracted.
%   Recast as Λ cancellation PROGRAMME note pending verdict-shell
%   resolution.
% AUDIT-FLAG: AUDIT-2026-05-02-Wave7-Aux-Epoch-Overclaim
%   (Math314-AddD extension covering Wave 1/4/5 papers Paper-09..16).
% Compile: pdflatex Paper-11.tex (×2 for refs)
% Canonical source: Math58-v7, Math58-v7-Addendum-A, Math58-v7-AddC,
%                   Math314-AddD
% =====================================================================
% --- TECT canonical preamble (see _shared/tect-preamble.tex) ----------
\input{../_shared/tect-preamble.tex}

\begin{document}

\title{A four-sector cancellation programme note for the cosmological
constant in TECT \\
\normalsize{\textit{(NOT a Pillar-11 closure paper; the present
draft fails its own pre-registered falsification gate as written ---
internal numerical / gate inconsistency flagged for revision.)}}}

\author{Jusang Lee}
\email{jtkor@outlook.com}
\affiliation{Independent researcher, Republic of Korea}

\date{\today}

\begin{abstract}
We outline a candidate four-sector cancellation programme for the
cosmological constant within the Topological Energy Condensate Theory
(TECT). The BCC topological condensate is decomposed into four
candidate independent sectors: (i) the BCC order-parameter
self-interaction energy, (ii) the monopole sector (captured by the
topological Chern class $c_2$), (iii) the Dirac-fermion zero-mode
sector, and (iv) the vortex sector (defect core energy).

\textbf{Internal-inconsistency flag (AUDIT-2026-05-02-Wave7,
Math314-AddD)}: as drafted, this paper claims a near-cancellation
residual $|\sum_i E_i^{\rm vac}| < 10^{-10}\hbar\omega_0$ and
identifies $\Lambda_{\rm TECT} \approx 10^{-120}\,M_{\rm Planck}^4$
in §Mechanism, but the §Numerical-result computation gives
$|\Lambda_{\rm TECT}|/M_{\rm Planck}^4 \sim 10^{-118}\text{ to }10^{-119}$,
which DOES NOT PASS the pre-registered falsification gate
$|\Lambda_{\rm TECT}|/M_{\rm Planck}^4 < 10^{-120}$. The paper
internally fails its own falsification gate. The Pillar-11 closure
claim and the ``T6 PROVED CONDITIONAL'' tier statement are
therefore RETRACTED at the present canonical tier; the document is
recast as a candidate programme note pending (a) repair of the
numerical-vs-gate inconsistency, (b) honest re-statement of the
expected cancellation tier, and (c) verdict-shell scheduling per the
canonical Math3xx framework. The current canonical tier of
Pillar~11 is recorded in \texttt{Docs/status/TOE-FACT-SHEET.md}.
\end{abstract}

\maketitle

% =====================================================================
\section{Introduction}\label{sec:intro}
% =====================================================================
The cosmological constant problem is one of the most acute tensions
in theoretical physics: the observed value
$\Lambda_{\mathrm{obs}} \approx 10^{-120}\,M_{\mathrm{Planck}}^4$
(type-Ia supernovae, CMB, BAO) is many orders of magnitude smaller
than naive quantum-field-theory vacuum-energy estimates.

TECT \emph{proposes} a candidate four-sector cancellation programme
in which the cosmological constant arises as the residual of
near-cancellation among four topologically-distinguished sectors of
the BCC condensate vacuum energy. At the present canonical tier the
programme \emph{conjectures} that the cancellation is enforced by
lattice topological selection rules rather than by a fine-tuning of
couplings; the conjecture is \emph{not} discharged at theorem level
in this paper.

The present paper \emph{records} the four-sector decomposition, the
candidate cancellation condition, the explicit numerical operating
point, and the \emph{pre-registered falsification gate that the
present draft fails as written} (residual is observed at
$10^{-118}$ to $10^{-119}$ in $M_{\mathrm{Planck}}^4$ units, while
the gate requires $< 10^{-120}$). The Pillar~11 closure claim is
\emph{not} made here; the document is a programme note pending (i)
repair of the numerical-vs-gate inconsistency, (ii) honest
re-statement of the expected cancellation tier, and (iii)
verdict-shell scheduling per the canonical Math3xx framework.

% =====================================================================
\section{The four-sector decomposition}
% =====================================================================

The TECT vacuum energy (at one-loop order) decomposes into four sectors:

\subsection{Sector 1: BCC order-parameter self-interaction}

The Brazovskii free energy yields a one-loop effective potential:
\begin{equation}
E_1^{\rm vac} = \frac{1}{2} \int \frac{d^3\mathbf{k}}{(2\pi)^3} \omega_\mathbf{k},
\end{equation}
where $\omega_\mathbf{k}$ is the one-particle dispersion of the BCC order parameter.
In the broken phase, $\omega_\mathbf{k} = \sqrt{m^{*2} + (k/m^*)^2}$ (with $m^*$
the mass gap from Pillar 1). The integral is regularized via dimensional
regularization and renormalized mass (Math58-v3 framework):
\begin{equation}
E_1^{\rm vac} \sim \lambda^{1/3} M_X^4 + \text{(log terms)}.
\end{equation}

\subsection{Sector 2: Monopole sector (topological Chern class)}

The BCC lattice admits topological monopole excitations, whose vacuum contribution
arises from the loop integral over monopole propagation. The Chern-class index
$c_2(E)$ of the monopole gauge bundle constrains the spectrum. Under the gauge
choice $c_1 = 0$ (Math191), the Chern number becomes:
\begin{equation}
c_2(E) = \int_X c_2 = -40 \quad \text{(on } \Sigma_0 \text{)}.
\end{equation}
The vacuum energy from this sector is:
\begin{equation}
E_2^{\rm vac} = -\gamma^{2/3} M_X^4 + \text{(log terms)},
\end{equation}
with the opposite sign from Sector 1.

\subsection{Sector 3: Dirac-fermion zero-mode sector}

The protected chiral zero mode (Pillar 5, via index theorem) contributes a
fermionic zero-point energy. Since it is a single zero mode per BCC unit cell,
the total fermionic contribution is:
\begin{equation}
E_3^{\rm vac} = \frac{1}{2} \hbar v_F q_0 \quad \text{(one Dirac zero mode per cell)}.
\end{equation}
In natural units and volume-normalized, this becomes:
\begin{equation}
E_3^{\rm vac} = \alpha_D M_X^4 + \text{(log terms)},
\end{equation}
with $\alpha_D$ a dimensionless coefficient depending on the Fermi velocity.

\subsection{Sector 4: Vortex sector (defect core energy)}

Topological defects (vortices) in the BCC order parameter carry core energy.
The vacuum loop integral over vortex pairs yields:
\begin{equation}
E_4^{\rm vac} = -(\alpha_1 \lambda^{1/3} + \alpha_2 \gamma^{2/3}) M_X^4 + \text{(log terms)},
\end{equation}
with $\alpha_1, \alpha_2$ dimensionless coefficients.

% =====================================================================
\section{The candidate cancellation condition (programme statement,
not theorem)}\label{sec:cancellation}
% =====================================================================

The four-sector sum reads
\begin{equation}\label{eq:Etotal}
  E_{\mathrm{vac}}^{\mathrm{total}}
  \;=\; \big(E_1
    - \alpha_1 \lambda^{1/3}
    + \alpha_D
    - \gamma^{2/3}\,E_2\big)\,M_X^4
  + \text{(log)}.
\end{equation}
The candidate near-cancellation condition, at the tree level before
renormalisation, is
\begin{equation}\label{eq:cancel-cond}
  1 \;-\; \alpha_1 \lambda^{1/3} \;+\; \alpha_D \;-\; \gamma^{2/3}
  \;\approx\; 0.
\end{equation}

\begin{remark}[The cancellation \eqref{eq:cancel-cond} is a candidate
programme statement, NOT a theorem at the present canonical
tier]\label{rmk:cancel-not-theorem}
The earlier draft of this paper asserted that
\eqref{eq:cancel-cond} is an ``automatic consequence'' of the
topological selection rules and that Math58-v7 ``proves'' the
coefficients $\{\alpha_1,\alpha_2,\alpha_D\}$ are forced by the
lattice geometry and Dirac-index invariants. That assertion is
\emph{programme}, not \emph{theorem}. Even within Math58-v7, the
coefficient identification is performed under the load-bearing
hypotheses (H1)--(H3) listed in \S\ref{sec:hypotheses-H}, and the
matching of the resulting near-cancellation residual to
$\Lambda_{\mathrm{obs}}$ requires the verdict-shell scheduling of
the canonical Math3xx framework. At the present canonical tier
\eqref{eq:cancel-cond} is a \textbf{T2 \textsc{conjecture}}, not a
\textbf{T7 \textsc{proved}} theorem; the corresponding Pillar~11
status is \textbf{T4 \textsc{strong evidence}}.
\end{remark}

If \eqref{eq:cancel-cond} held exactly, the residual vacuum energy
would arise from one-loop corrections to the cancellation:
\begin{equation}\label{eq:Eres}
  E_{\mathrm{vac}}^{\mathrm{residual}}
  \;\sim\; \hbar\,\frac{\lambda^2}{16\pi^2}\,M_X^4
  + \text{(higher-order)}.
\end{equation}
At the Math58-v7 operating point with $\lambda \sim 10^{-3}$ at the
renormalisation scale, \eqref{eq:Eres} estimates
\begin{equation}\label{eq:Eres-num}
  E_{\mathrm{vac}}^{\mathrm{residual}}
  \;\sim\; 10^{-10}\,\hbar\,M_X^4.
\end{equation}
The estimate \eqref{eq:Eres-num} is a programme-level scaling
estimate; it is \emph{not} a constant-bound theorem.

% =====================================================================
\section{Candidate connection to the observed cosmological constant
(target value, NOT verified prediction)}\label{sec:hypotheses-H}
% =====================================================================

The TECT vacuum energy would be related to the cosmological constant
via the Einstein equation,
\begin{equation}\label{eq:einstein-Lambda}
  \Lambda_{\mathrm{TECT}}
  \;=\; \frac{8\pi G}{3}\,\rho_{\mathrm{vac}}
  \;=\; \frac{8\pi G}{3}\,
        \frac{E_{\mathrm{vac}}^{\mathrm{residual}}}{V}.
\end{equation}
Substituting \eqref{eq:Eres-num} and the TECT-derived constants
$G, c, a_{\mathrm{BCC}}$ from the prior pillars yields the
\emph{target value}
\begin{equation}\label{eq:Lambda-target}
  \Lambda_{\mathrm{TECT}}^{\mathrm{target}}
  \;\approx\; 10^{-120}\,M_{\mathrm{Planck}}^4,
\end{equation}
which would match the observed value
($\Omega_\Lambda \approx 0.73$). The actual numerical evaluation of
the four-sector residual at the Math58-v7 operating point gives
$|\Lambda_{\mathrm{TECT}}|/M_{\mathrm{Planck}}^4 \sim 10^{-118}$ to
$10^{-119}$ (\S\ref{sec:numerics}), which differs from
\eqref{eq:Lambda-target} by $1$--$2$ orders of magnitude. The
target--evaluation gap is the canonical falsification-gate failure
recorded in Remark~\ref{rmk:gate-fail}.

The candidate programme rests on three explicit load-bearing
hypotheses.
\begin{enumerate}
  \item \textbf{(H1) Chern-class exactness (Math191).} The gauge
    choice $c_1 = 0$ leaves the Chern number $c_2 = -40$ invariant
    and the cancellation \emph{schematic} as written. Conditional on
    the mathematical exactness of the Chern-class formula on the
    BCC lattice.
  \item \textbf{(H2) Vortex topology stability (Math58-v4/v5).}
    Topological defects on the BCC lattice preserve their winding
    numbers under small perturbations. Topological property; binary.
  \item \textbf{(H3) Lattice--continuum matching (Math58-v6/v7).}
    The continuum limit of the four-sector loop integrals matches
    the discrete lattice calculation to within $\sim 10^{-12}$
    relative error. Conditional on the discretisation scheme;
    Math58-v8 tests the continuum limit.
\end{enumerate}

% =====================================================================
\section{Numerical evaluation and the
falsification-gate failure as written}\label{sec:numerics}
% =====================================================================

Math58-v7 §Q5 executes a numerical evaluation of the four-sector
cancellation \eqref{eq:cancel-cond}. The operating point is
\begin{equation}\label{eq:opt-pt}
  (\lambda,\gamma,Y,q_0,a_{\mathrm{BCC}})
  \;=\; (-0.0394,-0.0188,280.2,14.32,4\sqrt{\pi}\,\ell_P).
\end{equation}
The evaluated residual is
\begin{equation}\label{eq:Lambda-num}
  \frac{|\Lambda_{\mathrm{TECT}}|}{M_{\mathrm{Planck}}^4}
  \;\approx\; 10^{-118}\;\text{ to }\;10^{-119}.
\end{equation}

\paragraph{Pre-registered falsification gate.}
\begin{equation}\label{eq:fgate}
  \frac{|\Lambda_{\mathrm{TECT}}|}{M_{\mathrm{Planck}}^4}
  \;<\; 10^{-120}.
\end{equation}

\begin{remark}[The present draft FAILS the falsification gate
\eqref{eq:fgate} as written]\label{rmk:gate-fail}
\eqref{eq:Lambda-num} is in the range $10^{-118}$ to $10^{-119}$,
which exceeds the gate threshold $10^{-120}$ of \eqref{eq:fgate} by
$1$--$2$ orders of magnitude. The pre-registered falsification gate
is therefore \emph{not passed} by the present draft. This is a
self-failure recorded honestly per CLAUDE.md~§6.3.4 quantitative
sanity check. Pillar~11 \emph{cannot} be promoted to T6 on the
basis of this paper; the canonical tier reverts to (or remains at)
\textbf{T4 \textsc{strong evidence}} with this gate-failure
recorded as part of the verdict-shell scheduling.
\end{remark}

The 2026-06-01 verdict scheduled in
\texttt{PHASE\_8\_TO\_14\_PLAN.md} §11 must therefore consume the
gate-failure as a condition of promotion: either (a) the operating
point \eqref{eq:opt-pt} or the cancellation coefficient identification
of \S\ref{sec:cancellation} must be revised to drive the residual
below $10^{-120}$, or (b) the gate \eqref{eq:fgate} itself must be
re-registered at a different threshold reflecting the canonical
near-cancellation expectation. Until either option is exercised and
audited, Pillar~11 status remains \textbf{T4 \textsc{strong
evidence}}.

% =====================================================================
\section{Conclusion}\label{sec:conclusion}
% =====================================================================

The TECT four-sector cancellation programme of \S\ref{sec:cancellation}
is a candidate mechanism for the smallness of the cosmological
constant within the BCC condensate. It is recorded here as a
\textbf{T2 \textsc{conjecture}} on the cancellation, supported by an
order-of-magnitude estimate \eqref{eq:Eres-num} of the residual. The
target value \eqref{eq:Lambda-target} matches the observed value
$\Lambda_{\mathrm{obs}}$ in order of magnitude, but the actual
numerical evaluation \eqref{eq:Lambda-num} differs from the
pre-registered falsification gate \eqref{eq:fgate} by one to two
orders of magnitude. The Pillar~11 canonical tier remains
\textbf{T4 \textsc{strong evidence}}; promotion to T6 \textsc{proved
conditional} is contingent on (a) the gate-failure repair tracked in
Remark~\ref{rmk:gate-fail}, and (b) the verdict-shell scheduling per
the canonical Math3xx framework. This document is not a Pillar~11
closure paper; it is a programme note in which the pre-registered
gate is honestly reported as failed.

\begin{thebibliography}{99}

\bibitem{TECTRepo}
J. Lee, \textit{Topological Energy Condensate Theory (TECT) Repository},
\texttt{https://github.com/...} (2026).

\bibitem{Math58v7}
J. Lee, ``Pillar 11 Dirac-sector tightening,''
\textit{Math58-v7}, 2026-04-25.

\bibitem{Math58v7AddC}
J. Lee, ``Pillar 11 promotion to PROVED CONDITIONAL,''
\textit{Math58-v7-AddC}, 2026-04-25.

\bibitem{Math191}
J. Lee, ``Gauge choice $c_1 = 0$ canonical form,''
\textit{Math191}, 2026-04-25.

\bibitem{Math58v7AddA}
J. Lee, ``PV scheme adversarial audit,''
\textit{Math58-v7-Addendum-A}, 2026-04-25.

\bibitem{Math58v8}
J. Lee, ``Pillar 11 continuum-limit closure,''
\textit{Math58-v8}, 2026-04-26.

\end{thebibliography}

\end{document}
