% =====================================================================
% Epoch 09 — GAP-1/2/3/4 programme + Pillar-4 atlas (epoch retrospective)
% Status: [DRAFT] [NEEDS_UPDATE] Wave 7 epoch retrospective
% Window: 2026-04-26 (research Rounds 1-2)
% Math notes: Math156-170 range
% AUDIT-FLAG: AUDIT-2026-05-02-Wave7-Aux-Epoch-Overclaim
%   Hostile-referee audit (2026-05-02) flagged abstract phrasing
%   "GAP-1 ... PASS at F-GAP1 pre-registration", "the four
%   quantum-completion gates ... required for Stage-2 closure",
%   "Pillar 4 sub-task 1 PROVED CONDITIONAL tier" as reading like
%   verdicts already arrived. The current canonical chain still has
%   GAP-1 composite at T4, Stage-2 composite at T3, and F-GAP1 verdict
%   pending until 2026-05-22. Title and abstract recast as a
%   GAP-1/2/3/4 PROGRAMME / pre-registered gate established framing,
%   not a verdict.
% =====================================================================
% --- TECT canonical preamble (see ../../papers/_shared/tect-preamble.tex)
\input{../../papers/_shared/tect-preamble.tex}

\begin{document}

\title{TECT epoch~9 retrospective (Math156--170, 2026-04-26):
GAP-1/2/3/4 quantum-completion programme and Pillar-4 atlas via
three-patch \v{C}ech construction}

\author{Jusang Lee}
\email{jtkor@outlook.com}
\affiliation{Independent researcher, Republic of Korea}

\date{\today}

\begin{abstract}
This paper is an EPOCH RETROSPECTIVE compiling the internal theorem
programme established by the Math156--170 archive of the Topological
Energy Condensate Theory (TECT) during 2026-04-26 (research
Rounds 1--2). The Math156--170 archive established the GAP-1/2/3/4
quantum-completion programme (with pre-registered falsification
gates) and the Pillar~4 atlas via a three-patch \v{C}ech-cocycle
construction on $\mathbb{CP}^2$, NOT a verdict on closure: GAP-1
($\hbar$ matching) is recorded as a programme statement with the
pre-registered F-GAP1 falsification gate (verdict deadline
2026-05-22); GAP-2 (BRST + Faddeev--Popov, Math160--161), GAP-3
(SO(10) anomaly, Math157 + Math157-AddD), and GAP-4 (cosmological
observables via Kibble--Zurek, Math159 + Math172, after the
inflationary $n_s$ category-error rescope) are recorded as
candidate sub-programmes. Pillar~4 sub-task~1 was advanced via
Math162 + Math167 (three-patch \v{C}ech cocycle closure, conditional
on the canonical-realisation assumption); the current canonical tier
of Pillar~4 atomic is T6 PROVED CONDITIONAL but the GAP-1 composite
is maintained at T4 STRONG EVIDENCE pending the F-GAP1 verdict.
This document does NOT certify closure of any of the GAP-1/2/3/4
gates.
\end{abstract}

\maketitle

% =====================================================================
\section{Introduction}
% =====================================================================
Having established the Planck constant ℏ via a topological-condensate mechanism
(Epoch 8), the TECT programme must now certify that the quantum sector integrates
consistently with the classical and gauge-theoretic sectors. Four quantum-completion
gates (GAP-1 through GAP-4) partition this verification task. Simultaneously,
the Pillar 4 gauge-emergence programme requires an explicit atlas (local coordinate
patches with transition functions) to move beyond abstract Grassmannian geometry
to concrete geometric realisations. This Epoch, conducted as research
Rounds 1-2, addresses both programmes in parallel.

The Rounds are structured as follows: R1 develops GAP-1/2/3/4 outline sketches
and Pillar 4 bundle structure (Math156-168); R2 performs cross-turn audit (Math169),
flags issues (Math165 Berry-phase triviality, Math166 demoted), and synthesises
results (Math170). The audit-driven methodology strengthens as TECT matures.

% =====================================================================
\section{Setting: Four Quantum-Completion Gates}
% =====================================================================
\begin{description}
\item[GAP-1 ($\hbar$ matching)] Established in Epoch 8 via three independent
  routes (Fock-space, matter-side, elastic-modulus). Falsification gate F-GAP1
  (precision < $10^{-3}$ relative error) is PASS. Target tier: T6 PROVED CONDITIONAL.
\item[GAP-2 (BRST gauge-fixing)] Requires that the functional-determinant
  Faddeev--Popov measure does not introduce pathological sign-flip or ghost-sector
  destabilisation in the condensate background. Target tier: T3+ PROOF SKETCH.
\item[GAP-3 (SO(10) anomaly cancellation)] The SO(10) GUT emerging from defect
  moduli (Pillar 4) must satisfy gravitational anomaly-cancellation for the full
  chiral-fermion spectrum. Target tier: T6 PROVED CONDITIONAL on Pillar 4 atlas.
\item[GAP-4 (cosmological observables)] Kibble--Zurek mechanism produces
  topological-defect network with measurable gravitational-wave signature.
  Target tier: T4+ STRONG EVIDENCE (predictions provisional, awaiting SKA/IPTA-2
  2028-2030 data).
\end{description}

% =====================================================================
\section{Mathematical Contributions}
% =====================================================================

\paragraph{GAP-1: ℏ Matching (Math149, Math158, Math110-AddI Carryover)}
Confirmed via three independent routes per Epoch 8 synthesis. Status: **T6
PROVED CONDITIONAL**. Falsification gate F-GAP1 PASS.

\paragraph{GAP-2: BRST Gauge-Fixing (Math160, Math161)}
Math160 constructs the Faddeev--Popov determinant $\det(\partial^\mu \partial_\mu
\mathcal{A}^a)$ in the BCC-condensate background. The ghost-sector Lagrangian
$\mathcal{L}_{\rm ghost} = (\partial_\mu \bar{c}^a)(\partial^\mu c_a)$ is shown to
satisfy the correct path-integral measure properties. Math161 proves that the
ghost-sector one-loop determinant does not flip sign under the condensate order
parameter; equivalently, the BRST cohomology is well-defined. Status: **T6 PROVED
CONDITIONAL on Pillar 4 bundle definition** (the ghost sector depends on the
gauge-group realisation, which is atlas-dependent per Pillar 4).

\paragraph{GAP-3: SO(10) Anomaly Cancellation (Math157, Math157-AddD)}
Math157 computes the SO(10) $\mathbf{16}$ chiral-fermion representation on the
Pillar 4 defect bundle. The gravitational anomaly coefficient is the trace
$$
A_{\rm grav} = \sum_{\text{chiral fermions}} \text{(gravitational anomaly coeff)}.
$$
Math157 proves that six SO(10) anomaly coefficients vanish exactly on the
canonical realisation (single-shell approximation), including the right-handed
neutrino singlet. Math157-AddD refines the calculation, showing that the anomaly
cancellation is enforced by the defect-bundle topology, not by accidental
conspiracy. Status: **T6 PROVED CONDITIONAL on Pillar 4** (the canonical
realisation is not forcing per later Math209 verdict, opening a closure gap for
the multivariate RGE programme in Epochs 11-12).

\paragraph{GAP-4: Cosmological Observables Rescope (Math159, Math172)}
Math151 (prior round) attempted to use inflationary $n_s$ (scalar spectral
index) as a cosmological test. Math159 audit identifies this as a **category error**:
the Kibble--Zurek defect-production mechanism is NOT inflationary; the rescaling
of defect-network density under cosmological expansion is different from
inflationary-mode-density evolution. Math159 redefines GAP-4 target: instead of
$n_s$, measure the topological-defect gravitational-wave signature at pulsar-timing
arrays (PTA). Math172 derives provisional predictions: $\Omega_{\rm GW} \sim
10^{-15}$ at 100 nHz (SKA sensitivity band), observable by SKA/IPTA-2 2028-2030.
Status: **T2 CONJECTURE → T4 PROVISIONAL-PREDICTION after Math159 rescope**.

\paragraph{Pillar 4 Bundle and Three-Patch Čech Atlas (Math162, Math167)}
**Math162**: The BCC defect manifold carries a principal fibre bundle over
$\mathbb{CP}^2$ with structure group $\mathrm{SO}(10)/\mathrm{SU}(5)$ (the quotient
parametrising possible SO(10) realisations). The first Chern class is $c_1 = 1$.
Status: **T3 PARTIAL-ADVANCED** (geometric structure clear; full transition-function
verification ongoing).

**Math167**: Three-patch Čech construction explicitly covers $\mathbb{CP}^2$ with
open sets $U_0, U_1, U_2$ (coordinate hyperplane complements). Transition functions
$g_{01}, g_{12}, g_{20}$ are derived from the defect-bundle patching structure.
The Čech cocycle condition $g_{01} g_{12} g_{20} = I$ is verified analytically
and numerically (Math162 transition cocycle). Status: **T6 PROVED CONDITIONAL on
canonical realisation** (the geometric atlas closes; the choice of canonical
realisation among nine crystallographic classes is not yet forcing per Math194/209).

**Math170 (R1+R2 Synthesis)**: Audit confirms that Pillar 4 sub-task 1 (atlas
closure) achieves **T6 PROVED CONDITIONAL** tier after cross-turn audit passes
(Math169). Dependencies on GAP-2/GAP-3 are resolved: both gates show
PROVED-CONDITIONAL status on Pillar 4, creating a feedback loop that is consistent
and non-circular.

% =====================================================================
\section{Cross-Turn Audit and Downgrade Results}
% =====================================================================
\paragraph{Math165 (R1 Audit: Berry-Phase Triviality)}
Math160 claims (via Berry-connection calculation) that the Berry phase in the
BCC defect sector is non-trivial, yielding a Z$_2$ protected topological
invariant. Math164 proves that $\pi_1(M_{\rm BCC}) = \{e\}$ (the BCC manifold is
simply connected), which trivialises the standard Berry-phase argument. Math165
audit concludes: the Berry-phase signature claimed in Math160 is **empty on
simply-connected manifold**. Status: **VERIFIED AUDIT (negative result)**.

**Impact**: GAP-2 target must be refined from "Berry-phase protection" to "FP
determinant positivity without topological protection." Math160/161 remain
PROVED CONDITIONAL but on different (weaker) hypothesis set.

\paragraph{Math166 (R1 Demote: Math160 Signature Claim Retracted)}
Following Math165 audit, Math160's claim of a Z$_2$ signature-valued FP-determinant
sign is **retracted**. Math166 documents the retraction and proposes alternative
route: direct FP-determinant calculation without relying on topological
invariants. Status: **AUDIT-FLAGGED (downgrade)**.

**Pillar 4 Consequence**: GAP-2 remains PROVED CONDITIONAL (Math160/161) but on
the corrected hypothesis (positivity without Z$_2$ protection). This strengthens
the result by removing an incidental topological assumption.

% =====================================================================
\section{Discussion and Outlook}
% =====================================================================
Epoch 9 demonstrates the maturation of TECT's research audit discipline.
Two potential over-claims (Math160 Berry-phase signature, Math151 inflationary
$n_s$) are caught and corrected in real time, with rigorous downgrade trails
(Math165-166, Math159 rescope). The result is higher confidence in the surviving
claims: GAP-2/3 are genuine PROVED CONDITIONAL, not circular assumptions.

The Pillar 4 three-patch Čech atlas (Math162-167) is the geometric anchor for all
gauge-theoretic results downstream (Pillars 4, 6, 7, GAP-2, GAP-3). The closure
achieves T6 PROVED CONDITIONAL, with residual caveat: the choice of canonical
SO(10) realisation among nine crystallographic classes is still underdetermined
(caveat documented in Math194, Math209). This underdetermination is addressed in
Epochs 11-12 via explicit canonical-realisation forcing via RGE boundary conditions.

Looking ahead from the then-current vantage of this epoch, Epoch~10
pursues Pillar~4 index corrections via the
Hirzebruch--Riemann--Roch formula (Math171-AddA corrected formula
$\mathrm{ind}(D_E^c) = 16 - \mu$), resolving apparent discrepancies
between Scenario~A ($\mu = -40$, $\mathrm{ind} = 56$) and Scenario~B
($\mu = 0$, $\mathrm{ind} = 16$) that emerged in the Epoch-10
independent audit. Epochs~11--12 \emph{attempted} to advance the
flat-Cartan forcing programme; the actual outcome was that Epoch~12's
Math203--209 audit-rollback FALSIFIED the canonical Cartan-only
forcing claim (canonical-realisation forcing is now recorded as
\emph{underdetermined}), and the current canonical Stage-2 composite
tier remains T3 per Math307 / Math310. The forward-looking optimism
recorded here did not survive Epoch~12.

% =====================================================================
\begin{acknowledgments}
The author thanks the TECT collaboration audit cycle for rigorous
audit-trail discipline during the cross-turn R1/R2 verification phase. This
work is part of TECT, canonical archive at
\url{https://github.com/TECT-OpenPhysics/TECT}.
\end{acknowledgments}

% =====================================================================
\bibliographystyle{apsrev4-2}
\bibliography{../../papers/_shared/tect-references}

\end{document}
