% =====================================================================
% Paper TI-3 — A2 axiom WEAKENING / RECLASSIFICATION (NOT elimination)
% Status: [DRAFT] [NEEDS_UPDATE] — Wave 2 top-impact
% AUDIT-FLAG: AUDIT-2026-05-02-Wave7-Aux-Epoch-Overclaim
%   (Math314-AddB extension covering the four Top-impact TI-1..4 papers).
%   Hostile-referee audit (2026-05-02) identified three FATAL defects
%   in the original argument:
%   (1) The dissipative TDGL flow is NOT time-reversible; the original
%       Step 2 "backward extrapolation by time-reversibility" cannot
%       support a unique initial-condition theorem.
%   (2) "Symmetric phase ⟨Ψ⟩=0 = unique microscopic boundary state" is
%       a category error: ⟨Ψ⟩=0 is an ensemble/phase statement, not a
%       single microscopic Cauchy datum at t=-∞.
%   (3) "Reduces from 3 to 2" misrepresents the count: total premises
%       remain 3; the actual change is RECLASSIFICATION
%       (2 internal axioms + 1 external boundary input).
%   The theorem is downgraded from "A2 elimination" to "A2 weakening
%   / reclassification" — A2 need not be imposed as an independent
%   microscopic dynamical law; it can be replaced by the weaker
%   requirement that the early-time state belongs to the symmetric
%   high-temperature phase class. Title and abstract recast accordingly.
% Compile: pdflatex Paper-TI-3.tex (×2 for refs)
% Canonical archive: Math195, Math314-AddB
% =====================================================================
% --- TECT canonical preamble (see ../../papers/_shared/tect-preamble.tex)
\input{../../papers/_shared/tect-preamble.tex}

\begin{document}

\title{On the reclassification of A2 in TECT: from an independent
ultra-high-energy postulate to a high-temperature symmetric-phase
boundary class}

\author{Jusang Lee}
\email{jtkor@outlook.com}
\affiliation{Independent researcher, Republic of Korea}

\date{\today}

\begin{abstract}
We analyse the logical role of axiom A2 (an ultra-high-energy
isotropic initial state at $t = -\infty$) in the foundations of
topological energy condensate theory and show that A2 admits a
\emph{weakening / reclassification}, NOT an elimination. Given a
Brazovskii free-energy functional A0, dissipative TDGL kinetics A1,
and an externally supplied cosmological cooling history $T(t)$ with
an early-time regime $T \gg T_c$, the original axiom A2 need not be
imposed as an independent microscopic dynamical law. It can be
replaced by the weaker requirement that the early-time state belongs
to the symmetric high-temperature phase \emph{class}, characterised
at the coarse-grained level by $\langle \Psi \rangle = 0$ and full
unbroken spatial / internal symmetry. Two structural caveats prevent
a stronger ``elimination'' claim: (a) the dissipative TDGL flow is
NOT time-reversible, so a unique microscopic backward extrapolation
to $t = -\infty$ cannot be invoked; (b) the ensemble-level
phase-class statement $\langle \Psi \rangle = 0$ does not single out a
unique microscopic Cauchy datum. The total number of premises is
preserved (3 = 2 internal axioms + 1 external boundary input); the
reclassification moves $T(t)$ from an internal TECT axiom to an
external cosmological input rather than eliminating it.
\end{abstract}

\maketitle

% =====================================================================
\section{Introduction}
% =====================================================================
In constructing a candidate theory-of-everything framework, a useful
structural question is: how many genuinely independent internal
assumptions does the theory require, and which of those assumptions
are properly internal as opposed to being inherited from external
boundary data? A theory with fewer genuinely independent internal
assumptions is, all else equal, structurally more economical, in the
sense that fewer postulates are subject to falsification at the level
of the theory itself.

TECT originally posited three independent axioms (A0, A1, A2). The
present work explores whether one of these—the ultra-high-energy initial
state (A2)—can be derived from the other two in the presence of
cosmological inputs. If so, the logical structure of TECT simplifies
from a "3-axiom framework" to a "2-axiom + 1-boundary-condition
framework," moving one axiom from the theory itself to the specification
of the problem domain.

% =====================================================================
\section{Setting and main result}
% =====================================================================
\subsection{The three TECT axioms}

\begin{enumerate}
\item {\bf A0 (Brazovskii functional)}: The primordial BCC condensate is
  governed by a Brazovskii-type free-energy functional $\mathcal{F}[\Psi]$
  with locked parameters $(\mu^2, \lambda, \gamma)$ and shell radius $q_0$.
  This is the dynamical foundation: it specifies the equations of motion
  via TDGL.

\item {\bf A1 (TDGL kinetics)}: The time evolution is governed by
  time-dependent Ginzburg–Landau (TDGL) Model-A kinetics:
  \begin{equation}
  \partial_t \Psi = -\Gamma \frac{\delta \mathcal{F}}{\delta \Psi^*} + \xi(t),
  \end{equation}
  where $\Gamma$ is the Onsager relaxation coefficient and $\xi$ is
  thermal noise (possibly suppressed in the zero-temperature limit).

\item {\bf A2 (Ultra-high-energy isotropic initial state)}: At $t = -\infty$
  (or $t \to -\infty$), the order parameter is symmetric and isotropic,
  $\langle \Psi \rangle = 0$, with energy density set by the high-temperature
  regime $T \gg T_c$. Full $O(3) \rtimes \mathbb{R}^3 \times U(1)$ symmetry.
\end{enumerate}

\subsection{Main theorem}

\begin{theorem}[A2 weakening / reclassification]
\label{thm:main}
Assume:
\begin{enumerate}
\item A Brazovskii-type free-energy functional $\mathcal{F}[\Psi; T]$
  with locked parameters $(\mu^2, \lambda, \gamma, q_0)$ depending
  smoothly on temperature $T$ (axiom A0).
\item Dissipative TDGL evolution toward lower free energy
  $\partial_t \Psi = -\Gamma\, \delta \mathcal{F} / \delta \Psi^*$
  (axiom A1).
\item An externally supplied cosmological cooling history $T(t)$ with
  an early-time regime $T \gg T_c$ (boundary input, NOT an internal
  TECT axiom).
\end{enumerate}

Then the original axiom A2 (independent ultra-high-energy isotropic
initial state) need NOT be imposed as an independent microscopic
dynamical law. It can be replaced by the weaker requirement that the
early-time state belongs to the symmetric high-temperature phase
\emph{class}, characterised at the coarse-grained level by
\[
\langle \Psi \rangle \;=\; 0
\quad \text{and} \quad
\text{full unbroken spatial / internal symmetry.}
\]
The total premise count is preserved as $3 = 2_{\rm internal} +
1_{\rm boundary}$; A2 itself is removed from the internal-axiom list,
and $T(t)$ is moved from an implicit internal assumption to an
explicit external boundary input.
\end{theorem}

\begin{remark}[Why this is weakening, not elimination]
\label{rem:weak-not-elim}
Two structural obstacles prevent a stronger ``elimination'' claim. (i)
The dissipative TDGL flow $\partial_t \Psi = -\Gamma\,\delta
\mathcal{F} / \delta \Psi^*$ is NOT time-reversible; a backward
extrapolation from a late-time observation to a unique microscopic
Cauchy datum at $t = -\infty$ is not available. (ii) The phase-class
statement $\langle \Psi \rangle = 0$ is an ensemble / coarse-grained
characterisation, not a single microscopic configuration; it admits
many distinct microscopic Cauchy data compatible with the same
phase-class behaviour. The theorem above therefore provides a
\emph{reclassification} of A2 (from an independent internal axiom to a
phase-class boundary requirement consistent with A0 + A1 + $T(t)$),
not a derivation of a unique microscopic initial state.
\end{remark}

\section{Proof sketch}
% =====================================================================

\paragraph{Step 1 (Cauchy-problem formulation).}
The TDGL dynamics defines a Cauchy problem: given an initial state
$\Psi(t_0)$ at some time $t_0$, the equation
\begin{equation}
\partial_t \Psi = -\Gamma \frac{\delta \mathcal{F}}{\delta \Psi^*}
\end{equation}
(ignoring noise in the zero-temperature limit) uniquely determines
$\Psi(t)$ for all $t > t_0$.

\paragraph{Step 2 (Forward consistency, NOT backward time-reversibility).}
The dissipative TDGL flow is NOT time-reversible (cf.\
Remark~\ref{rem:weak-not-elim}); we therefore do NOT attempt a
microscopic backward extrapolation from a late-time observation. The
relevant statement is forward consistency: under TDGL evolution,
states starting in the symmetric high-temperature phase
$\langle \Psi \rangle = 0$ at $t \to -\infty$ flow into the broken-phase
BCC basin only after the temperature crosses $T_c$. Backward uniqueness
of the microscopic Cauchy datum is NOT used.

\paragraph{Step 3 (High-temperature limit).}
At $t = -\infty$, the early universe was hot: $T \gg T_c$. In the
high-temperature regime, the free energy $\mathcal{F}[\Psi]$ is dominated
by the quadratic term $\sim \mu^2 |\Psi|^2$ with $\mu^2 > 0$ (symmetric phase).
The lowest-energy state is $\Psi = 0$ (isotropic vacuum). This is not a
postulate—it is a thermodynamic consequence of the free-energy form at
high $T$.

As the universe cools ($T(t)$ decreases), the parameters $\mu^2(T)$ and
$\lambda(T)$ evolve. At some critical temperature $T_c$, a phase transition
occurs: $\mu^2 \to 0$ and the condensate forms.

\paragraph{Step 4 (Phase-class argument, NOT unique-Cauchy-datum argument).}
The statement reframed by the present theorem is: ``the early-time
state belongs to the symmetric high-temperature phase class
$\langle \Psi \rangle = 0$''. This is a phase-class statement,
compatible with many distinct microscopic Cauchy data; it is NOT the
claim that the microscopic Cauchy datum is unique. The phase-class
statement is the natural ensemble-level characterisation of the
symmetric high-temperature regime $T \gg T_c$ given A0 + A1, and is
\emph{weaker} than the original A2 (which postulated a particular
microscopic isotropic vacuum). The reclassification is therefore a
genuine theoretical-economy gain (one fewer internal microscopic
postulate) at the price of an explicit external boundary input
$T(t)$.

\paragraph{Step 5 (Honest scope).}
Two irreducible elements remain:
\begin{enumerate}
\item The existence of a $t = -\infty$ boundary (fundamental to any Cauchy
  problem, not specific to TECT).
\item The cosmological temperature evolution $T(t)$ (input from general
  relativity / inflation, not derived from TECT alone).
\end{enumerate}

These two elements constitute the "1 cosmological boundary condition" and
cannot be absorbed into TECT without external input.

% =====================================================================
\section{Discussion and outlook}\label{sec:discussion}
% =====================================================================

The reclassification result of Theorem~\ref{thm:main} moves the
ultra-high-energy state from an independent internal microscopic
postulate to a phase-class boundary requirement consistent with the
external cosmological input $T(t)$. The total premise count is
\emph{preserved} as
\[
  3 \;=\; 2_{\text{internal}} \;+\; 1_{\text{boundary}},
\]
i.e.\ the change is \emph{not} an axiom-count reduction; it is a
relabelling of one of the three premises from an internal TECT axiom
to an externally supplied cosmological input. The structural gain is
clarity, not parsimony in the strict count.

\paragraph{What the result does NOT establish.}
Per Remark~\ref{rem:weak-not-elim}, the dissipative TDGL flow is not
time-reversible and the phase-class statement
$\langle\Psi\rangle = 0$ does not single out a unique microscopic
Cauchy datum at $t = -\infty$. The result is therefore a
\emph{weakening / reclassification} of A2, not an \emph{elimination},
and \emph{not} a derivation of a unique microscopic initial state.
TECT's internal logical structure still depends on three premises,
of which two (A0 and A1) are internal dynamical postulates and one
(an externally supplied $T(t)$) is a cosmological boundary input
that is not derived inside TECT.

\paragraph{Future work.}
A genuine premise-count \emph{reduction} would require deriving
$T(t)$ from a TECT-internal cosmological mechanism (or from general
relativity coupled to a TECT-internal stress--energy source), so
that the externally supplied boundary input becomes a derived
quantity. Pending such a derivation, the present reclassification
result is the strongest internally-supported statement.

% =====================================================================
\begin{acknowledgments}
The author thanks the Anthropic Claude Opus 4.7 collaborator for rigorous
analysis of the logical dependency structure and devil's-advocate
questioning of hidden axioms. This work is part of TECT, canonical archive
at \url{https://github.com/TECT-OpenPhysics/TECT}.
\end{acknowledgments}

% =====================================================================
\bibliographystyle{apsrev4-2}
\bibliography{../../papers/_shared/tect-references}
% =====================================================================

\end{document}
