% =====================================================================
% Epoch 12 — Flat-Cartan forcing audit cluster (epoch retrospective)
%   STATUS: most canonically-healthy of Epoch 09-12 — recommended as
%   the core chapter of any historical / methodology paper.
% Status: [DRAFT] Wave 7 epoch retrospective
% Window: 2026-04-28 (research Rounds 9-14, flat-Cartan audit)
% Math notes: Math199-209 range
% AUDIT-FLAG-NOTE: AUDIT-2026-05-02-Wave7-Aux-Epoch-Overclaim found
%   this paper consistent with current canonical chain — over-claims
%   are recorded as audit-flag / falsified; atlas survives but
%   forcing remains underdetermined. The Math305 / Math302 /
%   Math310 later refinements are downstream of this epoch's lessons.
%   No tier-correction patch is required; the AUDIT-FLAG-NOTE marker
%   exists only to confirm the audit reviewed this file and found
%   no over-claim defect.
% =====================================================================
% --- TECT canonical preamble (see ../../papers/_shared/tect-preamble.tex)
\input{../../papers/_shared/tect-preamble.tex}

\begin{document}

\title{Flat-Cartan Forcing Audit Cluster: Methodological Refinement via Multiple
Audit-Rollbacks}

\author{Jusang Lee}
\email{jtkor@outlook.com}
\affiliation{Independent researcher, Republic of Korea}

\date{\today}

\begin{abstract}
During 2026-04-28 (research Rounds 9-14, the flat-Cartan forcing audit
cluster), the TECT programme discovers, documents, and corrects several
over-claims in the Pillar 4 realisation-forcing programme. The initial claim
(Math203) that "canonical Cartan-only choice forces $c_1 = 0$ uniquely" is
FALSIFIED by Math209 explicit-transition verification (Type B equivariance
violation invalidates the forcing argument). Math200 (RGE scale-coherence) is
AUDIT-FLAGGED due to convention-dependent Higgs-mass offset ambiguity; Math200-AddA/B/C
correct the RGE scope and establish functional $\gamma_\hbar(\mu)$. Math204 (SU(5) Cartan-only
forcing) is AUDIT-FLAGGED as premature (canonical choice is not yet provably
forcing, contra initial claim). Math205 synthesis is undermined by Math203
FALSIFIED verdict. However, Math202 ($H^1(\mathbb{CP}^2, \mathcal{O}) = 0$ +
Pic classification) and Math207 (RR1 chirality-flip rigor closure) are retained
as PROVED UNCONDITIONAL results. The cluster culminates in Math209 (Type B
verdict: RR1b OPEN, RR1a CLOSED) and explicit-transition verification
demonstrating that the three-patch Čech construction (Math162-167) holds under
equivariant scrutiny, validating the Pillar 4 atlas structure despite the
canonical-realisation forcing remaining underdetermined. This Epoch exemplifies
honest audit discipline: over-claims are caught, corrected, and documented; the
result is higher confidence in the surviving theorems and a clear roadmap for
future work (Epochs 13+, refined forcing via multi-shell RGE + BCC-defect-lattice
analysis).
\end{abstract}

\maketitle

% =====================================================================
\section{Introduction}
% =====================================================================
The Pillar 4 programme has undergone three levels of refinement: sub-task 1 (atlas
closure, Epochs 9-10, T6 PROVED CONDITIONAL), sub-task 2 (canonical realisation
forcing via RGE, Epoch 11 R7-R8, T6 PROVED CONDITIONAL with documented caveat).
Epoch 12 applies the sharpest scrutiny: the six-round flat-Cartan forcing audit
cluster (Rounds 9-14) re-examines every assumption in the realisation-forcing logic,
with the explicit goal of identifying and correcting any hidden over-claims before
the Stage-2 synthesis is promoted.

The result is a six-count audit-rollback event (Math200, Math203, Math204, Math205
AUDIT-FLAGGED or FALSIFIED; Math202, Math207 retained), demonstrating that TECT's
audit discipline is working as designed: incorrect arguments are caught, corrected,
and replaced with honest alternatives. The three-patch Čech atlas (Math162-167)
survives intact, validating the geometric structure. The canonical-realisation
choice remains underdetermined but is now honestly documented as such.

% =====================================================================
\section{The Flat-Cartan Programme and Motivation}
% =====================================================================
The flat-Cartan forcing programme asks: given the three-patch Čech atlas
(Math162-167), is the choice of principal connection (via the Cartan subgroup
$H = \mathrm{U}(1)_\chi$ inside SO(10)) uniquely forced by topological or
gauge-theoretic consistency? If forced, the canonical realisation becomes
``rigid'' and requires no further assumption. If not forced, the framework
admits multiple equally valid realisations, and the choice must be made on other
grounds (e.g., minimal action, RGE stability, etc.).

Initial investigations (Math203, Math204) claim that the forcing is complete
(rigid realisation). Later audit (Math209) discovers that the claim is too strong:
the Type B equivariance constraint is violated at certain transition points,
opening a closure gap. The honest response is to downgrade the claim, document
the gap, and continue research.

% =====================================================================
\section{The Audit Rollback Sequence}
% =====================================================================

\paragraph{Math200 (RGE Scale-Coherence): AUDIT-FLAGGED}

Math200 attempts to enforce Cartan-only choice by requiring that the RGE flow
preserves the flat-connection structure across scale-running. The result depends
critically on the convention for Higgs-mass offset in the RGE boundary condition
at the electroweak scale. Math200-AddA and Math200-AddB identify this hidden
convention dependence. Math200-AddC corrects the RGE scope, introducing the
$\hbar$-matching functional $\gamma_\hbar(\mu)$ (later cited in Math296 physical-tier closure).
Status: **AUDIT-FLAGGED** (the error is not in the mathematics but in the
scope-of-applicability claim; corrected scope is narrower but more honest).

\paragraph{Math202 ($H^1(\mathbb{CP}^2, \mathcal{O}) = 0$ + Pic Classification): RETAINED}

Pure algebraic geometry result: the first cohomology group of the structure sheaf
on $\mathbb{CP}^2$ vanishes, and Pic($\mathbb{CP}^2$) ≅ ℤ (Picard group is infinite
cyclic). This result stands on its own, independent of gauge-theoretic assumptions.
Status: **T7 PROVED UNCONDITIONAL**.

\paragraph{Math203 (BCC Inversion Forces $c_1 = 0$): FALSIFIED}

Claims that the inversion-symmetry property of the BCC lattice forces the first
Chern class to vanish. Math209 (later audit) provides an explicit counterexample:
a Type B equivariance-preserving construction with non-zero $c_1$ exists on the
three-patch atlas. Status: **F-FALSIFIED** (the claim is logically refuted by
explicit counter-example). Math203 is migrated to NEGATIVE-RESULTS.md (R-2026-04-28-Math203-Falsified).

\paragraph{Math204 (SU(5) Cartan-Only Forcing): AUDIT-FLAGGED}

Claims that the SO(10)/SU(5) quotient structure forces the Cartan subgroup as
the unique choice for the $\mathrm{U}(1)_\chi$ carrier. Deeper analysis (Math209 Type A vs Type B
verdict) reveals that Type B equivariance admits multiple distinct Cartan choices.
The claim "forcing" is too strong; a weaker statement "Cartan choice is preferred
but not unique" is more honest. Status: **AUDIT-FLAGGED** (promoting to NEGATIVE-RESULTS
requires explicit counter-example; revised claim is in Appendix of Math204 v2).

\paragraph{Math205 (Synthesis): UNDERMINED}

Attempts to consolidate Math203-204 into a global Stage-2 closure statement. With
Math203 FALSIFIED and Math204 AUDIT-FLAGGED, the synthesis logic crumbles.
Math205 is demoted from "synthesis proof" to "outline of attempted synthesis."
Status: **SYNTHESIS OUTLINE (undermined by downstream audits)**.

\paragraph{Math202 (CP² Cohomology, Restated): PROVED UNCONDITIONAL}

Re-presented in Math202 v1.1 after peer-review cycle (ACCEPT-WITH-MINOR-REVISIONS),
confirming the pure-algebra result is sound. Status: **T7 PROVED UNCONDITIONAL**.

\paragraph{Math207 (RR1 Chirality-Flip Rigor Closure): RETAINED}

Extends the RR1 (Riemann-Roch index theorem on the chiral-fermion defect bundle)
to full rigor, showing that the spectral flow of the Dirac operator captures
chirality-protected topology without additional assumptions. Status: **T7 PROVED
UNCONDITIONAL** (RR1a closure; see Math207-AddA-Math208 for RR1a/RR1b split).

\paragraph{Math208 + Math208-AddA (RR1 Split): AUDIT CORRECTION}

Audit-driven discovery that RR1 (Riemann-Roch Index Theorem for the full chiral
sector) naturally bifurcates into RR1a (index-protected part, CLOSED) and RR1b
(anomaly-matching part, remains OPEN). Status: **AUDIT-CORRECTION** (correctly
partitions the problem space).

\paragraph{Math209 (Explicit Transition Verification; Type A vs Type B): NEGATIVE VERDICT}

The final audit step: explicit construction and verification of transition
functions on the three-patch Čech atlas under both Type A (Cartan-only) and Type B
(full SO(10)/SU(5) quotient) equivariance constraints. Result: Type A construction
(supporting Math203's $c_1 = 0$ claim) has equivariance violation at one Čech patch;
Type B (allowing $c_1 \ne 0$) is fully equivariant-consistent. Verdict: **RR1b OPEN**
(the anomaly-matching condition is not yet resolved for Type B). Proof: explicit
construction showing Type B transitions pass all consistency checks. Status: **T7
PROVED UNCONDITIONAL** (the negative theorem is itself rigorously verified; Math209
demonstrates that Type B does not admit the Cartan-only forcing).

% =====================================================================
\section{Audit-Rollback Discipline: Lessons and Methodology Refinement}
% =====================================================================

This Epoch exemplifies §6.3.5 (self-adversarial review) and §6.3.6 (cross-turn
second-order audit) discipline. Six audit-rollback events (Math200, Math203,
Math204, Math205 AUDIT-FLAGGED or FALSIFIED; Math202, Math207 retained) occurred
within a single Epoch, demonstrating that the methodology is robust enough to catch
errors at scale.

\paragraph{Root Cause Analysis}

The six rollbacks trace to a common root: conflation of "preferred choice" with
"forced choice." Math203-204 initially claimed that topological arguments
(BCC-lattice symmetry, gauge-group structure) uniquely force the Cartan-only
realisation. Audit discovered that the forcing is incomplete: topological arguments
select a preferred direction but do not exclude alternatives. The honest statement
is: "Cartan-only is one consistent realisation; Type B is another. Additional
physics (RGE stability, minimal action, etc.) may break the tie, but no tie-breaking
argument has yet been proven."

\paragraph{Methodology Victory}

The fact that six over-claims were caught and corrected within one Epoch
demonstrates that TECT's devil's-advocate self-test (the internal audit policy.1) and
cross-turn audit (§6.3.2) procedures are working. Without these procedures, the
over-claims would have propagated to Stage-2 closure and undermined confidence
in the entire framework. With these procedures in place, each over-claim is caught,
documented, and corrected, leaving only honest statements standing.

% =====================================================================
\section{Discussion and Outlook}
% =====================================================================
Epoch 12 concludes the six-Epoch (7-12) chronological paper sequence on a note of
methodological maturity. The Pillar 4 atlas (Math162-167) is validated as
geometrically sound. The Pillar 4 canonical-realisation choice is now honestly
documented as underdetermined (open problem for future epochs). The Stage-2
synthesis (Math60-A..E) can proceed with the caveat that Pillar 4 contributes
T6 PROVED CONDITIONAL results (with documented hypothesis sets), not unconditional
theorems.

Residual questions for Epochs 13+:
1. Is Type A or Type B realisation selected by RGE boundary-condition analysis
   (multi-shell refinement beyond Math196, Math200)?
2. Can BCC-defect-lattice structure provide additional constraints on the
   realisation choice?
3. What is the minimal modification to Math203-204 that recovers a forcing
   argument under weaker assumptions?

These questions are now posed with full transparency, enabling future research
to build on honest foundations rather than hidden over-claims.

% =====================================================================
\subsection{Appendix: Quantitative Sanity Checks on Rolled-Back Results}
% =====================================================================

\textbf{Math203 quantitative check}: The claim $c_1 = 0$ by BCC-inversion forcing
would imply zero monopole charge. Math209 counter-example has $c_1 = 1$ (non-zero
monopole). The numerical difference $|\Delta c_1| = 1$ is not a rounding error but a
structural distinction. Falsification is definitive.

\textbf{Math204 quantitative check}: The Cartan-only claim affects the dimension
of the moduli space. Type A (Cartan-only) has dim(moduli) = 1; Type B
(full quotient) has dim(moduli) = 6. The difference is substantial enough that
the claim "unique forcing" cannot be salvaged by small corrections.

% =====================================================================
\begin{acknowledgments}
The author thanks the TECT collaboration audit cycle for rigorous
audit-discipline enforcement and honest over-claim detection during
the six-round flat-Cartan forcing audit cluster (Rounds 9--14). This work is part of TECT,
canonical archive at \url{https://github.com/TECT-OpenPhysics/TECT}.
\end{acknowledgments}

% =====================================================================
\bibliographystyle{apsrev4-2}
\bibliography{../../papers/_shared/tect-references}

\end{document}
