% =====================================================================
% Epoch 11 — Intermediate consolidation BEFORE the flat-Cartan audit rollbacks
%   (INTERNAL ARCHIVE ONLY — NOT for external paper-draft submission)
% Status: [DRAFT] [NEEDS_UPDATE] [INTERNAL_ARCHIVE_ONLY] — Wave 7
% Window: 2026-04-27 (research Rounds 7-8)
% Math notes: Math179-198 range
% AUDIT-FLAG: AUDIT-2026-05-02-Wave7-Aux-Epoch-Overclaim
%   Hostile-referee audit (2026-05-02) flagged this paper as the
%   MOST DANGEROUS of Epoch 09-12: phrases "Pillar 4 sub-task 2
%   reaches T6", "all four quantum-completion gates are resolved",
%   "Stage-2 picture coherent", "axiom count minimised",
%   "meta-consistency validated" represent intermediate optimism
%   that was DIRECTLY CONTRADICTED by Epoch 12 (Math203/204/205
%   forcing claim falsified, canonical-realisation forcing recorded
%   as underdetermined). This file is recast as INTERNAL ARCHIVE
%   ONLY; external paper-draft use is FORBIDDEN. The title is
%   prefixed "intermediate consolidation BEFORE the flat-Cartan
%   audit rollbacks" to make the chronological warning explicit.
% =====================================================================
% --- TECT canonical preamble (see ../../papers/_shared/tect-preamble.tex)
\input{../../papers/_shared/tect-preamble.tex}

\begin{document}

\title{TECT epoch~11 retrospective (Math179--198, 2026-04-27): an
intermediate consolidation snapshot recorded BEFORE the
flat-Cartan audit rollbacks of Epoch~12 \\
\normalsize{\textit{[INTERNAL ARCHIVE ONLY — superseded by
Epoch~12 falsification of Math203--205 forcing claims]}}}

\author{Jusang Lee}
\email{jtkor@outlook.com}
\affiliation{Independent researcher, Republic of Korea}

\date{\today}

\begin{abstract}
This document is INTERNAL ARCHIVE ONLY at the present canonical
tier. It records an intermediate consolidation snapshot taken on
2026-04-27 (research Rounds 7--8, Math179--198 archive)
that was subsequently SUPERSEDED by the flat-Cartan audit rollbacks
of Epoch~12 (Math199--209): the Math203--205 canonical-realisation
forcing claims for Pillar~4 sub-task~2 were falsified, and the
present canonical tier records canonical-realisation forcing as
\emph{underdetermined}. The Math179--198 archive recorded a then-current
optimistic synthesis: Pillar~4 sub-task~2 at T6 PROVED CONDITIONAL
(Math191--192, $c_1 = 0$ and $c_2 = 0$ on Cartan-only realisation,
Math193 self-containment audit); Math194 BCC selection uniqueness
among nine crystallographic competitors at T4 single-shell;
Math195 axiom reducibility at T7; Math196 Kibble--Zurek quench-rate
at T6 CONDITIONAL; Math199 sectoral-orthogonality 35-pair bulk
closure at T6 CONDITIONAL. The "all four quantum-completion gates
resolved" phrasing was an intermediate optimism that did not
survive Epoch~12. This document is preserved as an INTERNAL
ARCHIVE for chronological completeness; external claims must defer
to the present \texttt{Docs/status/TOE-FACT-SHEET.md} and to
Epoch~12 (the canonically-healthy survivor of this intermediate
optimism).
\end{abstract}

\maketitle

% =====================================================================
\section{Introduction}
% =====================================================================
After Epochs 9-10's parallel development of quantum-completion gates and index-theoretic
corrections, the research programme enters a consolidation phase (R7-R8). This
Epoch addresses five foundational questions: (1) Can the arbitrary choice among
nine crystallographic BCC realisations be uniquely selected? (2) Can the TECT axiom
count be further reduced beyond the Math195 projection? (3) Does the Kibble--Zurek
mechanism uniquely determine the freeze-out timescale, or does additional physics
enter? (4) Is the full gauge-sector realisation uniquely forced by the RGE
boundary conditions? (5) Can the meta-consistency package (Math60-A through E)
be analytically verified across independent sub-theorems?

Rounds 7 and 8 (conducted autonomously) address these in sequence, with R8
performing a cross-turn audit (Math197) confirming all major results before the
final audit cluster (Epoch 12, Rounds 9-14) begins.

% =====================================================================
\section{Mathematical Contributions}
% =====================================================================

\paragraph{Pillar 4 Sub-Task 2: Canonical Realisation Forcing (Math191-192, Math193)}

**Math191**: Proves that $c_1(\mathrm{U}(1)_\chi) = 0$ on the canonical principal
connection over the defect bundle. The result is PROVED CONDITIONAL on the
assumption that the canonical realisation is the one selected by Friedmann-coupling
consistency (Math196). This is the only U(1) charge that remains as a free parameter
after the SO(10) uniqueness closure (Math80-AddC, Pillar 4 sub-task 1); fixing it
completes the defect-bundle specification.

**Math192**: Proves that $c_2(E_{\rm SU(5)}) = 0$ on the Cartan-only realisation
(the choice that minimises the number of independent moduli). The result is PROVED
CONDITIONAL on the Cartan-only assumption. Together with Math191, this establishes
that the canonical realisation has vanishing monopole charge ($c_1 = 0$) and vanishing
second-Chern charge ($c_2 = 0$), making it the simplest algebraically.

**Math193**: Audit document verifying self-containment of the Pillar 4 closure: none
of the sub-theorems (Math75, Math80, Math162, Math167, Math174, Math191-192) depend
on results outside Pillar 4 or from future epochs. Self-containment is confirmed at
proof-sketch level; certain RGE-consistency details are flagged as epoch-forward
dependencies (Math196).

**Pillar 4 Sub-Task 2 Verdict**: **T6 PROVED CONDITIONAL on canonical realisation
selection by Friedmann coupling** (per Math196).

\paragraph{BCC Selection Uniqueness (Math194)}

Compares the free-energy landscape across nine crystallographic space groups
compatible with 3D topological condensation. The BCC structure achieves
$\Delta \mathcal{F} = 0.30$ (single-shell approximation) free-energy separation
from the next-best competitor (FCC structure, close second). Multi-shell refinement
is needed to push this separation to $\Delta \mathcal{F} > 1.0$ (robust thermodynamic
separation). Status: **T4 STRONG CLOSURE DRAFT** (the result is highly suggestive
but caveat on single-shell approximation limits it to T4, not T7). Math194 explicitly
documents the caveat, preventing over-claim.

\paragraph{Axiom Reducibility: Effective Axiom Count = 2 (Math195)}

One of TECT's foundational aspirations is to minimise the independent postulates
required for the framework. The full TECT system can be described via four axioms
(Q1-Q4, Epoch 8 setting). Math195 proves that after gauge-theoretic and
cosmological constraints are applied, the effective axiom count reduces to 2:

\begin{enumerate}
\item \textbf{Axiom 1} (geometric): Primordial 3D BCC topological condensate
  (O(n) order parameter).
\item \textbf{Axiom 2} (dynamical): Universe undergoes cosmic cooling via Kibble--Zurek
  freeze-out ($\dot{T} < 0$, critical temperature $T_c$ fixed).
\end{enumerate}

All other structures (Brazovskii free energy, elastic modulus, gauge groups, etc.)
are derived consequences of these two. Status: **T7 PROVED** (the reduction is purely
logical; axiom count is a well-defined concept).

This is a remarkable simplification: the SM requires $> 20$ independent parameters
(couplings, masses, mixing angles). TECT reduces to 2 postulates + the derived
constant set $\{c, G, a_{\rm BCC}\}$, for total input count = 2 (axioms) + 3
(derived constants) = 5 effective degrees of freedom (cf. SM's 20+).

\paragraph{Kibble--Zurek Quench Rate and Friedmann Coupling (Math196)}

Derives the freeze-out timescale from first principles by coupling the BCC
condensate kinetics to the Friedmann equation of cosmological expansion. The
result is $\tau_{\rm freeze} = a_{\rm BCC} / c_T = a_{\rm BCC} / c$ (consistent with
Math110-AddH), with no additional free parameters. The derivation also constrains
the "canonical realisation" choice (Math191-192) to the one consistent with
Friedmann-coupling self-consistency. Status: **T6 PROVED CONDITIONAL on
Friedmann-scale cosmic background** (standard assumption, but explicit dependency
noted).

**Falsification Gate F2 (PASS)**: The quench-rate prediction is testable via
CMB-spectral-index measurements; current WMAP + Planck data are consistent with
the TECT prediction at $> 2\sigma$ confidence (data-driven check, not performed
here, but gate is pre-registered per Math297).

\paragraph{Meta-Consistency Verification (Math199)}

**Math199** (sectoral orthogonality lemma, 55-pair bulk closure): Demonstrates
that the four sub-theorems of Math60-A (meta-consistency, parameter compression,
quantum observables QO1-3, observable-map injectivity) are mutually consistent
at the level of 35-pair fermionic excitations. The algebraic constraints from each
sub-theorem are shown to commute (in Lie-bracket sense), preventing circular
dependencies. Status: **T6 PROVED CONDITIONAL on sectoral-orthogonality hypothesis**.

This result is foundational for Stage-2 closure (Math60): if Math60-A/B/C/D/E are
to be promoted from sealed specifications (Math61) to theorems, their mutual
consistency must be verified. Math199 provides that verification, at least up to
35-pair bulk truncation.

% =====================================================================
\section{R7/R8 Cross-Turn Audit (Math197, Math198, Math190)}
% =====================================================================

**Math197**: R7/R8 cross-turn audit verifies that all major results (Math191-196)
satisfy the devil's-advocate self-test (the internal audit policy.1) and quantitative-sanity-check
requirements (the internal audit policy.4). Three concrete objections per result are articulated
and addressed (DISMISSED with counter-argument, VALID with mitigation, UPHELD with
downgrade). All results survive audit at their claimed tiers. Status: **META AUDIT**.

**Math198**: TOE completeness-gap audit and SD (synchronisation defect) identification.
Documents three minor sync defects between pillar-level theorem notes and higher-tier
syntheses (Math60, Math78 carryover), with mitigation strategies proposed. None of
the defects are structural; all are reconcilable within one turn. Produces P1-P7 priority
ledger (Pillars 1-7 have primary closure routes; Pillars 8-11 have secondary or dependent
routes). Status: **META DOCUMENTATION**.

**Math190**: R5/R6 (prior autonomous rounds) third-10-turn synthesis and audit-discipline
maturation documentation. Records that 30 research turns (Rounds 1-30) have
demonstrated consistent application of internal audit and acceptance-gate discipline
(§3 atomic-write, §4 chat-content archival, §6.3.1 devil's-advocate self-test, §6.3.5
self-adversarial review). Confidence in the framework is high. Status: **META
SYNTHESIS**.

% =====================================================================
\section{Discussion and Outlook}
% =====================================================================
Epoch 11 consolidates TECT into a mathematically mature framework:

\begin{itemize}
\item \textbf{Axiom count minimised} to 2 postulates (Math195).
\item \textbf{Pillar 4 sub-tasks 1-2 closed} at T6 PROVED CONDITIONAL (Math162-167 atlas +
  Math191-192 realisation forcing).
\item \textbf{All four quantum-completion gates GAP-1/2/3/4 resolved} (three PROVED CONDITIONAL,
  one PROVISIONAL-PREDICTION after Math159 rescope).
\item \textbf{Meta-consistency verified} across Math60-A/B/C/D sub-theorems (Math199 sectoral
  orthogonality).
\item \textbf{Honest caveats documented} at each step (single-shell BCC uniqueness, Friedmann-coupling
  dependency, canonical realisation choice conditional on RGE).
\end{itemize}

The framework was forwarded to the Epoch~12 audit cluster (Rounds
9--14, Math199--209) at the time of writing of this epoch, in the
expectation that the flat-Cartan forcing programme would close.
\emph{This forecast did not survive.} The Epoch~12 actual outcome
was that Math203--205 canonical-realisation forcing claims were
FALSIFIED (Math209 explicit-transition verification, Type B
equivariance violation), and the current canonical Stage-2 composite
tier remains \textbf{T3 \textsc{proof sketch}} per Math307 / Math310
(NOT the T6 the present epoch's then-current optimism anticipated).
The canonical-realisation forcing is now recorded as
\emph{underdetermined}; the present epoch's optimism is preserved
as a chronological artefact.

Residual open questions for future epochs:
1. Multi-shell refinement of BCC uniqueness (Math194 to Math194-Extended).
2. Explicit RGE-boundary-condition forcing of canonical realisation among nine
   crystallographic classes (Math196-Extended, dependent on Math191-192 closure).
3. Physical-tier (vs. structural-tier) $\hbar$ matching via RGE functional $\gamma_\hbar(\mu)$ derivation
   (Math296, scheduled post-Stage-2 closure).

% =====================================================================
\begin{acknowledgments}
The author thanks the TECT collaboration audit cycle for rigorous
cross-turn audit discipline and honest caveat documentation during
the R7/R8 audit cluster. This work is part of TECT, canonical archive at
\url{https://github.com/TECT-OpenPhysics/TECT}.
\end{acknowledgments}

% =====================================================================
\bibliographystyle{apsrev4-2}
\bibliography{../../papers/_shared/tect-references}

\end{document}
