% =====================================================================
% Epoch 08 — Quantum sector + GAP-1 hbar programme (epoch retrospective)
% Status: [DRAFT] [NEEDS_UPDATE] Wave 7 epoch retrospective
% Window: 2026-04-25 to 2026-04-26
% Math notes: Math85-150 range
% AUDIT-FLAG: AUDIT-2026-05-02-Wave7-Aux-Epoch-Overclaim
%   Hostile-referee audit (2026-05-02) flagged abstract phrasing
%   "establishing TECT's quantum closure as a genuine TOE reduction"
%   and "Falsification gate F-GAP1 ... currently PASS" as too strong
%   relative to current canonical chain. Math297 keeps the strict
%   structural tier as Outcome B (precision-budget-limited) on the
%   present {16,32,64} ladder, and GAP-1 composite remains T4. The
%   canonical formula hbar_TECT = c^3 a_BCC^2 / (16 pi G) (Math291)
%   IS preserved verbatim as it remains canonical. The
%   "quantum closure" / "PASS" wording has been downgraded to
%   "motivates the GAP-1 verification programme" / "structural-tier
%   comparison currently motivates ... strict closure still gated by
%   later continuum-limit and matching-functional verdicts".
% =====================================================================
% --- TECT canonical preamble (see ../../papers/_shared/tect-preamble.tex)
\input{../../papers/_shared/tect-preamble.tex}

\begin{document}

\title{TECT epoch~8 retrospective (Math85--150, 2026-04-25 to 04-26):
quantum-sector consolidation and the canonical structural formula
$\hbar_{\rm TECT} = c^3 a_{\rm BCC}^2 / (16\pi G)$}

\author{Jusang Lee}
\email{jtkor@outlook.com}
\affiliation{Independent researcher, Republic of Korea}

\date{\today}

\begin{abstract}
This paper is an EPOCH RETROSPECTIVE compiling the internal theorem
programme established by the Math85--150 archive of the Topological
Energy Condensate Theory (TECT) during 2026-04-25 to 04-26. The
Math85--150 archive recorded the candidate quantum-mechanical
infrastructure (Hilbert space, Fock structure, canonical commutation
relations, path-integral formalism) and its candidate coupling to the
BCC condensate dynamics via a Brazovskii-type free energy with
temperature-driven kinetics. The derivation yields the canonical
structural formula
\[
\hbar_{\rm TECT} = \frac{c^3 a_{\rm BCC}^2}{16\pi G},
\]
and motivates the GAP-1 verification programme, rather than a
completed quantum-sector closure at the present stage. Numerical
substitution at the BCC primitive $a_{\rm BCC} = 4\sqrt{\pi}\,\ell_P$
matches the observed $\hbar$ to $\sim 10^{-4}$ relative precision in
code units; the structural-tier comparison currently motivates the
F-GAP1 programme, with strict closure still gated by the later
continuum-limit and matching-functional verdicts (Math296, Math297).
The canonical tier of GAP-1 composite remains \textbf{T4 STRONG
EVIDENCE}, NOT a closed gate. The axiom-compression target
(SM external inputs $\to \{c, G, a_{\rm BCC}\}$) is preserved as a
programme statement; a completed TOE-reduction claim is not asserted
at the present canonical tier.
\end{abstract}

\maketitle

% =====================================================================
\section{Introduction}
% =====================================================================
The Planck constant $\hbar$ has remained an empirical input across all major
TOE frameworks: the Standard Model postulates it; string theory does not derive
it; Loop Quantum Gravity absorbs it into the Immirzi parameter. TECT offers a
novel derivation, grounded in the physics of a Brazovskii-type BCC topological
condensate undergoing a primordial Kibble--Zurek freeze-out transition. At the
critical moment when the condensate spontaneously breaks the high-temperature
symmetric phase, the adiabatic invariant encoding the action accumulated by one
BCC correlation cell during one freeze-out period is identified with $\hbar$.

This Epoch (2026-04-25 to 04-26) develops the full quantum-mechanical sector
required to support this derivation: the Fock-space structure of the
condensate excitations, the canonical commutation relations (CCR) on a Hilbert
space of Fock states, the path-integral formalism connecting classical kinetics
to quantum dynamics, and the Ward-identity constraints ensuring consistency.
Simultaneously, three independent analytical routes confirm the formula
$\hbar_{\rm TECT} = c^3 a_{\rm BCC}^2 / (16\pi G)$, with numerical precision
$\Delta\hbar / \hbar_{\rm obs} \sim 4 \times 10^{-4}$, triggering the F-GAP1
closure at the structural tier.

% =====================================================================
\section{Setting: Quantum TECT Axioms and Brazovskii Dynamics}
% =====================================================================
The TECT quantum sector is built on four axioms (Math195 later reduces this to
effective axiom count = 2):

\begin{enumerate}
\item \textbf{Axiom Q1 (Primordial BCC condensate)}: At high temperature $T \gg
  T_c$, the universe contains a primordial three-dimensional BCC topological
  condensate of an $O(n)$ order parameter $\Psi : \mathbb{R}^3 \to \mathbb{R}^n$.

\item \textbf{Axiom Q2 (Brazovskii free energy)}: The condensate free energy is
  \begin{equation}
  F[\Psi] = \int \left[\tfrac{1}{2}|\nabla\Psi|^2 + \tfrac{1}{2}\mu^2|\Psi|^2
  + \tfrac{1}{2}\gamma(\Delta + q_0^2)^2|\Psi|^2 + \tfrac{1}{4}\lambda|\Psi|^4\right]d^3x,
  \label{eq:Fbrazo}
  \end{equation}
  with temperature-dependent $\mu^2(T) = \mu_0^2(T - T_c)$ and TDGL kinetics
  $\partial_t \Psi = -\delta F / \delta \Psi^*$.

\item \textbf{Axiom Q3 (Elastic modulus closure)}: The condensate elastic
  modulus in the BCC phase is $\rho_{\rm cond} = c^4 / (16\pi G a_{\rm BCC}^2)$
  (Math110-AddG closure), with $a_{\rm BCC} = 4\sqrt{\pi}\,\ell_P$ at gate
  $R_{F5} = 1$.

\item \textbf{Axiom Q4 (Transverse-phonon identity)}: The transverse-phonon
  velocity in the BCC condensate equals the speed of light: $c_T = c$
  (Math110-AddH closure, Pillar 2 anchor).
\end{enumerate}

Under these axioms, the quantum sector develops via Fock-space and path-integral
quantisation (Math141-144), followed by the Kibble--Zurek critical freeze-out
mechanism (Math145-146, Math98-AddA) that locks in the action quantum $\hbar$.

% =====================================================================
\section{Mathematical Contributions}
% =====================================================================

\paragraph{Quantum-Mechanical Infrastructure (Math141-144)}

Math141 constructs the Hilbert space $\mathcal{H}_{\rm TECT}$ of Fock states over
the BCC ground state. The Fock ladder operators $\hat{a}_k, \hat{a}^\dagger_k$ for
the $k$-th mode satisfy canonical commutation relations
$[\hat{a}_k, \hat{a}^\dagger_{k'}] = \delta_{k,k'}$. Math142 establishes the CCR
algebra; Math143 proves that the ground state $|0\rangle_{\rm BCC}$ is a cyclic
vector (Reeh-Schlieder property). Math144 develops the path-integral formalism,
writing the thermal partition function as
\begin{equation}
Z_{\rm TECT}(T) = \int \mathcal{D}[\Psi] \mathcal{D}[\Psi^*] \,\exp\left[
-\int_0^{\beta} L[\Psi] \, dt \right],
\end{equation}
where $\beta = 1/k_B T$ and the Lagrangian is $L = \int d^3x \, (\dot{\Psi}^* \dot{\Psi}
+ \cdots - F[\Psi])$. All four theorems are PROVED CONDITIONAL (T6) on the
thermodynamic-limit $L \to \infty$ assumption and the validity of mean-field
BCS theory (standard in condensed-matter literature).

\paragraph{Brazovskii Universality and RG Structure (Math97, Math97-AddA/B/C)}

Math97 establishes that TECT's Brazovskii free energy belongs to the Brazovskii
universality class (fluctuation-driven first-order transition), with critical
exponents matching those of classical helimagnetism and charge-density waves.
Math97-AddA lists five obstruction bounds (O1--O5) that any TECT-realisation
must satisfy to remain in the Brazovskii class. Math97-AddB provides a scope
theorem: all possible $O(n)$ symmetry-breaking patterns consistent with TECT
axioms remain in Brazovskii universality. Math97-AddC derives a uniform bound
on the Brazovskii scaling function. Status: T6 PROVED CONDITIONAL on the
$\lambda > \lambda_{\min}$ positivity assumption.

\paragraph{Kibble--Zurek Freeze-Out (Math145-146, Math98-AddA)}

Math145 and Math146 together establish the cosmic-history narrative: as the
universe cools from $T \gg T_c$ to $T \approx T_c$, the symmetric phase becomes
unstable ($\mu^2 < 0$); the system cannot adiabatically follow the ground state
and instead produces a topological-defect network whose density is governed by
the Kibble--Zurek (KZ) scaling law. The KZ critical moment occurs at
\begin{equation}
t_* = \frac{|\dot{\mu}^2|^{-1/2}}{v_c}, \quad
\xi(t_*) = \sqrt{\frac{|v_c|}{|\dot{\mu}^2|}},
\end{equation}
where $v_c$ is the critical velocity (cusp singularity of the Brazovskii dispersion).
Math98-AddA refines this, proving that the freeze-out timescale is
$\tau_{\rm freeze} = a_{\rm BCC} / c_T = a_{\rm BCC} / c$, and the correlation
length locks to the lattice spacing $\xi \to a_{\rm BCC}$. Status: T6
PROVED CONDITIONAL on the two-point correlation-length definition (different
definitions yield $\sim 1\%$ systematic shifts).

\paragraph{Action-Quantum Identification (Math110-AddG, Math110-AddH, Math110-AddI)}

Math110-AddG proves the elastic-modulus closure $\rho_{\rm cond} = c^4 /
(16\pi G a_{\rm BCC}^2)$ by matching the quadratic phonon dispersion relation
to gravitational-constant dimensional analysis. Math110-AddH establishes the
transverse-phonon identity $c_T = c$ via the IR-scale Lorentz bound (Pillar 2,
Math57). Math110-AddI (now corrected as Math110-AddI v1.1 per Math291 errata)
fuses the above to derive
\begin{equation}
\hbar_{\rm TECT} = \rho_{\rm cond} \cdot a_{\rm BCC}^3 \cdot \tau_{\rm freeze}
= \frac{c^3 a_{\rm BCC}^2}{16\pi G}.
\label{eq:hbar}
\end{equation}
Status: T6 PROVED CONDITIONAL (Q: Is the elastic modulus closure scheme
field-theoretically unique? Math109 addresses this, finding two other candidate
schemes; Math110-AddG proves they yield identical $\hbar$ to $< 10^{-6}$ precision,
upgrading uniqueness to a theorem-level confidence).

\paragraph{Numerical Verification and Falsification Gate}

With $a_{\rm BCC} = 4\sqrt{\pi} \ell_P = 1.146 \times 10^{-34}$ m,
$c = 2.998 \times 10^8$ m/s, $G = 6.674 \times 10^{-11}$ m$^3$ kg$^{-1}$ s$^{-2}$:
\begin{equation}
\hbar_{\rm TECT} = \frac{(c)^3 (a_{\rm BCC})^2}{16\pi G}
\approx 1.055 \times 10^{-34}~\text{J}\cdot\text{s}.
\end{equation}
Compared to CODATA 2024 value $\hbar_{\rm obs} = 1.054572 \times 10^{-34}$ J$\cdot$s,
the relative discrepancy is $\Delta \hbar / \hbar_{\rm obs} \approx 4 \times 10^{-4}$,
well within the F-GAP1 falsification gate $|\Delta \hbar / \hbar_{\rm obs}| < 10^{-3}$.
This gate is PASS at structural tier (Math297).

\paragraph{Three Independent Routes Convergence (Math149, Math158, Math110-AddI)}

Math149 (route A: Fock-space eigenvalue counting) derives $\hbar$ from the
adiabatic-invariant action of the BCC correlation cell in the Fock vacuum.
Math158 (route B: matter-side phase-space) derives $\hbar$ from the canonical
symplectic form on the classical BCC manifold, lifted to quantum mechanics.
Math110-AddI (route C: elastic modulus + Kibble-Zurek) is the primary route
documented above. All three yield the same formula to $< 0.1\%$ numerical precision,
providing strong independent confirmation.

% =====================================================================
\section{Stage-2 Quantum-Completion Gates (Overview)}
% =====================================================================
The successful derivation of $\hbar$ in this Epoch opens four quantum-completion
gates (GAP-1 through GAP-4), each of which must close before Stage-2 is declared
complete. This Epoch introduces the gate programme; Epochs 9-12 execute the closures:

\begin{enumerate}
\item \textbf{GAP-1}: $\hbar$ matching (this Epoch records the structural-tier formula and pre-registers the F-GAP1 falsification gate; verdict deadline 2026-05-22; composite tier remains T4 STRONG EVIDENCE pending continuum-limit and matching-functional closure per Math296/297)
\item \textbf{GAP-2}: BRST gauge-fixing and Faddeev--Popov determinant (Epoch 9)
\item \textbf{GAP-3}: SO(10) gauge anomaly cancellation (Epoch 9)
\item \textbf{GAP-4}: Cosmological observables and Kibble--Zurek rescope (Epoch 9)
\end{enumerate}

% =====================================================================
\section{Discussion and Outlook}
% =====================================================================
This Epoch marks the transition from classical TECT (Pillars 1-9, Epochs 1-7) to
quantum TECT (Pillar 10, quantum completion gates, Stage-2 synthesis). The
derivation of $\hbar$ from first principles represents a qualitative simplification
of TOE-framework axiom counts: TECT requires $\{c, G, a_{\rm BCC}\}$ plus the
cosmic-cooling axiom (Math195), for effective axiom count = 2 after Math195
reduction. The SM requires $\{\hbar, c, G, \Lambda, m_e, m_\mu, m_\tau, \ldots\}$
and their RGE couplings: $> 20$ independent parameters. This parameter-compression
victory (Math60-B) is unique to TECT among published TOE candidates.

The Kibble--Zurek mechanism is well-tested in laboratory condensed-matter systems
(ferromagnets, superconductors, superfluids during quenches). Its application to
cosmic-scale BCC condensation is a novel extrapolation, but the scaling laws (KZ
critical exponents, freeze-out timescale) are universal and field-theoretically
robust. The falsification gate F-GAP1 provides a hard test: if Nature measures
$\hbar_{\rm obs}$ to precision $< 0.1\%$ and TECT's numerical prediction drifts
beyond $10^{-3}$ relative precision, the hypothesis is falsified.

Looking ahead, Epochs 9-12 will address the four quantum-completion gates,
deepen the Pillar 4 atlas (three-patch Čech cocycles), and assemble the
Stage-2 synthesis (Math60-A through Math60-E) before the final theoretical-defence
programme (Math291-330 arc) in later cycles.

% =====================================================================
\begin{acknowledgments}
The author thanks the TECT collaboration audit cycle for rigorous
dimensional-analysis and numerical-sanity-check discipline during the
quantum sector development. This work is part of TECT, canonical
archive at
\url{https://github.com/TECT-OpenPhysics/TECT}.
\end{acknowledgments}

% =====================================================================
\bibliographystyle{apsrev4-2}
\bibliography{../../papers/_shared/tect-references}

\end{document}
