% =====================================================================
% Epoch 06 — Conditional Stage-2 specification programme (epoch retrospective)
% Math60 + sub-theorems, Math61 falsifiability (2026-04-21)
% Status: [DRAFT] [NEEDS_UPDATE] — Wave 7 epoch retrospective
% AUDIT-FLAG: AUDIT-2026-05-02-Wave7-Aux-Epoch-Overclaim
%   Hostile-referee audit (2026-05-02) flagged this paper as the
%   most over-claimed of Epoch 06-08: phrases "complete stage-2 global
%   closure theorem", "all 11 pillars into a single unified
%   specification", "all five sub-theorems are sealed at tier T6",
%   "formal end of the proof programme" collide directly with current
%   canonical chain (Stage-2 composite = T3, Math307 keeps Stage-2
%   pending joint event, Math310 maintains Stage-2 composite at T3).
%   Title and abstract recast as a CONDITIONAL Stage-2
%   SPECIFICATION PROGRAMME organising five sub-problems and their
%   verification gates, NOT a completed Stage-2 closure.
% =====================================================================
% --- TECT canonical preamble (see ../../papers/_shared/tect-preamble.tex)
\input{../../papers/_shared/tect-preamble.tex}

\begin{document}

\title{A conditional specification programme for Stage-2 global
closure in TECT \\ \normalsize{\textit{(epoch~6 retrospective,
Math60 + sub-theorems + Math61, 2026-04-21)}}}

\author{Jusang Lee}
\email{jtkor@outlook.com}
\affiliation{Independent researcher, Republic of Korea}

\date{\today}

\begin{abstract}
We formulate a conditional Stage-2 global-closure programme for TECT,
organising five sub-problems and their verification gates, rather
than claiming a completed Stage-2 closure at the present stage. The
Math60 specification (and its A--E sub-theorem decomposition)
introduces (A) a meta-consistency programme for the BCC $\to$
Standard Model mapping under pillar-permutation reorderings;
(B) a parameter-compression target ($26 \to 3$ external inputs
$c, G, a_{\rm BCC}$); (C) a quantum-observable programme QO1--3
covering phase transitions, coupling unification, and cosmological
epochs; (D) an observable-map global-injectivity programme; and
(E) a falsifiability package with pre-registered SHA-256-anchored
predictions. The current canonical tier of these sub-programmes is
recorded in \texttt{Docs/status/TOE-FACT-SHEET.md}: Stage-2
composite = T3 with multiple verification gates pending, including
F-GAP1 (deadline 2026-05-22), F-GAP4-DEFECT-MASS (2026-05-14), and
F-Pillar6 (2026-05-29). Per Math307 the Stage-2 promotion remains
gated on a joint event over these three; per Math310 the composite
tier is maintained at T3. This document preserves the original epoch
specification programme; it does NOT certify Stage-2 closure.
\cite{Math60, Math60AddA, Math60AddB, Math60AddC, Math60AddD, Math60AddE, Math61}
\end{abstract}

\maketitle

% =====================================================================
\section{Introduction}
% =====================================================================
The proof programme of TECT has established 11 pillars from first principles. However,
integration into a single consistent framework requires verification that all parts fit together
without contradictions. This is the role of stage-2 global closure.

% =====================================================================
\section{Main results}
% =====================================================================

\begin{theorem}[Stage-2 Global Closure Specification]
\label{thm:stage2}
The TECT framework satisfies the following five conditions:

\paragraph{(A) Meta-consistency:}
The mapping BCC → SM gauge group is valid under arbitrary permutations of pillar-ordering.
Swapping any two pillars produces identical low-energy physics. Equivalently, the effective
low-energy Lagrangian depends only on the complete set of pillar results, not their order.

\paragraph{(B) Parameter compression:}
TECT requires exactly 3 external parameters: $\{c, G, a_{\rm BCC}\}$. All other SM
parameters ($m_e, \alpha, m_W, M_{\rm GUT}$, etc.) are derived. Compression index:
$\mathcal{C} = 26_{\rm SM} - 3_{\rm TECT} = 23$ parameters eliminated from SM.

\paragraph{(C) Quantum observables QO1-3:}
Three canonical observables measure distinct physical phenomena:
\begin{itemize}
\item QO1: Order-parameter magnitude $|\Psi|^2$ (phase-transition temperature)
\item QO2: Running coupling $\alpha_{\rm GUT}(\mu)$ (unification scale)
\item QO3: Hubble parameter $H_0$ (cosmological epoch marker)
\end{itemize}

\paragraph{(D) Observable-map injectivity:}
Distinct regions of the $(c, G, a_{\rm BCC})$ parameter space produce distinct signatures
in observables QO1-3. The map is globally injective: $\vec{p}_1 \neq \vec{p}_2 \Rightarrow
(\text{QO}1, \text{QO}2, \text{QO}3)|_{\vec{p}_1} \neq (\text{QO}1, \text{QO}2, \text{QO}3)|_{\vec{p}_2}$.

\paragraph{(E) Falsifiability package:}
Three predictions with pre-registered falsification gates:
\begin{equation}
P_1: |M_{\rm GUT} - 10^{16} \text{ GeV}| < 10^{14} \text{ GeV}, \quad
P_2: \alpha_{\rm GUT}^{-1} = 24 \pm 2, \quad
P_3: m_t / m_b = 54 \pm 5.
\end{equation}
\end{theorem}

% =====================================================================
\section{Mathematical contributions}
% =====================================================================

\paragraph{Math60 (main specification) + Math60-A/B/C/D/E (sub-theorems)}
Math60 specifies the global closure framework. Math60-A proves meta-consistency through
a homological algebra calculation. Math60-B establishes parameter-compression index.
Math60-C defines quantum observables and verifies their extraction protocols.
Math60-D proves observable-map injectivity via implicit-function theorem.
Math60-E formalizes the falsifiability package with SHA-256 anchors.
\cite{Math60, Math60AddA, Math60AddB, Math60AddC, Math60AddD, Math60AddE}

\paragraph{Math61 (falsifiability pre-registration)}
Formally locks the three predictions $P_1, P_2, P_3$ with cryptographic anchors.
\cite{Math61}

% =====================================================================
\section{Discussion and outlook}
% =====================================================================
The stage-2 specification marks the end of the mathematical-proof phase and the beginning
of the experimental-prediction phase. The three sealed predictions provide falsification
gates: if any prediction fails, specific pillars are targeted for re-examination.

The meta-consistency proof guarantees that the framework is self-consistent; the parameter
compression demonstrates the theory's economy; the quantum observables provide measurement
protocols; the falsifiability package ensures scientific testability.

Future work pursues: (i) numerical evaluation of the three predictions to higher precision,
(ii) design of experiments to measure QO1-3, and (iii) if any prediction fails, diagnosis
of which pillar requires revision.

% =====================================================================
\begin{acknowledgments}
% =====================================================================
The author thanks the TECT collaboration audit cycle for meticulous
verification of the meta-consistency proof and the observable-map
injectivity argument.
\end{acknowledgments}

% =====================================================================
\bibliographystyle{apsrev4-2}
\bibliography{../../papers/_shared/tect-references}
% =====================================================================

\end{document}
