% =====================================================================
% Paper 12 — HISTORICAL Stage-2 synthesis draft (Math60 OLD packaging)
%   (NOT a current canonical Stage-2 closure paper; external use
%    FORBIDDEN at present canonical tier per Math314-AddD)
% Status: [DRAFT] [NEEDS_UPDATE] [EXTERNAL_USE_FORBIDDEN]
% AUDIT-FLAG: AUDIT-2026-05-02-Wave7-Aux-Epoch-Overclaim
%   (Math314-AddD extension covering Wave 1/4/5 papers Paper-09..16).
%   Hostile-referee audit (2026-05-02): paper reuses old Math60-A..E
%   Stage-2 packaging that is no longer aligned with the current
%   canonical bookkeeping. Current canonical state:
%     GAP-2 = T6, GAP-3 = T6, GAP-1 = T4, GAP-4 = T3
%     Stage-2 composite = min(T4, T6, T6, T3) = T3
%     Stage-2 promotion requires (C_1 ∧ C_2 ∧ C_3) ∧ (F-GAP4 = PASS)
%     (Math307, Math310 latest synthesis)
%   This paper's "Stage-2 global closure theorem" / "quantum sector is
%   mathematically complete" / "five sub-theorems establish structural
%   integrity" wording is far ahead of T3 composite. External use is
%   FORBIDDEN at present canonical tier; the paper is preserved as a
%   historical Stage-2 synthesis draft for chronological completeness
%   only.
% Compile: pdflatex Paper-12.tex (×2 for refs)
% Canonical archives: Math60, Math60-A..E, Math61, Math83, Math307,
%                     Math310, Math314-AddD
% =====================================================================
% --- TECT canonical preamble (see _shared/tect-preamble.tex) ----------
\input{../_shared/tect-preamble.tex}

\begin{document}

\title{A historical Stage-2 synthesis draft for TECT (Math60-A..E
old packaging) \\
\normalsize{\textit{(NOT a current canonical Stage-2 closure paper;
the current canonical Stage-2 composite tier is T3 per Math307 /
Math310 with promotion gated by $(C_1 \wedge C_2 \wedge C_3)
\wedge (\text{F-GAP4}=\text{PASS})$. External use FORBIDDEN at the
present canonical tier per Math314-AddD audit.)}}}

\author{Jusang Lee}
\email{jtkor@outlook.com}
\affiliation{Independent researcher, Republic of Korea}

\date{\today}

\begin{abstract}
This document is preserved as a historical Stage-2 synthesis draft
(Math60-A..E old packaging) for the Topological Energy Condensate
Theory (TECT). External use is FORBIDDEN at the present canonical
tier per the Math314-AddD audit, because the original abstract /
introduction wording (``Stage-2 global closure theorem'' / ``quantum
completion'' / ``structural integrity established'') is incompatible
with the current canonical bookkeeping:
\[
\text{GAP-2}=T6,\ \text{GAP-3}=T6,\ \text{GAP-1}=T4,\ \text{GAP-4}=T3,
\quad
\text{Stage-2 composite} = \min = T3.
\]
Stage-2 promotion requires the joint event
$(C_1 \wedge C_2 \wedge C_3) \wedge (\text{F-GAP4}=\text{PASS})$ per
Math307 / Math310 / Math311 latest synthesis; none of these gates
have arrived at the present date. The original Math60-A..E
five-sub-theorem packaging predates the GAP-1/2/3/4 +
verdict-shell decomposition that Math270--313 introduced; this draft
is therefore a chronological-record artefact, not a current
canonical claim. Refer to the canonical
\texttt{Docs/status/TOE-FACT-SHEET.md} and to Paper-12 successor
drafts (when available) for the current Stage-2 status.
\end{abstract}

\maketitle

% =====================================================================
\section{Introduction --- historical record framing}
\label{sec:intro}
% =====================================================================

\textbf{Historical scope.} This document records the
\emph{Math60-A..E (2026-04 era) Stage-2 synthesis packaging} as it
was drafted prior to the Math270--Math313 verdict-shell decomposition.
At that time, ``Stage-2 closure'' was framed as the conjunction of
five sub-theorems M60-A, \dots, M60-E. The packaging was overtaken
in late April / early May 2026 by the GAP-1/2/3/4 +
verdict-shell architecture introduced in Math270 onwards, in which
Stage-2 promotion is gated by the joint event
$(C_1 \wedge C_2 \wedge C_3) \wedge (\text{F-GAP4} = \text{PASS})$.
The current canonical Stage-2 composite tier per Math307 / Math310 is
\textbf{T3 \textsc{proof sketch}}, with the four-GAP sub-tiers
\[
  \text{GAP-2}=T6,\quad \text{GAP-3}=T6,\quad \text{GAP-1}=T4,\quad
  \text{GAP-4}=T3.
\]
Because the present paper's body uses the older Math60 packaging, it
\emph{cannot} be promoted to or used as a current canonical
Stage-2 closure paper.

\textbf{Reading guide.} The remainder of this document reproduces the
2026-04 era Math60 packaging verbatim, with each section now
introduced by an explicit ``Historical record'' header noting the
gap between the older claim and the current canonical bookkeeping.
A reader interested in the current Stage-2 status should consult
\texttt{Docs/status/TOE-FACT-SHEET.md} and the canonical Math307 /
Math310 / Math311 verdict-shell archives, not the body of this paper.

% =====================================================================
\section{Historical setting: the 11-pillar framework
(Math60-A..E packaging)}\label{sec:setting}
% =====================================================================

\textbf{Historical record.} The 2026-04 era Math60 packaging
listed eleven foundational closure conditions, reproduced verbatim
below. The list has \emph{not} been re-audited against the current
Math270--Math313 verdict-shell decomposition; it should be read as a
chronological record, not as a current canonical roster.

\subsection{The 11-pillar framework (historical Math60 packaging)}

TECT posits 11 foundational closure conditions:
\begin{enumerate}
\item BCC ground-state uniqueness (mass gap $m^*$)
\item Kinematic Lorentz invariance at the BCC fixed point
\item Emergent gravity (spin-2 graviton at one loop)
\item SO(10) gauge-group emergence
\item Chirality from index-theoretic protection
\item Generations and SM embedding
\item Per-generation quantum consistency (Ward + Witten + mod-2)
\item Lorentz invariance (interval certificate)
\item Equivalence principle from maximum-proper-distance principle
\item Planck constant $\hbar$ origin (phase transition + matter side)
\item Cosmological constant $\Lambda$ four-sector cancellation
\end{enumerate}

In the Math60 packaging, ``Stage-2 closure'' was framed as a
\emph{compatibility} statement on the 11-pillar system, not as
independent verification of each pillar.

\subsection{Historical Math60 composite (NOT a current theorem)}

\begin{remark}[The following theorem statement is preserved as a
historical artefact and is NOT a current canonical claim]
\label{rmk:historical}
The text below reproduces the Math60-era Stage-2 composite statement
verbatim. It was correct as a packaging proposal at the
2026-04 canonical tier but has been \emph{superseded} by the
GAP-1/2/3/4 verdict-shell decomposition of Math307 / Math310 /
Math311. Promoting this statement to a current canonical claim is
forbidden by the Math314-AddD audit and by the canonical-source
hierarchy (the internal canonical-source hierarchy). External use is FORBIDDEN at the present
canonical tier.
\end{remark}

\paragraph{Historical Math60 composite (verbatim, 2026-04 packaging,
NOT current canonical).}
The Math60-era proposal defined the TECT global qualification
predicate as the conjunction
\[
  S_2^{\,\text{Math60-era}} \;:=\; \mathrm{M60\text{-}A}
  \wedge \mathrm{M60\text{-}B} \wedge \mathrm{M60\text{-}C}
  \wedge \mathrm{M60\text{-}D} \wedge \mathrm{M60\text{-}E},
\]
where:
\begin{enumerate}
\item {\bf M60-A (Meta-consistency)}: The 11-pillar decomposition
  admits a pairwise-commutativity diagram showing no logical cycles or
  circularity under the BCC condensate assumption~\cite{Math60A}.
  Status: T6 PROVED CONDITIONAL.

\item {\bf M60-B (Parameter compression)}: The TECT effective axiom
  count $N_{\rm axiom}$ reduces from 3 independent postulates to
  $2 + 1_{\rm cosmological}$ under the Meta-consistency diagram.
  Compression ratio $\rho_{\rm compression} = 4.75 \times$ quantifies the
  redundancy elimination. Status: T6 PROVED CONDITIONAL.

\item {\bf M60-C (Quantum observables)}: Three canonical quantum
  observables (QO1, QO2, QO3) are uniquely determined by the classical
  condensate structure, with closed-form extraction rules
  (Casimir operator, noise spectrum, form factor). Status: T4 STRONG EVIDENCE.

\item {\bf M60-D (Observable-map injectivity)}: The quantum-to-classical
  map from 5 quantum observables to a 9-dimensional classical observable
  vector is globally injective. The Jacobian matrix is $5 \times 9$ with
  full column rank (rank = 5). Status: T6 PROVED CONDITIONAL.

\item {\bf M60-E (Falsifiability)}: Four independent falsification gates
  (F1, F2, F3, F4) bind quantum predictions to classical cosmological
  observations. Status: T3 PROOF SKETCH (gates marked, closure pending).
\end{enumerate}
The Math60-era composite is a T3 \textsc{proof sketch}. The
2026-04 packaging then conjectured that, under (H1) Pillars 1--9
being individually closed or \textsc{strong-evidence}, and
(H2) the five sub-theorems being independently verified, TECT would
be ``mathematically self-consistent and falsifiable''.

\paragraph{Status of the Math60 composite under the current
canonical bookkeeping.}
Under the current Math270--Math313 verdict-shell architecture, the
Math60 composite is replaced by the GAP-1/2/3/4 conjunction. The
correspondences are
\[
  \mathrm{M60\text{-}A,B}\;\longleftrightarrow\;\text{GAP-2,3 (T6 each)},
  \quad
  \mathrm{M60\text{-}C,D}\;\longleftrightarrow\;\text{GAP-1 (T4)},
  \quad
  \mathrm{M60\text{-}E}\;\longleftrightarrow\;\text{GAP-4 (T3)}.
\]
The current canonical Stage-2 composite is therefore $\min(T6,T6,T4,T3) = T3$,
matching the Math60-era $T3$ verdict but for a structurally different
reason (the limiting tier is now driven by GAP-4 falsifiability
package readiness and by the GAP-1 verdict-shell consumption). The
Math60-era ``H2: five sub-theorems independently verified'' clause
is replaced by the verdict-shell joint event
$(C_1 \wedge C_2 \wedge C_3) \wedge (\text{F-GAP4} = \text{PASS})$.

\section{Historical record: Math60 sub-theorem proof-sketches
(verbatim, NOT current canonical)}\label{sec:proof-sketches}
% =====================================================================

\textbf{Historical record.} The five proof-sketches below reproduce
the Math60-era arguments. They are NOT re-audited against the
current canonical Math270--Math313 archive; the reader should consult
the canonical Math notes for the current state of each claim.

\paragraph{Step 1 (Meta-consistency diagram, M60-A historical).}
\cite{Math60A} constructs an explicit pairwise-commutativity diagram among
the 11 pillars, showing that derivations taken in different orders reach
the same conclusion. No logical cycles are found. The diagram is closed
at T6 (rigorous proof with explicit hypothesis set).

\paragraph{Step 2 (Parameter compression, M60-B historical).}
\cite{Math60B} analyzes the axiom dependencies and identifies that A2
(the ultra-high-energy initial state) is partially derivable from A0
(BCC Brazovskii dynamics) + A1 (TDGL kinetics) given the cosmological
cooling curve $T(t)$. Thus, the irreducible axiom count is 2 core + 1
cosmological boundary condition. Compression ratio = 4.75×. Status: T6.

\paragraph{Step 3 (Quantum observables closure, M60-C historical).}
\cite{Math60C, Math60CAddA, Math60CAddB, Math60CAddC} derives three
canonical quantum observables (QO1 = Casimir, QO2 = noise spectrum,
QO3 = form factor) with closed-form extraction rules from the classical
condensate solution. QO1 and QO2 are analytically closed at T4 level.
QO3 includes a numerical-anchor term. Status: T4 STRONG EVIDENCE.

\paragraph{Step 4 (Observable-map injectivity, M60-D historical).}
\cite{Math60D, Math60DAddB, Math60DAddC} proves that the map from
5 quantum observables to a 9-dimensional vector of classical cosmological
observables is globally injective. The Jacobian is $5 \times 9$ with
analytically verified column rank = 5. Status: T6 PROVED CONDITIONAL.

\paragraph{Step 5 (Falsifiability gates, M60-E historical).}
\cite{Math60E} defines four falsification gates F1--F4 that bind
quantum predictions to classical observables. Each gate has a
pre-registered closure deadline and acceptance criterion. The gates
were marked T3 (proof sketch level) at the 2026-04 canonical tier;
closure awaits empirical testing or theoretical verification.
Under the current canonical bookkeeping these gates are subsumed by
the GAP-4 falsifiability package, whose composite tier is T3.

% =====================================================================
\section{Historical sub-theorem status summary
(2026-04 era; NOT current canonical)}\label{sec:status-table}
% =====================================================================

\textbf{Historical record.} The table below records the
2026-04 era Math60 sub-theorem tiers verbatim. The current canonical
tiers are recorded in
\texttt{Docs/status/TOE-FACT-SHEET.md} and the canonical Math notes;
they may differ.

\begin{table}[h]
\centering
\begin{tabular}{llcc}
\hline
Sub-theorem & Title & Historical (2026-04) & Evidence (historical) \\
\hline
M60-A & Meta-consistency               & T6 & Explicit pairwise diagram \\
M60-B & Parameter compression          & T6 & Axiom dependence analysis \\
M60-C & Quantum observables            & T4 & Analytical + numerical anchor \\
M60-D & Observable-map injectivity     & T6 & Jacobian rank verification \\
M60-E & Falsifiability gates           & T3 & Gates marked; closure pending \\
\hline
\multicolumn{4}{c}{Historical Math60-era composite $S_2^{\,\text{Math60-era}}$: T3 \textsc{proof sketch}} \\
\hline
\end{tabular}
\caption{Historical Math60-era sub-theorem status summary
(2026-04 packaging). The corresponding current canonical
GAP-1/2/3/4 composite is $\min(T6,T6,T4,T3) = T3$ per Math307 /
Math310.}
\end{table}

\subsection{Historical open gates and deadlines (2026-04 era)}

\begin{itemize}
\item F-GAP2 (M60-E §3.2): Quantum--classical correspondence gate
  (historical deadline: 2026-05-22).
\item F-GAP3 (M60-E §3.3): Cosmological-observable consistency
  (historical deadline: 2026-05-29).
\item F-GAP4 (M60-E §3.4): Falsifiability package closure
  (historical deadline: 2026-06-05).
\end{itemize}
For the current canonical state of these gates, consult
\texttt{Docs/status/OPEN-QUESTIONS.md} and the canonical Math3xx
verdict-shell archives.

% =====================================================================
\section{Discussion --- historical artefact, NOT a current canonical
Stage-2 verdict}\label{sec:discussion}
% =====================================================================

The Math60-era Stage-2 packaging recorded above represented the
2026-04 best-effort synthesis of the TECT internal-architecture
audits. It is preserved here as a chronological artefact; it is
\emph{not} a current canonical Stage-2 verdict and \emph{must not}
be cited as such. The current canonical Stage-2 composite tier is
\textbf{T3 \textsc{proof sketch}}, with the limiting tier driven by
GAP-1 (T4) verdict-shell consumption (Math299 / Math312) and by
GAP-4 (T3) falsifiability-package readiness (Math311 / Math313).
Promotion to T6 \textsc{proved conditional} requires the joint event
$(C_1 \wedge C_2 \wedge C_3) \wedge (\text{F-GAP4} = \text{PASS})$.

External use of this paper is FORBIDDEN per the Math314-AddD audit.
A future canonical Stage-2 closure paper will replace the present
historical record once the joint-event verdict is consumed.

% =====================================================================
\begin{acknowledgments}
The author thanks the Anthropic Claude Opus 4.7 collaborator for
comprehensive devil's-advocate auditing during the Stage-2 synthesis.
This work is part of TECT, canonical archive at
\url{https://github.com/TECT-OpenPhysics/TECT}.
\end{acknowledgments}

% =====================================================================
\bibliographystyle{apsrev4-2}
\bibliography{../_shared/tect-references}
% =====================================================================

\end{document}
