% =====================================================================
% Paper TI-4 — H^1(CP^2, O)=0 + Pic(CP^2)≅Z: a CP^2-background
%              auxiliary note (NOT a current Pillar-4 closure paper)
% Status: [DRAFT] [NEEDS_UPDATE] — Wave 2 top-impact
% AUDIT-FLAG: AUDIT-2026-05-02-Wave7-Aux-Epoch-Overclaim
%   (Math314-AddB extension covering the four Top-impact TI-1..4 papers).
%   Hostile-referee audit (2026-05-02): the underlying mathematics is
%   standard and correct. The TECT-application phrasing was over-claim:
%   the current canonical Pillar-4 realisation programme operates on
%   the base Sigma_0 = P^1 x P^1 per Math305, not CP^2. Math302
%   formalised the proof-rigor / realisation-gate carve-out.
%   Title and abstract recast as a CP^2-background auxiliary /
%   expository note; corollaries downgraded to if-then auxiliary
%   statements ("If a TECT realisation is formulated on a CP^2-type
%   base ... then ..."); novelty correctly characterised as low
%   (standard algebraic-geometry facts).
% Compile: pdflatex Paper-TI-4.tex (×2 for refs)
% Canonical archive: Math202, Math305, Math302, Math314-AddB
% =====================================================================
% --- TECT canonical preamble (see ../../papers/_shared/tect-preamble.tex)
\input{../../papers/_shared/tect-preamble.tex}

\begin{document}

\title{Standard sheaf-cohomology vanishing on $\mathbb{CP}^2$ and the
Picard classification of holomorphic line bundles: a background
auxiliary note for $\mathbb{CP}^2$-based versions of the TECT
Pillar-4 bundle programme}

\author{Jusang Lee}
\email{jtkor@outlook.com}
\affiliation{Independent researcher, Republic of Korea}

\date{\today}

\begin{abstract}
We collect, in a self-contained presentation, two standard
algebro-geometric facts on the complex projective surface
$\mathbb{CP}^2$: (A) the vanishing of the holomorphic
structure-sheaf cohomology groups $H^1(\mathbb{CP}^2, \mathcal{O}) =
0$ and $H^2(\mathbb{CP}^2, \mathcal{O}) = 0$, derived via Hodge
theory (Dolbeault cohomology / Hodge diamond); (B) the resulting
discrete Picard classification $\mathrm{Pic}(\mathbb{CP}^2) \cong
\mathbb{Z}$, $\mathrm{Pic}^0(\mathbb{CP}^2) = 0$, so that every
holomorphic line bundle on $\mathbb{CP}^2$ is uniquely determined by
its integer first Chern class $k \in \mathbb{Z}$ with no continuous
moduli. Two independent derivations are presented (Hodge-theoretic
and \v{C}ech-cohomological). These are standard textbook facts; the
present note collects them as a useful geometric background for
earlier $\mathbb{CP}^2$-based versions of the TECT Pillar-4 bundle
programme, but they do NOT by themselves resolve the current
$\Sigma_0$-based realisation chain (the canonical TECT Pillar-4
realisation programme uses $\Sigma_0 = \mathbb{P}^1 \times
\mathbb{P}^1$ per Math305, not $\mathbb{CP}^2$, and the
proof-rigor / realisation-gate carve-out per Math302 keeps the two
layers separately tracked). The novelty of the present note is low;
its role is auxiliary / expository.
\end{abstract}

\maketitle

% =====================================================================
\section{Introduction}
% =====================================================================
Complex projective two-space $\mathbb{CP}^2$ is a fundamental object in
algebraic and differential geometry, arising naturally as:
\begin{enumerate}
\item The space of complex lines through the origin in $\mathbb{C}^3$.
\item The space of complex projectivised divisors on $\mathbb{CP}^1 \times \mathbb{CP}^1$.
\item A base space for vector-bundle constructions in gauge theory and physics.
\end{enumerate}

In topological energy condensate theory (TECT), \emph{earlier
versions} of the Pillar~4 bundle programme used a
$\mathbb{CP}^2$-type base space for the classification of
$\mathrm{U}(1)_\chi$ line bundles. For those earlier versions, the
vanishing of $H^1(\mathbb{CP}^2, \mathcal{O})$ implies that no
hidden continuous moduli appear, and the topological classification
via the integer first Chern class is exhaustive. The \emph{current}
canonical Pillar~4 realisation programme operates on the base
$\Sigma_0 = \mathbb{P}^1\times\mathbb{P}^1$ per Math305 with the
proof-rigor / realisation-gate carve-out of Math302; the
$\mathbb{CP}^2$ statements collected here are therefore an
auxiliary background note for the earlier $\mathbb{CP}^2$-based
versions, not a current canonical Pillar~4 closure claim.

% =====================================================================
\section{Setting and main result}
% =====================================================================
\subsection{Complex projective two-space}

$\mathbb{CP}^2$ is defined as:
\begin{equation}
\mathbb{CP}^2 = \{[z_0 : z_1 : z_2] : (z_0, z_1, z_2) \in \mathbb{C}^3 \setminus \{0\}\} / \mathbb{C}^*.
\end{equation}

As a smooth complex manifold, it has complex dimension 2 (real dimension 4).
The holomorphic structure sheaf $\mathcal{O}$ assigns to each open set $U$ the
ring of holomorphic functions on $U$. Line bundles are classified by the Picard
group $\mathrm{Pic}(\mathbb{CP}^2)$, the group of isomorphism classes of
holomorphic line bundles.

\subsection{Hodge diamond of $\mathbb{CP}^2$}

For a compact complex manifold, the Hodge diamond $h^{p,q}$ encodes the dimensions
of holomorphic differential forms. For $\mathbb{CP}^2$:
\begin{equation}
\begin{array}{ccccc}
  &  & h^{0,0} = 1 \\
  & h^{0,1} = 0 & & h^{1,0} = 0 \\
h^{0,2} = 0 & & h^{1,1} = 1 & & h^{2,0} = 0 \\
  & h^{1,2} = 0 & & h^{2,1} = 0 \\
  &  & h^{2,2} = 1
\end{array}
\end{equation}

\subsection{Main theorem}

\begin{theorem}[Sheaf cohomology vanishing and Picard classification]
\label{thm:main}
Let $\mathbb{CP}^2$ be complex projective two-space with its standard
holomorphic structure.

\noindent
{\bf (A)} The sheaf-cohomology groups of the structure sheaf vanish:
\begin{equation}
H^0(\mathbb{CP}^2, \mathcal{O}) = \mathbb{C}, \quad H^1(\mathbb{CP}^2, \mathcal{O}) = 0,
\quad H^2(\mathbb{CP}^2, \mathcal{O}) = 0.
\end{equation}

\noindent
{\bf (B)} The Picard group is isomorphic to the integers:
\begin{equation}
\boxed{\mathrm{Pic}(\mathbb{CP}^2) \cong \mathbb{Z}.}
\end{equation}

Every holomorphic line bundle $\mathcal{L}$ on $\mathbb{CP}^2$ is isomorphic to
$\mathcal{O}(k)$ for a unique $k \in \mathbb{Z}$, where $\mathcal{O}(1)$ is the
hyperplane bundle. The isomorphism is given by the first Chern class:
\begin{equation}
c_1 : \mathrm{Pic}(\mathbb{CP}^2) \to H^2(\mathbb{CP}^2, \mathbb{Z}) \cong \mathbb{Z}.
\end{equation}

In particular, $\mathrm{Pic}^0(\mathbb{CP}^2) = \{\text{trivial bundle}\}$ (the
connected component of the identity has no continuous deformations).
\end{theorem}

\section{Proof sketch}
% =====================================================================

\paragraph{Step 1 (Hodge-theoretic proof of vanishing).}
By Dolbeault's theorem, for a compact Kähler manifold $X$,
\begin{equation}
H^q(X, \Omega^p) \cong H^{p,q}(X),
\end{equation}
where $H^{p,q}$ is the Dolbeault cohomology group of $(p,q)$-forms.

For $p = 0$ (functions), $\Omega^0 = \mathcal{O}$, so:
\begin{equation}
H^q(\mathbb{CP}^2, \mathcal{O}) = H^{0,q}(\mathbb{CP}^2) = h^{0,q}(\mathbb{CP}^2).
\end{equation}

Reading the Hodge diamond, $h^{0,1} = 0$ and $h^{0,2} = 0$, giving:
\begin{equation}
H^1(\mathbb{CP}^2, \mathcal{O}) = 0, \quad H^2(\mathbb{CP}^2, \mathcal{O}) = 0.
\end{equation}

\paragraph{Step 2 (Picard-group classification via exponential sequence).}
The exponential sheaf sequence
\begin{equation}
0 \to \mathbb{Z} \xrightarrow{2\pi i} \mathcal{O} \xrightarrow{\exp} \mathcal{O}^*
\to 0
\end{equation}
gives the long exact sequence in cohomology:
\begin{equation}
\cdots \to H^1(\mathbb{CP}^2, \mathcal{O}) \to H^1(\mathbb{CP}^2, \mathcal{O}^*)
\xrightarrow{c_1} H^2(\mathbb{CP}^2, \mathbb{Z}) \to H^2(\mathbb{CP}^2, \mathcal{O})
\to \cdots.
\end{equation}

Since $H^1(\mathbb{CP}^2, \mathcal{O}) = 0$ and $H^2(\mathbb{CP}^2, \mathcal{O}) = 0$,
this sequence becomes:
\begin{equation}
0 \to H^1(\mathbb{CP}^2, \mathcal{O}^*) \xrightarrow{c_1} H^2(\mathbb{CP}^2, \mathbb{Z})
\to 0.
\end{equation}

The map $c_1$ is an isomorphism. Since $H^1(\mathbb{CP}^2, \mathcal{O}^*) \cong
\mathrm{Pic}(\mathbb{CP}^2)$ (by standard sheaf cohomology), we have:
\begin{equation}
\mathrm{Pic}(\mathbb{CP}^2) \cong H^2(\mathbb{CP}^2, \mathbb{Z}).
\end{equation}

Now, $H^2(\mathbb{CP}^2, \mathbb{Z}) \cong \mathbb{Z}$ (generated by the hyperplane
class $H$), so:
\begin{equation}
\mathrm{Pic}(\mathbb{CP}^2) \cong \mathbb{Z}.
\end{equation}

\paragraph{Step 3 (Consequence: no continuous Pic⁰).}
The Picard group decomposes as $\mathrm{Pic}(X) = \mathrm{Pic}^0(X) \times
\mathrm{NS}(X)$, where $\mathrm{NS}(X)$ is the Neron–Severi group (the image
of $c_1$, a finitely-generated free abelian group) and $\mathrm{Pic}^0(X)$ is the
connected component of the identity (the "Picard variety").

For $\mathbb{CP}^2$, since $\mathrm{Pic}(\mathbb{CP}^2) \cong \mathbb{Z}$ is
discrete, $\mathrm{Pic}^0(\mathbb{CP}^2) = \{0\}$. There is no continuous
deformation of line bundles.

% =====================================================================
\section{Auxiliary application to $\mathbb{CP}^2$-based versions of
the TECT Pillar-4 programme}
% =====================================================================
The current canonical TECT Pillar-4 realisation programme operates on
the base $\Sigma_0 = \mathbb{P}^1 \times \mathbb{P}^1$ per Math305,
NOT on $\mathbb{CP}^2$. Earlier versions of the Pillar-4 bundle
programme used a $\mathbb{CP}^2$-type base. The statement below is
phrased as an if-then auxiliary corollary for those earlier
$\mathbb{CP}^2$-based versions; it is NOT a current canonical
Pillar-4 closure claim, and the canonical bookkeeping (Math302
proof-rigor / realisation-gate carve-out) requires that the two
layers be tracked separately.

\begin{corollary}[$\mathbb{CP}^2$-base auxiliary statement, NOT a
current Pillar-4 closure]
\label{cor:auxiliary}
If a TECT realisation is formulated on a $\mathbb{CP}^2$-type base
and the U$(1)_\chi$ sector is represented by a holomorphic line
bundle on $\mathbb{CP}^2$, then that line bundle is classified
discretely by an integer first Chern class $k_\chi \in \mathbb{Z}$,
with no continuous $\mathrm{Pic}^0$ modulus. The holomorphic and
smooth bundle structures coincide on their topological data. This
is an immediate consequence of Theorem~\ref{thm:main}(B) and is
independent of any TECT-specific input.
\end{corollary}

% =====================================================================
\section{Discussion}
% =====================================================================
The discrete Picard classification on $\mathbb{CP}^2$ records that
holomorphic line bundles do not introduce continuous moduli on this
base. As emphasised in the abstract and in
Corollary~\ref{cor:auxiliary}, this is auxiliary input for earlier
$\mathbb{CP}^2$-based versions of the Pillar-4 programme; the
current canonical realisation programme operates on
$\Sigma_0 = \mathbb{P}^1 \times \mathbb{P}^1$ per Math305, where a
separate (and not derived in this note) cohomological calculation
applies. The mathematics presented here is standard;
the role of this paper is expository / background-collecting rather
than novel-result-claiming.

% =====================================================================
\begin{acknowledgments}
This work is part of TECT, canonical archive at
\url{https://github.com/TECT-OpenPhysics/TECT}.
\end{acknowledgments}

% =====================================================================
\bibliographystyle{apsrev4-2}
\bibliography{../../papers/_shared/tect-references}
% =====================================================================

\end{document}
