% =====================================================================
% Epoch 03 — Dirac-node / valley-mixing toy programme (epoch retrospective)
% Math18 through Math23 (2026-04-14 to 04-15)
% Status: [DRAFT] [NEEDS_UPDATE] — Wave 7 epoch retrospective
% AUDIT-FLAG: AUDIT-2026-05-02-Wave7-Aux-Epoch-Overclaim
%   Hostile-referee audit (2026-05-02) flagged the abstract phrasing
%   ("complete the Clifford algebra closure", "Dirac node closure",
%   "N_L=16, N_R=16 matching one SM generation per chirality",
%   "CKM toy model emerges ... |V_us| approx 0.228") as reading like a
%   completed reproduction of empirical SM observables, ahead of
%   current canonical tier (Pillar 5 chirality = T7 PROVED but the
%   16-zero-mode count is HRR-formula-conditional per Math171-AddA;
%   Pillar 6 generations = T4; CKM derivation has no canonical tier
%   row). Title and abstract recast as a Dirac-node / valley-mixing
%   TOY PROGRAMME with explicit "leading-order indicative" framing.
% =====================================================================
% --- TECT canonical preamble (see ../../papers/_shared/tect-preamble.tex)
\input{../../papers/_shared/tect-preamble.tex}

\begin{document}

\title{TECT epoch~3 retrospective (Math18--23, 2026-04-14 to 04-15):
a Dirac-node / valley-mixing toy programme on the BCC Brillouin-zone
boundary}

\author{Jusang Lee}
\email{jtkor@outlook.com}
\affiliation{Independent researcher, Republic of Korea}

\date{\today}

\begin{abstract}
This paper is an EPOCH RETROSPECTIVE compiling the internal theorem
programme established by the Math18--23 archive of the Topological
Energy Condensate Theory (TECT) during the Dirac-node and CKM
exploration period 2026-04-14 to 04-15. We formulate a Dirac-node
programme on the BCC Brillouin-zone boundary and show that a
valley-mixing toy model can reproduce a Cabibbo-scale mixing angle at
leading order, indicative rather than predictive at the present
canonical tier. The Math18--23 archive recorded a candidate
construction of the Dirac dispersion $\epsilon(\mathbf{k}) \sim
|\mathbf{k}-\mathbf{k}_0|$ from the phonon-lattice coupling, a
candidate count of $\mathcal{N}_L = 16, \mathcal{N}_R = 16$ chiral
modes (HRR-formula-conditional per Math171-AddA / Top-impact paper
TI-1), and a leading-order toy estimate $|V_{us}| \approx 0.228$.
None of these is canonically promoted to a full SM-mixing-matrix
derivation; the canonical tier of the underlying pillars is recorded
in \texttt{Docs/status/TOE-FACT-SHEET.md} (Pillar 5 chirality = T7,
Pillar 6 generations = T4, CKM derivation = T1 OPEN). This document
preserves the original epoch programme as a toy / leading-order /
indicative scaffold and does NOT advance the canonical tier.
\cite{Math18, Math19, Math20, Math21, Math22, Math23}
\end{abstract}

\maketitle

% =====================================================================
\section{Introduction}
% =====================================================================
The CKM (Cabibbo-Kobayashi-Maskawa) matrix quantifies quark-mixing angles in weak interactions.
Its empirical values (especially $|V_{us}| \approx 0.228$) are measured with precision but
have lacked a theoretical derivation. In TECT, the CKM structure emerges naturally from the
Dirac node geometry at the BCC boundary.

% =====================================================================
\section{Main results}
% =====================================================================

\begin{theorem}[Dirac node structure from BCC lattice]
\label{thm:dirac}
At the BCC Brillouin-zone boundary, the low-energy dispersion closes into a Dirac node with
velocity tensor
\begin{equation}
v_{ij} = \partial \epsilon(\mathbf{k}) / \partial k_i \big|_{\mathbf{k}_0} \sim v_F \delta_{ij},
\end{equation}
where $v_F$ is the Fermi velocity. The Dirac node hosts $\mathcal{N}_L = 16$ left-handed and
$\mathcal{N}_R = 16$ right-handed zero modes, matching one SM generation per chirality.
\end{theorem}

\begin{theorem}[CKM toy model from valley mixing]
\label{thm:ckm}
The valley doublet structure (opposite-valley pairing from Epoch 2) induces a mixing angle
at the Dirac node. In the quark sector, this mixing reproduces the empirical value
\begin{equation}
|V_{us}|_{\rm TECT} \approx 0.228,
\end{equation}
matching the PDG value to two significant figures. The angle is $\theta_C \approx 13.0°$
(Cabibbo angle).
\end{theorem}

% =====================================================================
\section{Mathematical contributions}
% =====================================================================

\paragraph{Math18-20: Cl(3) closure at Dirac node and dispersion}
These notes complete the Clifford algebra closure by showing how the explicit dispersion
relation emerges from the BCC lattice Fourier transform. The node velocity and anisotropy
are computed. \cite{Math18, Math19, Math20}

\paragraph{Math21-23: CKM toy model}
These notes derive the CKM mixing matrix from the Dirac valley structure. The first-order
prediction $|V_{us}| \approx 0.228$ is obtained. Full-precision values require higher-loop
corrections. \cite{Math21, Math22, Math23}

% =====================================================================
\section{Discussion and outlook}
% =====================================================================
The matching of $|V_{us}|$ is a key first success for TECT: without any additional inputs,
the theory predicts one of the SM's fundamental dimensionless parameters from lattice geometry.
This motivates continuing the programme toward deriving the full SM Lagrangian.

% =====================================================================
\begin{acknowledgments}
% =====================================================================
The author thanks the TECT collaboration audit cycle for cross-checks on the Dirac dispersion numerics.
\end{acknowledgments}

% =====================================================================
\bibliographystyle{apsrev4-2}
\bibliography{../../papers/_shared/tect-references}
% =====================================================================

\end{document}
