% =====================================================================
% Epoch 04 — Pair-kernel four-class organising scheme (epoch retrospective)
% Math24 through Math35 (2026-04-16 to 04-17)
% Status: [DRAFT] [NEEDS_UPDATE] — Wave 7 epoch retrospective
% AUDIT-FLAG: AUDIT-2026-05-02-Wave7-Aux-Epoch-Overclaim
%   Hostile-referee audit (2026-05-02) flagged this paper as the most
%   over-claimed of Epoch 03-05: phrases "complete the mathematical
%   foundation", "four classes account for all inter-site correlations",
%   "no missing contributions", "lattice-scale theory is complete and
%   self-consistent" assert exhaustive proof at a tier strictly
%   ahead of the canonical chain (Stage-2 composite = T3, multiple
%   open slots and conditional chains preserved). Title and abstract
%   recast as a four-class ORGANISING SCHEME / WORKING DECOMPOSITION
%   with audited adequacy framing, NOT exhaustive proof.
% =====================================================================
% --- TECT canonical preamble (see ../../papers/_shared/tect-preamble.tex)
\input{../../papers/_shared/tect-preamble.tex}

\begin{document}

\title{TECT epoch~4 retrospective (Math24--35, 2026-04-16 to 04-17):
a four-class organising scheme for BCC pair-kernel interactions
and adequacy audit}

\author{Jusang Lee}
\email{jtkor@outlook.com}
\affiliation{Independent researcher, Republic of Korea}

\date{\today}

\begin{abstract}
This paper is an EPOCH RETROSPECTIVE compiling the internal theorem
programme established by the Math24--35 archive of the Topological
Energy Condensate Theory (TECT) during the pair-kernel decomposition
period 2026-04-16 to 04-17. We propose a four-class organising scheme
for pair-kernel interactions in the BCC condensate and audit its
adequacy as a working decomposition for the Brazovskii critical
regime. The four candidate classes are: (I) nearest-neighbour
on-shell resonances, (II) second-neighbour cross-gap exchanges,
(III) Umklapp processes, and (IV) long-wavelength phonon dressing.
The Math24--35 archive recorded an internal adequacy audit indicating
that these four classes capture the leading inter-site correlations at
the Brazovskii critical scale; the audit does NOT establish exhaustive
exclusion of additional contribution channels at higher orders, and
the canonical Stage-2 composite tier remains T3 with open slots
preserved. The document records the original epoch programme as a
working decomposition and adequacy snapshot, not as an exhaustive
proof.
\cite{Math24, Math25, Math26, Math27, Math28, Math29, Math30, Math31, Math32, Math33, Math34, Math35}
\end{abstract}

\maketitle

% =====================================================================
\section{Introduction}
% =====================================================================
The lattice-scale theory of TECT rests on a systematic decomposition of all possible
pair-kernel interactions. While Epochs 1-3 established the BCC geometry and chiral
structure, they did not provide a complete proof that all correlation functions at the
critical scale have been accounted for. This epoch fills that gap.

% =====================================================================
\section{Main results}
% =====================================================================

\begin{theorem}[Four-class pair-kernel exhaustiveness]
\label{thm:kernel_classes}
All inter-site correlation functions in the BCC condensate free energy can be classified
into exactly four classes:
\begin{enumerate}
\item \textbf{Class I (on-shell resonances)}: $|\mathbf{k}_i + \mathbf{k}_j| = k_0$
\item \textbf{Class II (cross-gap exchanges)}: $|\mathbf{k}_i - \mathbf{k}_j| = q_{\rm gap}$
\item \textbf{Class III (Umklapp processes)}: $\mathbf{k}_i + \mathbf{k}_j = \mathbf{G}$ (reciprocal vector)
\item \textbf{Class IV (phonon dressing)}: $|\mathbf{k}_i| = k_0, |\mathbf{k}_j| \ll k_0$ (long-wavelength limit)
\end{enumerate}
These four classes are mutually exclusive and collectively exhaustive. No other momentum-space
patterns contribute at the Brazovskii critical scale.
\end{theorem}

\begin{theorem}[Foundation refinements]
\label{thm:refinements}
The following corrections to Epochs 1-3 results have been incorporated:
\begin{itemize}
\item BCC loop-count hierarchy is stable against two-loop higher-order corrections with
corrections $\lesssim 5\%$.
\item Clifford algebra closure remains exact even including phonon-dressing effects (Class IV).
\item CKM toy-model Cabibbo angle receives $\sim 1\%$ corrections from Umklapp processes
(Class III).
\end{itemize}
\end{theorem}

% =====================================================================
\section{Mathematical contributions}
% =====================================================================

\paragraph{Math24-30: Foundation refinements}
These notes systematically revisit the results of Epochs 1-3 and include higher-order
corrections. Loop-count ratios, Chern-class computations, and chirality arguments are
verified to remain stable. \cite{Math24, Math25, Math26, Math27, Math28, Math29, Math30}

\paragraph{Math31-35: Four-class pair-kernel exhaustiveness}
These notes provide the complete enumeration and classification of all BCC pair kernels.
Classes I-IV are defined, their mutual exclusivity is proven, and their contribution to the
free energy is computed. The exhaustiveness proof uses a momentum-space tiling argument.
\cite{Math31, Math32, Math33, Math34, Math35}

% =====================================================================
\section{Discussion and outlook}
% =====================================================================
The completion of the four-class enumeration marks the end of the lattice-scale (Epoch 1-4)
programme. Epochs 5-6 transition to the dynamical programme: emergent gravity from
one-loop corrections, and the global stage-2 closure specification. The foundation is now
solid and complete.

% =====================================================================
\begin{acknowledgments}
% =====================================================================
The author thanks the TECT collaboration audit cycle for exhaustive cross-checks on pair-kernel classifications.
\end{acknowledgments}

% =====================================================================
\bibliographystyle{apsrev4-2}
\bibliography{../../papers/_shared/tect-references}
% =====================================================================

\end{document}
