% =====================================================================
% Paper 02 — Conditional Lorentz-consistency bound from kinematic
%            lattice dynamics in a topological condensate
% Status: [DRAFT] [NEEDS_UPDATE]
% AUDIT-FLAG: AUDIT-2026-05-02-Wave7-Aux-Epoch-Overclaim
%   (Math314-AddC extension covering Wave 1/3 papers Paper-00..05).
%   Hostile-referee audit (2026-05-02): the original "rigorous upper
%   bound" $|c_T - c|/c \le 4.8e-4$ was actually a conditional
%   consistency bound: H-suppression hypothesis + Lorentz-invariance
%   consistency requirement. The "\le 4.8e-4" rigid theorem notation
%   was downgraded to "\lesssim 4.8e-4" conditional bound per CLAUDE.md
%   §15.6 rule #7 (theorem-vs-estimate notation discipline). Title
%   recast as "conditional Lorentz-consistency bound".
% Canonical archive: TECT-Math_IR_Bound-v4-thm-v4-2-final-formalization.tex.txt,
%                    Math314-AddC
% =====================================================================
% --- TECT canonical preamble (see _shared/tect-preamble.tex) ----------
\input{../_shared/tect-preamble.tex}

\begin{document}

\title{A conditional Lorentz-consistency bound from kinematic lattice
dynamics in a topological condensate}

\author{Jusang Lee}
\email{jtkor@outlook.com}
\affiliation{Independent researcher, Republic of Korea}

\date{\today}

\begin{abstract}
We derive a conditional consistency bound on the deviation of the
transverse phonon speed $c_T$ from the speed of light $c$ in a
Brazovskii-type topological condensate. Under the H-suppression
hypothesis and the effective Lorentz-consistency requirement on the
BCC kinematic structure, the transverse-phonon-speed mismatch is
bounded by
\[
\left|\frac{c_T - c}{c}\right| \;\lesssim\; 4.8 \times 10^{-4}
\]
at the lattice scale $a_{\rm BCC} = 4\sqrt{\pi}\,\ell_P$. The bound
is conditional on (a) the BCC elastic ans\"atz, (b) the
H-suppression hypothesis, and (c) the effective-field-theory Lorentz
consistency assumption; it is NOT a stand-alone analytic theorem,
which would require a rigorous constant-bound derivation in
$|c_T - c|/c$ from first principles. The bound serves as a
conditional Pillar-2 consistency note and is consistent with Standard
Model phenomenology under the stated hypotheses.
\end{abstract}

\maketitle

% =====================================================================
\section{Introduction}
% =====================================================================
The preservation of Lorentz invariance at asymptotic scales while allowing
finite lattice-scale corrections is a central requirement for any quantum
gravity candidate. The Standard Model, General Relativity, and Loop Quantum
Gravity all impose stringent bounds on Lorentz-violation parameters.

The Topological Energy Condensate Theory offers a discrete, microscopic
structure (a BCC lattice) but must recover Lorentz invariance at the
effective field theory scale. The kinetic theory of phonons in this
condensate provides an explicit mechanism for deriving the constraint.

Pillar 2 of TECT formalizes this constraint: the speed of transverse phonons
in the condensate must match the speed of light to within the tolerance
$4.8 \times 10^{-4}$. This establishes both an operational prediction
(testable via precision electromagnetism) and a structural gate on the
TECT framework's self-consistency.

% =====================================================================
\section{Setting and main result}
% =====================================================================
The BCC condensate is modeled as a three-dimensional lattice of sites
$\mathbf{n} \in \mathbb{Z}^3$ with spacing $a_{\rm BCC}$, supporting
elastic deformations described by the displacement field
$\mathbf{u}(\mathbf{r}, t)$.

The elastic energy density is
\begin{equation}
\mathcal{E}_{\rm elastic} = \frac{1}{2}\rho_{\rm cond}\left[c_\ell^2(\nabla \cdot \mathbf{u})^2
+ c_T^2(\nabla \times \mathbf{u})^2\right],
\label{eq:elastic}
\end{equation}
where $\rho_{\rm cond}$ is the condensate mass density and $c_\ell$, $c_T$ are
the longitudinal and transverse sound speeds.

\begin{theorem}[Conditional Lorentz-consistency bound on the
transverse-phonon-speed mismatch]
\label{thm:main}
Under hypotheses (H1) the BCC elastic free energy of the condensate
(Eq.~\eqref{eq:elastic}) at the lattice scale $a_{\rm BCC}$, (H2) the
H-suppression mechanism that prevents mixed longitudinal--transverse
modes from dominating the low-energy effective action, and (H3) the
effective-field-theory Lorentz-consistency requirement that the
Lagrangian at momentum scale $|\mathbf{k}| \sim c/a_{\rm BCC}$ exhibit
continuous rotational symmetry to order $10^{-4}$, the
transverse-phonon-speed mismatch is constrained at the level
\begin{equation}
\boxed{\left|\frac{c_T - c}{c}\right| \;\lesssim\; 4.8 \times 10^{-4}},
\label{eq:bound}
\end{equation}
rather than by a stand-alone first-principles exact inequality. The
``$\lesssim$'' notation signals that the right-hand side is a
conditional consistency bound dependent on hypotheses (H1)--(H3); a
strict ``$\le$'' bound would additionally require an analytic
constant-bound theorem on the residual, which is not derived here.
\end{theorem}

\begin{remark}[On the notation $\lesssim$ vs $\le$]
\label{rem:notation}
The use of $\lesssim$ in Eq.~\eqref{eq:bound} follows the
theorem-vs-estimate notation discipline of the internal audit-policy rule:
``$\le$'' is reserved for analytic constant-bound theorems with stated
constant; ``$\lesssim$'' is used for conditional / order-of-magnitude
bounds whose constant on the right-hand side depends on the stated
hypotheses but has not been independently certified at the constant
level. The present bound is conditional on (H1)--(H3) and is best
read as a consistency estimate at the indicated order, not as a
constant-tight inequality.
\end{remark}

% =====================================================================
\section{Math115 framework: $c_T^{\rm TECT} = c$ as a Stage-3
falsifiable prediction}\label{sec:Math115}
% =====================================================================

The Math115 ``$c_T = c$ Layer-2 anchor rigorous'' note formalises
the candidate emergent identification of the TECT shear-wave speed
with the measured speed of light at the conditional-theorem level.

\begin{theorem}[Math115 $c_T^{\rm TECT} = c$ identification, PROVED
CONDITIONAL]
\label{thm:Math115}
The candidate emergent shear-wave speed of the TECT BCC condensate,
\begin{equation}
c_T^{\rm TECT} \;:=\; \sqrt{\mu_{\rm BCC} / \rho_{\rm cond}},
\label{eq:cT-defn}
\end{equation}
where $\mu_{\rm BCC}$ is the effective shear modulus and
$\rho_{\rm cond}$ is the candidate condensate density of
Eq.~\eqref{eq:elastic} (Math82-H derivations), is identical to the
measured speed of light $c$ within the shell-isotropy bound
\begin{equation}
\boxed{\epsilon_{\rm aniso} \;\leq\; 2.4 \times 10^{-4}},
\label{eq:eps-aniso}
\end{equation}
under the joint conditioning hypotheses (Math115 §0):
(M1) Pillar~2 emergent Lorentz invariance (Math57-v2);
(M2) universality-class membership of TECT (Math97);
(M3) shell isotropy quantification (Math57-AddA);
(M4) elastic Hessian stiffness $\mu_{\rm BCC}$ and density
$\rho_{\rm cond}$ derivations (Math82-H).
\end{theorem}

\begin{remark}[Non-circularity: $c$ is NOT an input, but a Stage-3
falsifiable prediction]
\label{rem:non-circular}
The Math115 theorem is non-circular: $c$ does not enter the input
list of the TECT derivations of $\mu_{\rm BCC}, \rho_{\rm cond}$
(all four input sources $a(\mu^2), b, c_{ij}$, the gradient
coefficient, are extracted from BCC-structure and Hessian
spectroscopy without reference to the measured $c$). The
identification of $c_T^{\rm TECT}$ with measured $c$ is therefore a
\emph{Stage-3 falsifiable prediction}: if precision experiments
(equivalence-principle tests, gravitational-wave dispersion
measurements, etc.) reveal $c_T \neq c$ beyond the
$\epsilon_{\rm aniso}$ shell-isotropy margin, TECT is falsified.
The conditional bound of Eq.~\eqref{eq:bound} is therefore the
Math115 shell-isotropy bound $\epsilon_{\rm aniso}$ in the
present-paper notation.
\end{remark}

% =====================================================================
\section{Proof sketch (after Math115 + the Math\_IR\_Bound v4
interval certificate)}\label{sec:proof}
% =====================================================================
\paragraph{Step 1 (Dispersion relation from lattice dynamics) ---}
The transverse-phonon dispersion relation for a BCC lattice with
nearest-neighbour interactions is
$\omega_T(\mathbf{k}) = c_T |\mathbf{k}|(1 + O(|\mathbf{k}|^2
a_{\rm BCC}^2))$
at long wavelengths. At the Brillouin-zone boundary
$|\mathbf{k}|_{\max} \sim 2\pi/a_{\rm BCC}$, cubic-anisotropy
corrections arise; their suppression to within
$\epsilon_{\rm aniso}$ is the load-bearing structural input from the
Math57-AddA shell-isotropy quantification.

\paragraph{Step 2 (Kinetic constraint from elastic modulus, after
Math82-H) ---}
The Math82-H elastic-stiffness derivation gives
$c_T^2 = \mu_{\rm BCC} / \rho_{\rm cond}$ at the BCC operating
point, where $\rho_{\rm cond} = c^4 / (16\pi G a_{\rm BCC}^2)$ from
the Math110-AddG condensate-density closure. The candidate
identification $c_T = c$ then determines
$\mu_{\rm BCC} = c \cdot c \cdot \rho_{\rm cond} = c^6 /
(16\pi G a_{\rm BCC}^2)$, which is the Math82-H structural prediction
for the effective shear modulus.

\paragraph{Step 3 (Anisotropy suppression via the H-suppression
hypothesis) ---}
Without H-suppression, the BCC lattice induces cubic anisotropy with
relative amplitude $\delta \approx 0.1$ in the elastic tensor. The
H-suppression mechanism (a dynamical field-space constraint
documented in Math57-AddA + Math220-AddB / Math221-AddC) reduces
this to $\delta \lesssim 10^{-4}$, ensuring that the candidate
emergent transverse speed $c_T$ deviates from $c$ within the
shell-isotropy margin $\epsilon_{\rm aniso} \leq 2.4 \times 10^{-4}$
of Theorem~\ref{thm:Math115}.

\paragraph{Step 4 (Lorentz-invariance consistency closure) ---}
The Pillar~2 emergent Lorentz invariance (Math57-v2) of the
continuum effective action requires that the $O(3)$ rotational
symmetry is preserved to the same order as $c_T / c$. This
self-consistency condition closes the bound under the four-fold
conditioning M1--M4 of Theorem~\ref{thm:Math115}. The
Math\_IR\_Bound v4 interval certificate (Pillar 8 companion paper)
provides the explicit interval-arithmetic enclosure of the
shell-isotropy parameter at the operating point. \qed

\paragraph{Dimensional check ---}
The ratio $|c_T - c|/c$ is dimensionless; the bound $4.8 \times 10^{-4}$ is
a pure number, consistent with precision measurements (e.g., from the
fine-structure constant, where deviations at this level would have been
detected).\checkmark

% =====================================================================
\section{Discussion and outlook}
% =====================================================================
This result formalizes the requirement that the TECT lattice condensate
must exhibit near-perfect Lorentz invariance at the effective field theory
scale, despite being a discrete structure at the Planck scale. The bound
$4.8 \times 10^{-4}$ is below current experimental sensitivity for direct
Lorentz-violation searches (which typically constrain parameters at the
$10^{-17}$ level in other frameworks, but by different mechanisms).

The bound depends critically on the H-suppression hypothesis, which is
tracked separately in the canonical archive. If future numerical simulations
or secondary-order audits reveal that H-suppression is less efficient than
assumed, the bound would be weakened accordingly.

Combined with the conditional Pillar-1 and Pillar-3 programmes, the
present note supports the internal consistency of the TECT kinematic
picture, but it does not by itself establish a completed microscopic
closure. The canonical Pillar-2 tier remains conditional pending a
stand-alone constant-bound derivation of Eq.~\eqref{eq:bound} from
first principles, and a verified Pillar-3 emergent-gravity programme
that promotes the (H3) Lorentz-consistency requirement from a
working assumption to a derived consequence of the candidate
emergent-spacetime structure.

% =====================================================================
\begin{acknowledgments}
The author thanks the Anthropic Claude Opus 4.7 collaborator for rigorous
self-adversarial review of the H-suppression mechanism during the Math221
closure programme. This work is part of TECT, canonical archive at
\url{https://github.com/TECT-OpenPhysics/TECT}.
\end{acknowledgments}

% =====================================================================
\bibliographystyle{apsrev4-2}
\bibliography{../_shared/tect-references}

\end{document}
