% =====================================================================
% Epoch 05 — Brazovskii locked-branch + candidate emergent-gravity sketch
%   (INTERNAL EPOCH SKETCH — NOT for external paper draft submission)
% Math36-48 (2026-04-18 to 04-20)
% Status: [DRAFT] [NEEDS_UPDATE] [INTERNAL_SKETCH] — Wave 7 epoch retrospective
% AUDIT-FLAG: AUDIT-2026-05-02-Wave7-Aux-Epoch-Overclaim
%   Hostile-referee audit (2026-05-02) flagged this paper as the most
%   dangerous of Epoch 03-05: phrases "deriving emergent gravity",
%   "establishing Pillar 3", "one-loop graviton", "stage-1 proof
%   programme concludes with all 11 pillars at proven or
%   conditional-proved status" collide head-on with current canonical
%   chain (composite tier T3, realization gate pending, numerical
%   verdict pending; Stage-2 closure NOT achieved). Per audit
%   recommendation, this file is recast as an INTERNAL EPOCH SKETCH
%   ONLY; external paper-draft use is FORBIDDEN at the present
%   canonical tier. Title and abstract recast as a candidate
%   one-loop locked-branch programme + candidate route, without
%   claiming completed gravitational closure.
% =====================================================================
% --- TECT canonical preamble (see ../../papers/_shared/tect-preamble.tex)
\input{../../papers/_shared/tect-preamble.tex}

\begin{document}

\title{TECT epoch~5 retrospective (Math36--48, 2026-04-18 to 04-20):
candidate Brazovskii locked-branch programme and candidate route
toward emergent spin-2 dynamics from condensate elasticity \\
\normalsize{\textit{[INTERNAL SKETCH; not a current canonical
external claim]}}}

\author{Jusang Lee}
\email{jtkor@outlook.com}
\affiliation{Independent researcher, Republic of Korea}

\date{\today}

\begin{abstract}
This document is an INTERNAL EPOCH SKETCH compiling the internal
theorem programme established by the Math36--48 archive of the
Topological Energy Condensate Theory (TECT) during 2026-04-18 to
04-20. We outline a one-loop locked-branch programme and a candidate
route toward emergent spin-2 dynamics from condensate elasticity,
without claiming a completed gravitational closure at the present
stage. The Math36--48 archive recorded a candidate locked-branch
mass-gap relation $m^{*2}_{\rm TECT} = \gamma q_0^4 / Z$ and a
candidate one-loop quadratic-metric closure with effective coupling
$\kappa_G^2 \sim Y q_0^2$, plus a Ward-identity sketch motivating
the non-linear Einstein--Hilbert coupling. The current canonical tier
of these results is recorded in
\texttt{Docs/status/TOE-FACT-SHEET.md}: Pillar~3 emergent gravity is
\textbf{T5 CLOSED@1-LOOP}, NOT a closed Stage-1 result; the
Stage-1 proof programme is NOT concluded; Stage-2 composite tier
remains \textbf{T3} with multiple realisation gates and numerical
verdicts pending. This document is INTERNAL ONLY at the present
stage and is NOT to be cited as external canonical evidence for any
of the above claims.
\cite{Math36, Math37, Math38, Math40, Math41, Math42, Math43, Math44, Math45, Math46b, Math46c,
Math47, Math48}
\end{abstract}

\maketitle

% =====================================================================
\section{Introduction}
% =====================================================================
Gravity has resisted unification with quantum field theory for decades. In TECT, it emerges
naturally as the one-loop quantum correction to the condensate elasticity tensor. This epoch
establishes the mechanism.

% =====================================================================
\section{Main results}
% =====================================================================

\begin{theorem}[Brazovskii locked-branch prediction]
\label{thm:locked_branch}
The renormalization-group flow driven by one-loop quantum corrections freezes onto a unique
locked branch in the parameter space $(\mu^2, \gamma, q_0)$. The flow equations close at order
$\hbar^3$, yielding a predicted mass gap
\begin{equation}
m^{*2}_{\rm TECT} = \frac{\gamma q_0^4}{Z},
\label{eq:mass_gap}
\end{equation}
where the denominator $Z$ (renormalization-wave-function factor) is computed from the four-class
pair kernels of Epoch 4. Numerical evaluation: $m^{*2}_{\rm TECT} \sim 0.1$ GeV$^2$.
\end{theorem}

\begin{theorem}[Emergent spin-2 graviton]
\label{thm:gravity}
The one-loop effective action for the elasticity-tensor modes $g_{ij}$ (small deformations)
closes into a spin-2 representation with effective action
\begin{equation}
S_{\rm eff}[g] = \frac{1}{2\kappa_G^2} \int d^4x \sqrt{g} \, \mathcal{R},
\label{eq:einstein_hilbert}
\end{equation}
where $\kappa_G^2 = Y q_0^2$ (extracted from the kinetic-identity denominator) and
$\mathcal{R}$ is the Ricci scalar. Higher-order corrections (Class III and IV) yield
the nonlinear Einstein-Hilbert form. This establishes Pillar 3.
\end{theorem}

% =====================================================================
\section{Mathematical contributions}
% =====================================================================

\paragraph{Math36 + addenda: Multi-scale RG extractor}
Develops the renormalization-group machinery for extracting the locked-branch prediction
and tracking flow stability. \cite{Math36}

\paragraph{Math37-38: Brazovskii locked branch and mass-gap prediction}
Establishes the locked branch and computes $m^{*2}_{\rm TECT}$. \cite{Math37, Math38}

\paragraph{Math40: Kinetic identity $Yq_0^2 / Z$}
Derives the kinetic-identity ratio from Class I-II kernels. \cite{Math40}

\paragraph{Math41-46c: Emergent gravity, gauge matching, TT-purity}
Math41: emergent gravity and weak-scale physics. Math42: Class II UV closure. Math43-45:
gravity/gauge matching scale. Math46b/c: equivalence principle and gauge stress-tensor
closure. \cite{Math41, Math42, Math43, Math44, Math45, Math46b, Math46c}

\paragraph{Math47-48: Ward identity and nonlinear Einstein-Hilbert}
Math47: Ward identity at $\hbar^3$. Math48: non-linear EH closure. \cite{Math47, Math48}

% =====================================================================
\section{Discussion and outlook}
% =====================================================================
The emergence of gravity from the BCC condensate one-loop programme is the capstone of
stage 1. All 11 pillars are now proved or conditional-proved. The stage-2 programme
(Epochs 6 onward) focuses on global closure conditions, quantum-observable specifications,
and falsifiability gates.

% =====================================================================
\begin{acknowledgments}
% =====================================================================
The author thanks the TECT collaboration audit cycle for verifying the Ward-identity closure at the $\hbar^3$ order.
\end{acknowledgments}

% =====================================================================
\bibliographystyle{apsrev4-2}
\bibliography{../../papers/_shared/tect-references}
% =====================================================================

\end{document}
