% =====================================================================
% Paper 13 — GAP-1 independent one-loop programme note for hbar matching
%   (NOT a current GAP-1 closure paper; conditional / consistency draft)
% Status: [DRAFT] [NEEDS_UPDATE]
% AUDIT-FLAG: AUDIT-2026-05-02-Wave7-Aux-Epoch-Overclaim
%   (Math314-AddD extension covering Wave 1/4/5 papers Paper-09..16).
%   Hostile-referee audit (2026-05-02): direction OK (canonical Math291
%   formula presupposed; GAP-1 = T4 with T6 promotion gated by joint
%   event correctly stated). Wording calibration required:
%   "first-principles hbar running" / "matching to four-digit precision"
%   / "one-loop result is solid and secure" / "two independent routes
%   both yield hbar_obs to four-digit precision" too strong relative
%   to Math297 / Math312 verdict-shell pending. Recast as
%   "GAP-1 independent one-loop programme note". Beta-coefficient and
%   sign-convention sketch flagged for cleanup at next pass.
% Compile: pdflatex Paper-13.tex (×2 for refs)
% Canonical archive: Math200-AddC, Math296, Math297, Math298, Math299,
%                    Math312, Math314-AddD
% =====================================================================
% --- TECT canonical preamble (see _shared/tect-preamble.tex) ----------
\input{../_shared/tect-preamble.tex}

\begin{document}

\title{An independent one-loop programme note for GAP-1 $\hbar$
matching from the BCC condensate effective-action running}

\author{Jusang Lee}
\email{jtkor@outlook.com}
\affiliation{Independent researcher, Republic of Korea}

\date{\today}

\begin{abstract}
We present a candidate independent one-loop route for GAP-1
($\hbar$ matching) within the Topological Energy Condensate Theory
(TECT), orthogonal to the cosmic-origin structural derivation
(Paper 0 / Paper 10) which yields the canonical Math291 formula
$\hbar_{\rm TECT} = c^3 a_{\rm BCC}^2 / (16\pi G)$. The candidate
running function for the effective-action $\hbar$ from the Planck
scale to the electroweak scale is parameterised as
$\gamma_h^{(1)}(\mu) = \alpha_h^{(1)} \ln(\mu / M_Z)$ with the
candidate one-loop coefficient
$\alpha_h^{(1)} = (16\pi^2)^{-1} \sum_i b_i g_i^2(M_Z) \approx
-0.0706$. Numerical evaluation at $\mu = M_Z$ is consistent with
$\hbar_{\rm obs}$ at the percent level (the precise digit-by-digit
match depends on convention choices for $\beta$-function signs and
matching scheme that are not fully fixed in the present draft).

\textbf{Honest scope}: this paper is a programme / consistency
note, NOT a closure paper. The canonical GAP-1 composite tier
remains \textbf{T4 STRONG EVIDENCE} per Math299 / Math310; T6
promotion is gated by the joint event $C_1 \wedge C_2 \wedge C_3$
per Math299, with consumption shell scheduled in Math312. The
F-GAP1 falsification gate (deadline 2026-05-22) is pre-registered.
The $\beta$-function and sign-convention details require cleanup
before any precision claim beyond programme-level consistency.
\end{abstract}

\maketitle

% =====================================================================
\section{Introduction}
% =====================================================================
Paper 0 derives $\hbar$ via the cosmic-origin Kibble–Zurek mechanism,
achieving the structural tier. But a second, independent route is
necessary: the running of $\hbar$ from the Planck scale down to low
energies via quantum corrections. This paper provides that route.

The key insight is that the BCC defect spectrum generates a beta function
for $\hbar$, just as it does for the coupling constants. The one-loop
beta function is
\begin{equation}
\beta_\hbar \equiv \mu \frac{d\hbar}{d\mu} = \gamma_h(\mu) \hbar(\mu),
\end{equation}
with anomalous dimension $\gamma_h(\mu)$ computed from the defect spectrum
(Math296).

% =====================================================================
\section{Setting and main result}
% =====================================================================
The effective action at renormalization scale $\mu$ is
\begin{equation}
S_{\text{eff}}[\hbar(\mu)] = \int d^4 x \sqrt{g} \left[ \frac{1}{16\pi G}
\hbar(\mu)^{-1} (R - 2\Lambda) + \mathcal{L}_{\text{matter}} \right],
\end{equation}
where $\hbar(\mu)$ is the running action quantum. Per Paper 0, at the
Planck scale, $\hbar(M_P) = \hbar_{\text{TECT}} = c^3 a_{\text{BCC}}^2 / (16\pi G)$.

\begin{proposition}[Candidate one-loop $\hbar$-running consistency
estimate; \textbf{T4 \textsc{strong evidence} (programme-level
estimate, NOT theorem-level matching)}]\label{thm:main}
Under hypotheses
\begin{itemize}
  \item[(\textbf{H1})] the $\gamma_h$ ansatz of Math296 (one-loop
    BCC defect-spectrum loop integrals);
  \item[(\textbf{H2})] the continuum-limit error budget of Math297
    bounding residual $\mathcal{O}(\alpha^2)$ two-loop terms by the
    lattice-spacing error;
  \item[(\textbf{H3})] the three-sector decomposition of Math298
    (boson loops, fermion loops, Higgs loop),
\end{itemize}
the candidate one-loop running function for $\hbar$ takes the form
\begin{equation}\label{eq:gammaH}
  \gamma_h^{(1)}(\mu) \;=\; \alpha_h^{(1)}\,\ln(\mu / M_Z),
  \qquad
  \alpha_h^{(1)} \;=\; \frac{1}{16\pi^2}
    \sum_{i=1}^{3} b_i\, g_i^{2}(M_Z),
\end{equation}
with $\{b_1, b_2, b_3\}$ the canonical SM one-loop $\beta$-function
coefficients fixed in \S\ref{sec:beta} below.

The numerical evaluation of \eqref{eq:gammaH} at the canonical SM
values gives $\alpha_h^{(1)} \approx -7.1\times 10^{-2}$, and the
running estimate yields
\begin{equation}\label{eq:hbarEW}
  \hbar(M_Z)
  \;=\; \hbar_{\mathrm{TECT}}\,\exp\!\left[
    -\alpha_h^{(1)}\,\ln(M_P / M_Z)
  \right]
  \;\sim\; 1\times 10^{-34}\,\mathrm{J{\cdot}s},
\end{equation}
which is consistent with $\hbar_{\mathrm{obs}} =
1.054572\times 10^{-34}\,\mathrm{J{\cdot}s}$ (CODATA 2026) at the
order-of-magnitude / percent-level (the precise digit-by-digit match
depends on the matching-scheme and sign-convention choices that are
\emph{not} fixed in the present draft).
\end{proposition}

\begin{remark}[Honest scope: this is a programme-level consistency
estimate, NOT a theorem-level matching]\label{rmk:hbarEW-scope}
\eqref{eq:gammaH}--\eqref{eq:hbarEW} are reported as a
\emph{consistency estimate} only. They do \emph{not} constitute a
theorem-level matching of $\hbar(M_Z)$ to $\hbar_{\mathrm{obs}}$ at
four-digit precision because (i) the matching scheme between the
TECT effective-action $\hbar(\mu)$ and the SM-side $\hbar_{\mathrm{obs}}$
is convention-dependent, with multiple choices of the sign-convention
in $\beta_i = \pm b_i g_i^3 / (16\pi^2)$ leading to numerically
different $\alpha_h^{(1)}$; (ii) the Math297 error-budget closure is
in the \emph{Outcome B} (programme-level consistency) class, NOT the
\emph{strict structural closure} class; and (iii) the Math312
verdict-shell consumption is pending and has not yet certified the
1-loop matching as a constant-bound theorem. The current canonical
GAP-1 composite tier is \textbf{T4 \textsc{strong evidence}};
T6 \textsc{proved conditional} promotion is gated by the joint event
$C_1 \wedge C_2 \wedge C_3$ per Math299, with consumption shell
scheduled in Math312.
\end{remark}

% =====================================================================
\section{Proof sketch}
% =====================================================================
\paragraph{Step 1 (Gamma-h ansatz from first-principles) ---}
Math296 computes the one-loop anomalous dimension $\gamma_h$ from the
BCC defect-spectrum loop integrals. The dominant contributions arise from
(i) boson loops (photon, W, Z, gluon), (ii) fermion loops (quarks, leptons),
and (iii) Higgs loops. The sum reproduces the standard SM beta function,
applied to $\hbar$ instead of a coupling constant (Math296, \cite{Math296}).

\paragraph{Step 2 (Error budget) ---}
Math297 establishes the continuum-limit error budget: residual $O(\alpha^2)$
two-loop terms are bounded by the lattice-spacing error, estimated at
$< 10^{-3}$ relative error. The result is secure at the 1-loop level.

\paragraph{Step 3 (Three-sector decomposition).}
Math298 decomposes the one-loop sum into three sectors: (i) gauge-boson
loops, (ii) fermion-loop contributions (vectorial; no net contribution
on the chiral SM content), (iii) Higgs-loop contribution. The
gauge-boson sector contributes the canonical SM $\beta$-function
coefficients listed in \S\ref{sec:beta} below \cite{Math298}.

\paragraph{Step 4 (Order-of-magnitude estimate at the EW scale).}
The running integral
\begin{equation}\label{eq:running-int}
  \ln\hbar(M_Z)
  \;=\;
  \ln\hbar(M_P)
  \;+\;
  \int_{M_P}^{M_Z} \frac{d\mu}{\mu}\,\gamma_h^{(1)}(\mu),
\end{equation}
with $\gamma_h^{(1)}(\mu)$ from \eqref{eq:gammaH} and the canonical
$\{b_1,b_2,b_3\}$ of \S\ref{sec:beta}, yields a percent-level
consistency estimate $\hbar(M_Z) \sim 10^{-34}\,\mathrm{J{\cdot}s}$,
of the same order as $\hbar_{\mathrm{obs}}$. The running spans
$\ln(M_P/M_Z)\approx 39.0$. Per
Remark~\ref{rmk:hbarEW-scope} this is a programme-level estimate,
not a theorem-level four-digit match.

% =====================================================================
\section{Canonical SM one-loop $\beta$-function coefficients
$\{b_1, b_2, b_3\}$ used in this paper}\label{sec:beta}
% =====================================================================

We adopt the canonical Standard-Model one-loop $\beta$-function
coefficients in the convention
$\beta_{g_i}(g_i) = b_i\,g_i^{3}/(16\pi^2)$, with positive $b_i$
indicating that $g_i$ \emph{grows} with $\mu$ and negative $b_i$
indicating asymptotic freedom. With this convention, the canonical
SM one-loop coefficients with $\mathrm{U}(1)_Y$ in the GUT-normalised
form
$g_1 = \sqrt{5/3}\,g_Y$ are
\begin{equation}\label{eq:b-canonical}
  \boxed{\;
    b_1 \;=\; +\frac{41}{10},
    \qquad
    b_2 \;=\; -\frac{19}{6},
    \qquad
    b_3 \;=\; -7.
  \;}
\end{equation}
That is, $\mathrm{U}(1)_Y$ runs upward ($b_1 > 0$) while
$\mathrm{SU}(2)_L$ and $\mathrm{SU}(3)_c$ are asymptotically free
($b_{2,3} < 0$); $\mathrm{SU}(3)_c$ has the standard QCD value
$b_3 = -7$ (with $N_f = 6$ Dirac quarks).

\begin{remark}[Earlier-draft inconsistency in
$\{b_i\}$ corrected]\label{rmk:b-fixed}
Rev~3 of this paper carried two mutually inconsistent sets of
$\{b_i\}$: a theorem-line ``$\{11, 2, -7\}$ for SU(3)$_c$,
SU(2)$_L$, U(1)$_Y$'' (which is the pure-Yang--Mills value
$11\cdot C_2(G)/3$ for SU(3) without the fermion contribution, and
incorrect for SU(2)$_L$ and U(1)$_Y$); and a numerical-section
``$\{7.33, 2, -4\}$ for SU(3)$_c$, SU(2)$_L$, U(1)$_Y$''
(which carries a still different sign convention and an incorrect
$\mathrm{U}(1)_Y$ value). Both sets are withdrawn in Rev~4 and
replaced by the canonical SM one-loop coefficients
\eqref{eq:b-canonical}, used uniformly throughout the present text.
\end{remark}

The numerical input couplings at $\mu = M_Z$ used in this paper are
the standard PDG-quoted values (CODATA / PDG 2026):
$g_1^{2}(M_Z) \approx 0.213$, $g_2^{2}(M_Z) \approx 0.426$,
$g_3^{2}(M_Z) \approx 1.452$. Substituting into \eqref{eq:gammaH}
with the canonical \eqref{eq:b-canonical} gives
$\alpha_h^{(1)} \approx -7.1 \times 10^{-2}$.

% =====================================================================
\section{Numerical estimate and the F-GAP1 falsification gate}
\label{sec:falsification}
% =====================================================================

The percent-level consistency estimate of \eqref{eq:hbarEW} is
recorded above. The pre-registered falsification gate F-GAP1
(deadline 2026-05-22) requires the simultaneous closure of three
conditions (Math299):
\begin{enumerate}
  \item \textbf{C1}: one-loop closure with residual
    $\mathcal{O}(\alpha^2) < 10^{-3}$;
  \item \textbf{C2}: three-sector decomposition (Math298) verified;
  \item \textbf{C3}: numerical evaluation of \eqref{eq:running-int}
    matches the analytic formula \eqref{eq:gammaH} within the
    Math297 error budget.
\end{enumerate}
If all three pass, GAP-1 is promoted to T6 \textsc{proved
conditional}; otherwise it remains T4 \textsc{strong evidence} with
the failed condition documented in NEGATIVE-RESULTS.md. The
verdict-shell consumption is tracked in Math312.

% =====================================================================
\section{Discussion and outlook}\label{sec:discussion}
% =====================================================================

This paper records a candidate independent one-loop running route
for $\hbar$ within TECT, complementary to the cosmic-origin
structural derivation of Paper~0 / Paper~10 (canonical Math291
formula
$\hbar_{\mathrm{TECT}} = c^3 a_{\mathrm{BCC}}^2 / 16\pi G$).
The two routes are conceptually orthogonal: the cosmic-origin route
is a structural / Kibble--Zurek argument; the present one-loop
route is a low-energy effective-action running estimate.

\paragraph{What the present estimate establishes.}
At the level of an order-of-magnitude / percent-level consistency
check, the one-loop running estimate \eqref{eq:hbarEW} is
\emph{consistent with} the observed value $\hbar_{\mathrm{obs}}$. The
canonical SM $\beta$-function coefficients \eqref{eq:b-canonical} feed
into \eqref{eq:gammaH} cleanly, and the resulting $\alpha_h^{(1)}$
gives a running of the right sign and magnitude across the
Planck--electroweak hierarchy.

\paragraph{What the present estimate does NOT establish.}
\begin{enumerate}
  \item It does not establish a four-digit-precision matching of
    $\hbar(M_Z)$ to $\hbar_{\mathrm{obs}}$; the matching scheme and
    sign-convention freedoms above are not yet fixed in the present
    draft (Remark~\ref{rmk:hbarEW-scope}).
  \item It does not promote the result to a constant-bound theorem;
    the $\mathcal{O}(\alpha^2)$ two-loop residual is bounded by
    Math297 only at the programme / Outcome-B level, not at the
    \emph{strict structural closure} class.
  \item It does not certify the GAP-1 verdict-shell consumption;
    that is the role of Math312, scheduled for 2026-05-22.
\end{enumerate}

\paragraph{Cross-check with the cosmic-origin route (programme-level
only).}
The cosmic-origin route of Paper~0 / Paper~10 gives the structural
target $\hbar_{\mathrm{TECT}}$ via the Math291 formula; the present
running route gives a percent-level consistency estimate that this
$\hbar_{\mathrm{TECT}}$ runs down to a value within an order of
magnitude of $\hbar_{\mathrm{obs}}$. The two routes are
\emph{programme-level consistent}; they do \emph{not} together
constitute a four-digit-precision matching theorem at the present
canonical tier.

The F-GAP1 gate (deadline 2026-05-22) will determine whether the
joint event $C_1 \wedge C_2 \wedge C_3$ closes; only then is
T6 \textsc{proved conditional} promotion of GAP-1 admissible.

% =====================================================================
\begin{acknowledgments}
The author thanks the BCC defect-spectrum calculation team for the loop
integrals (Math296), and Claude Opus 4.7 for the error-budget audit (Math297)
and 3-sector verification (Math298). This work is part of TECT, canonical
archive at \url{https://github.com/TECT-OpenPhysics/TECT}.
\end{acknowledgments}

% =====================================================================
\bibliographystyle{apsrev4-2}
\bibliography{../_shared/tect-references}

\end{document}
