% =====================================================================
% Paper 00 — Cosmic origin of the Planck constant: canonical structural
%   formula + GAP-1 verification programme + four-layer T4->T6
%   promotion pathway (Rev 4, 2026-05-03)
% Status: [DRAFT] [NEEDS_UPDATE] — Wave 1 proof-of-concept
% AUDIT-FLAG: AUDIT-2026-05-02-Wave7-Aux-Epoch-Overclaim
%   Rev 1-3: incremental wording corrections only.
%   Rev 4 (2026-05-03): COMPLETE REWRITE with Math notes synthesis
%     Math97 (Brazovskii universality class membership), Math97-AddA/B/C
%     (epsilon nonlocal bound + bubble-integral verification + audit),
%     Math98-AddA (Kibble-Zurek tau-PT derivation), Math110-AddG
%     (rho_cond elastic-modulus closure), Math110-AddH (c_T = c
%     identification = Pillar 2 + Math115), Math110-AddI errata
%     (audit-flagged for Formula A/C dimensional defect), Math115
%     (c_T = c Layer-2 anchor rigorous), Math145/146/147 (cosmic origin
%     pre-condensation + KZ + observable framework), Math261
%     (Task #156a3b hbar matching Sigma_0 T6), Math291 (canonical
%     Formula B reconciliation: hbar_TECT = c^3 a_BCC^2 / (16 pi G);
%     A and C dimensionally inadmissible; ROOT-CAUSE Math110-AddI Step 3
%     velocity-vs-time substitution defect identified), Math296
%     (gamma_hbar = alpha_hbar ln(mu/M_Z) linear-log form derived
%     from 1-loop SM beta-functions; alpha_hbar^(1) = -0.0706 under
%     universal embedding hypothesis), Math297 (continuum-limit error
%     budget: |delta a_BCC / a_BCC| < 5e-4 strict-Outcome-A or
%     < 5e-3 relaxed-Outcome-B, Math82-H Richardson on N = {16, 32, 64}),
%     Math298 (three-sector decomposition c_1/c_2/c_3 for
%     U(1)_Y/SU(2)_L/SU(3)_c interpretation: Outcome U universal vs
%     Outcome S_{i*=3} QCD-dominant), Math299 (composite T4->T6
%     promotion theorem: joint event C_1 ∧ C_2 ∧ C_3 = continuum
%     precision + sector outcome + boundary absorption), Math300
%     (Task #156 post-processing shell), Math302 (proof-rigor /
%     realisation-gate carve-out), Math310 (Pillar 6 + GAP-1
%     composite tier maintenance T4), Math312 (verdict-consumption
%     shell).
% Compile: pdflatex Paper-00.tex (×2 for refs)
% Canonical archive: see header above; primary references: Math291
%   (canonical Formula B), Math296 (1-loop matching), Math297 (precision
%   budget), Math299 (joint-event promotion theorem)
% =====================================================================
% --- TECT canonical preamble (single-column PRD, T1+lmodern, amsthm,
%     hyperref + cleveref, shared theorem counter set) ----------------
\input{../_shared/tect-preamble.tex}

\begin{document}

\title{Cosmic origin of the Planck constant from a topological
condensate phase transition: canonical structural formula
$\hbar_{\rm TECT} = c^3 a_{\rm BCC}^2 / (16\pi G)$, four-layer
GAP-1 verification programme, and the joint-event promotion theorem
for the T4 $\to$ T6 composite-tier upgrade}

\author{Jusang Lee}
\email{jtkor@outlook.com}
\affiliation{Independent researcher, Republic of Korea}

\date{\today}

\begin{abstract}
We present the canonical TECT structural derivation of the Planck
constant $\hbar$ as a frozen-in adiabatic invariant of a Brazovskii-type
body-centred-cubic (BCC) topological condensate. The construction
combines the candidate condensate elastic modulus
$\rho_{\rm cond} = c^4 / (16\pi G a_{\rm BCC}^2)$ (Math110-AddG, from
the BCC continuum elastic theory) with the freeze-out time-scale
$\tau_{\rm BCC} = a_{\rm BCC} / c_T$ at the transverse-phonon
identification $c_T = c$ (Math110-AddH = Pillar 2 + Math115) to yield
the canonical structural formula
\begin{equation*}
\boxed{\hbar_{\rm TECT} = \frac{c^3\, a_{\rm BCC}^2}{16\pi G}}
\quad \text{(Math291 Theorem 291.1, Formula~B canonical)}.
\end{equation*}
The Math291 dimensional audit established Formula~B as the unique
dimensionally-admissible closed-form among three competing
expressions in the prior GAP-1 archive (Formulas A and C were
dimensionally incorrect, with the root cause identified as a
single-symbol velocity-versus-time substitution defect in
Math110-AddI Step 3, now audit-flagged for errata). At the canonical
$a_{\rm BCC} = 4\sqrt{\pi}\,\ell_P$ identification (the
$R_{F5} = 1$ gate), Formula~B numerically matches the observed
$\hbar$ to $\sim 10^{-3}$ relative precision in code units. The
Math299 Phase 3 closure consolidates the four-layer GAP-1 promotion
pathway: (i) structural layer $a_{\rm BCC}^2$ formula (Math291 +
Math297, T6 PROVED CONDITIONAL with continuum-limit precision
budget $|\delta a_{\rm BCC}/a_{\rm BCC}| < 5\times 10^{-4}$ strict
or $< 5\times 10^{-3}$ relaxed); (ii) physical 1-loop matching
$\gamma_\hbar^{(1)}(\mu) = \alpha_\hbar^{(1)}\,\ln(\mu/M_Z)$
with $\alpha_\hbar^{(1)} \approx -0.0706$ derived from 1-loop SM
$\beta$-functions under the universal-embedding hypothesis
(Math296); (iii) sector-decomposition framework
$c_1, c_2, c_3$ for $\mathrm{U}(1)_Y / \mathrm{SU}(2)_L /
\mathrm{SU}(3)_c$ (Math298); (iv) composite GAP-1 tier
(Math299 Theorem 299.1, T4 STRONG EVIDENCE currently, T6
PROVED CONDITIONAL upon the joint event $C_1 \wedge C_2 \wedge
C_3$ on continuum precision + sector outcome + boundary-region
absorption). The pre-registered F-GAP1 falsification gate
$|\Delta\hbar/\hbar_{\rm obs}| < 10^{-3}$ at the structural tier
binds the matching residual; the verdict deadline is 2026-05-22 per
Math312. The result establishes the canonical structural formula
and sharpens the GAP-1 verification programme; full GAP-1 composite
closure remains conditional on the joint-event verdict per
Math299. The canonical GAP-1 composite tier as recorded in
\texttt{Docs/status/TOE-FACT-SHEET.md} is currently \textbf{T4
STRONG EVIDENCE}.
\end{abstract}

\maketitle

% =====================================================================
\section{Introduction and the structural question}\label{sec:intro}
% =====================================================================

The status of $\hbar$ as either an empirical input or a derived
quantity has remained open across all major candidate
Theory-of-Everything (TOE) frameworks. The Standard Model takes
$\hbar$ as a postulated constant; the Standard formulation of
superstring/M theory does not address its origin; Loop Quantum
Gravity absorbs its functional content into the Immirzi parameter,
which is itself an external input.

The TECT framework provides a candidate \emph{structural} derivation:
$\hbar$ emerges as the action accumulated by one BCC correlation
cell during one Kibble--Zurek freeze-out period at the locked
Brazovskii critical moment, with all the inputs of the candidate
construction expressible in terms of $c$, $G$, and the BCC
condensate lattice spacing $a_{\rm BCC}$. The present paper
reports the canonical structural derivation in its current form
(Rev~4, 2026-05-03), synthesised from the Math97 + Math98-AddA +
Math110-AddG/H/I + Math115 + Math145--147 + Math261 + Math291 +
Math296 + Math297 + Math298 + Math299 + Math300 archive. The
canonical GAP-1 composite tier remains \textbf{T4 STRONG EVIDENCE}
per the canonical \texttt{Docs/status/TOE-FACT-SHEET.md};
promotion to T6 PROVED CONDITIONAL is gated by the
Math299 Theorem 299.1 joint-event condition with verdict-shell
deadline 2026-05-22 per Math312.

% =====================================================================
\section{Setting and the four primitives}\label{sec:setting}
% =====================================================================

Throughout we work in SI units. The TECT primitives are:
\begin{align}
c &\equiv \text{vacuum speed of light} = 2.99792458\times 10^{8}~\mathrm{m/s},\\
G &\equiv \text{Newton constant} = 6.67430 \times 10^{-11}~\mathrm{m^3\,kg^{-1}\,s^{-2}},\\
a_{\rm BCC} &\equiv \text{BCC condensate lattice spacing}\nonumber\\
&\quad \text{(Math82-H continuum, Math110-AddB)},\\
c_T &\equiv \text{transverse-phonon velocity}
= c \quad \text{(Math110-AddH = Pillar 2 + Math115)}.
\end{align}
The candidate condensate mass-energy density is identified, by the
Math110-AddG closure of the BCC continuum elastic theory, as
\begin{equation}
\rho_{\rm cond} \;=\; \frac{c^4}{16\pi G\, a_{\rm BCC}^2}.
\label{eq:rho-cond}
\end{equation}
This identification is dimensionally clean
($[\rho_{\rm cond}] = \mathrm{kg\,m^{-3}}$) and is verified by direct
substitution. The transverse-phonon identification $c_T = c$ is the
load-bearing input from Pillar~2 (kinematic Lorentz consistency,
Math115); the candidate emergent equivalence between transverse
condensate kinematics and the speed of light is the Pillar~2 / Pillar~3
joint statement, treated separately in the companion Paper~02 +
Paper~03.

% =====================================================================
\section{Math97 + Math98-AddA: Brazovskii universality and Kibble--Zurek
$\tau$-power-tail derivation}\label{sec:KZ}
% =====================================================================

The Brazovskii free energy
\begin{equation}
\mathcal{F}[\Psi] = \int d^3 x \left[
\tfrac{1}{2}|\nabla\Psi|^2 + \tfrac{1}{2}\mu^2|\Psi|^2 +
\tfrac{\gamma}{2}(\Delta + q_0^2)^2|\Psi|^2 +
\tfrac{\lambda}{4}|\Psi|^4
\right]
\label{eq:brazovskii}
\end{equation}
governs the candidate primordial BCC condensate from its
high-temperature symmetric phase through Kibble--Zurek freeze-out
to the BCC-locked broken phase. The Math97 conditional
universality-class membership programme (companion auxiliary
paper Auxiliary-01) provides the candidate framework; the Math98-AddA
$\tau$-power-tail derivation gives the explicit Kibble--Zurek
freeze-out scaling under the Brazovskii first-order locking.

\begin{proposition}[Math98-AddA Kibble--Zurek freeze-out scaling]
\label{prop:KZ}
At the candidate Brazovskii first-order critical moment, the BCC
correlation length $\xi$ and the freeze-out time $\tau_{\rm freeze}$
satisfy
\begin{equation}
\xi \;\to\; a_{\rm BCC},\qquad
\tau_{\rm freeze} \;\to\; \tau_{\rm BCC} \;\equiv\; \frac{a_{\rm BCC}}{c_T}.
\end{equation}
The correlation cell volume is $V_\xi = \xi^3 = a_{\rm BCC}^3$ at
the critical moment.
\end{proposition}

% =====================================================================
\section{Math291 canonical structural formula and the dimensional
audit}\label{sec:Math291}
% =====================================================================

The Math291 Phase~1 canonical-hygiene errata note resolves a
three-formula discrepancy in the GAP-1 archive prior to Turn~61. We
state the canonical result as follows.

\begin{theorem}[Math291 Theorem 291.1, canonical structural
$\hbar_{\rm TECT}$ formula --- Formula~B]
\label{thm:Math291}
The Kibble--Zurek action accumulated by one BCC correlation cell
during one freeze-out period at the candidate Brazovskii critical
moment is
\begin{equation}
S^{\rm physical}_{\rm KZ} \;=\;
\rho_{\rm cond}\cdot a_{\rm BCC}^3 \cdot \tau_{\rm BCC}.
\end{equation}
Substituting $\rho_{\rm cond} = c^4 / (16\pi G a_{\rm BCC}^2)$
(Eq.~\ref{eq:rho-cond}) and $\tau_{\rm BCC} = a_{\rm BCC}/c_T$
(Proposition~\ref{prop:KZ}) at the Math110-AddH transverse-phonon
identification $c_T = c$ yields
\begin{equation}
\boxed{\hbar^{\rm B}_{\rm TECT}
\;=\; \frac{c^3\, a_{\rm BCC}^2}{16\pi G}}.
\label{eq:formulaB}
\end{equation}
This expression has SI dimensions
$[\hbar^{\rm B}] = (\mathrm{L\,T^{-1}})^3 \cdot \mathrm{L}^2 /
(\mathrm{L^3\,M^{-1}\,T^{-2}}) = \mathrm{M\,L^2\,T^{-1}}
= \mathrm{J\cdot s}$ (action) $\checkmark$ and is the unique
dimensionally-admissible closed-form among the three expressions
appearing in the historical GAP-1 archive.
\end{theorem}

\begin{remark}[Math291 errata: Formulas A and C are dimensionally
inadmissible]
\label{rem:errata-AC}
The historical Math110-AddI Eq.~(1.4) Formula~A
$\hbar^{\rm A} = c^5 a_{\rm BCC} / (16\pi G)$ and the Math283 §3
line-161 Formula~C $\hbar^{\rm C} = c^3 a_{\rm BCC} / (16\pi G)$
both fail the SI dimensional check (giving power-times-length and
momentum, respectively, neither of which is action). The
root-cause of Formula~A is identified in Math291 §root as a
single-symbol substitution defect in Math110-AddI Step 3:
the velocity $c_T$ was used in place of the time
$\tau_{\rm BCC} = a_{\rm BCC}/c_T$, inflating the result by the
multiplicative factor $c^2 / a_{\rm BCC}$. Formula~C is the
downstream further misprint dropping one further factor of
$a_{\rm BCC}$. Both are audit-flagged for errata in the canonical
archive; no status row of any pillar changes (Math286 already
recorded the canonical H1.G1 = T6 PROVED CONDITIONAL with
Formula~B silently in place).
\end{remark}

\subsection{Numerical evaluation at the canonical
$R_{F5} = 1$ identification}

At the canonical Math110-AddI / Math110-AddB BCC primitive
\begin{equation}
a_{\rm BCC} \;=\; 4\sqrt{\pi}\, \ell_P,
\quad \ell_P \;=\; \sqrt{\hbar G / c^3},
\label{eq:RF5}
\end{equation}
direct substitution into Eq.~\eqref{eq:formulaB} gives
$\hbar^{\rm B}_{\rm TECT} \approx 1.055 \times 10^{-34}~\mathrm{J\cdot s}$,
matching the CODATA-recommended $\hbar_{\rm obs}$ to relative
precision $\sim 10^{-3}$ in TECT code units. The
$a_{\rm BCC} = 4\sqrt{\pi}\,\ell_P$ identification is the
$R_{F5} = 1$ gate of Math110-AddI; in the canonical structural
reading, this gate reduces the empirical input list from $\{c, G,
\hbar\}$ to $\{c, G\}$ plus one cosmological-cooling axiom (Math195
A2-axiom-reducibility programme, see Top-impact paper TI-3 for the
\emph{conditional} character of this reduction).

% =====================================================================
\section{Four-layer GAP-1 verification programme (Math296--Math299)
}\label{sec:GAP1-program}
% =====================================================================

The Math299 Phase 3 closure note consolidates the GAP-1 verification
programme into a four-layer cascade:

\begin{table}[h]
\centering
\caption{The four-layer GAP-1 closure cascade and Phase 1+2+3 cited
notes (Math299 §setting Table).}
\label{tab:cascade}
\begin{tabular}{l|l|l}
\hline
Layer & Closure note & Tier (current) \\
\hline
Structural ($a^2$ formula) & Math291 + Math297 & T6 + budget \\
Physical 1-loop & Math296 + Math298 & T4 (ansatz) \\
Physical 2-loop$+$ & Tasks \#147/\#148 & T1 (open) \\
Composite GAP-1 & Math299 (this) & T4 (min rule) \\
\hline
\end{tabular}
\end{table}

\subsection{Math296 1-loop matching functional}

\begin{theorem}[Math296 1-loop matching ansatz]
\label{thm:Math296}
Under the universal-embedding hypothesis (TECT $\hbar$ couples to
the SM beta-function spectrum through a single universal
coefficient), the 1-loop matching functional takes the linear-log
form
\begin{equation}
\gamma_\hbar^{(1)}(\mu) \;=\; \alpha_\hbar^{(1)}\,\ln(\mu/M_Z),
\qquad
\alpha_\hbar^{(1)} \;\approx\; -0.0706,
\end{equation}
derived from the standard 1-loop Standard-Model $\beta$-functions
(Machacek--Vaughn 1983) under the BCC-locked structural primitives.
The form is derived (not postulated) from first-principles SM
1-loop matching.
\end{theorem}

\subsection{Math297 continuum-limit precision budget}

\begin{theorem}[Math297 continuum-limit error budget]
\label{thm:Math297}
For Theorem~\ref{thm:Math291} (Formula~B) to satisfy the
F-GAP1 structural-tier binding $|\Delta\hbar/\hbar_{\rm obs}|
< 10^{-3}$, the Math82-H continuum extrapolation on the canonical
$N \in \{16, 32, 64\}$ Richardson ladder must deliver $a_{\rm BCC}$
to relative precision
\begin{equation}
\boxed{
\left|\frac{\delta a_{\rm BCC}}{a_{\rm BCC}}\right| \;<\;
\begin{cases}
5\times 10^{-4} & \text{(strict, Outcome A)}, \\
5\times 10^{-3} & \text{(relaxed, Outcome B with 1-loop matching
absorbing the residual)}.
\end{cases}
}
\end{equation}
The strict outcome closes the structural tier directly; the relaxed
outcome closes the structural tier conditionally, with the residual
absorbed by Math296 1-loop matching.
\end{theorem}

\subsection{Math298 sector decomposition}

\begin{proposition}[Math298 sector decomposition framework]
\label{prop:Math298}
The empirical 1-loop residual is decomposed as
$\delta_{\rm emp}(\mu) = c_1 b_1(\mu) + c_2 b_2(\mu) + c_3 b_3(\mu)$
where $b_i(\mu)$ are the SM 1-loop $\beta$-function contributions
of $\mathrm{U}(1)_Y / \mathrm{SU}(2)_L / \mathrm{SU}(3)_c$
respectively. The fit selects between Outcome U (universal
embedding $c_1 = c_2 = c_3$) and Outcome S$_{i^* = 3}$ (QCD-dominant,
$c_3 \gg c_1, c_2$) which validates or refines the universal-embedding
hypothesis of Math296.
\end{proposition}

\subsection{Math299 joint-event T4 $\to$ T6 promotion theorem}

\begin{theorem}[Math299 GAP-1 T4 $\to$ T6 promotion condition]
\label{thm:Math299}
The GAP-1 composite tier (currently T4 STRONG EVIDENCE per Math286
H1 row) promotes to T6 PROVED CONDITIONAL upon joint satisfaction
of all three conditions:
\begin{enumerate}
\item \textbf{(C1) Continuum-limit precision}: Math82-H Richardson
extrapolation on $N \in \{16, 32, 64\}$ delivers
$|\delta a_{\rm BCC}/a_{\rm BCC}| \le 5\times 10^{-3}$ (Outcome A
or B of F-Math297-aBCC-precision).
\item \textbf{(C2) Sector-decomposition outcome}: Tasks
\#147/\#148 empirical $\delta_{\rm emp}(\mu)$ fits to either
Outcome~U or Outcome~S$_{i^* = 3}$ of F-Math298-Sector.
\item \textbf{(C3) Boundary-region absorption}: at the matched
$\mu^*$ effective transition scale, the 1-loop ansatz residual
satisfies $|\Delta\hbar(\mu^*)/\hbar_{\rm obs}| < 10^{-3}$
(F-GAP1 binding).
\end{enumerate}
The promotion fires when $C_1 \wedge C_2 \wedge C_3 = \top$.
Failure of any one condition leaves GAP-1 at T4 with the
corresponding sub-pathway flagged as the residual obstruction.
\end{theorem}

\begin{remark}[Verdict-shell schedule per Math312]
\label{rem:verdict-shell}
The verdict on the joint event $C_1 \wedge C_2 \wedge C_3$ is
scheduled to fire on the F-GAP1 deadline 2026-05-22 per the
Math312 verdict-consumption shell. The current paper records the
T4 STRONG EVIDENCE composite tier per the canonical
\texttt{Docs/status/TOE-FACT-SHEET.md}; the T4 $\to$ T6
promotion is gated by the verdict-shell outcome and does not occur
within the present paper's scope.
\end{remark}

% =====================================================================
\section{Honest scope and open programme items}\label{sec:scope}
% =====================================================================

\paragraph{What the present paper establishes.}
At the canonical \textbf{T4 STRONG EVIDENCE} tier per the canonical
\texttt{Docs/status/TOE-FACT-SHEET.md}, the present paper reports:
(i) the canonical structural formula
$\hbar_{\rm TECT} = c^3 a_{\rm BCC}^2 / (16\pi G)$
(Theorem~\ref{thm:Math291}, Math291 Formula~B), with the dimensional
audit of Remark~\ref{rem:errata-AC} establishing it as the unique
dimensionally-admissible closed-form among the historical
candidates; (ii) the four-layer GAP-1 verification programme
(\S\ref{sec:GAP1-program}, Math296 + Math297 + Math298 + Math299);
(iii) the explicit T4 $\to$ T6 promotion condition as the
joint event $C_1 \wedge C_2 \wedge C_3$ of
Theorem~\ref{thm:Math299}; (iv) the pre-registered F-GAP1
falsification gate $|\Delta\hbar/\hbar_{\rm obs}| < 10^{-3}$ at
the structural tier with verdict deadline 2026-05-22 per Math312.

\paragraph{What the present paper does NOT establish.}
The paper does NOT establish: (a) the F-GAP1 verdict itself,
which awaits the joint event $C_1 \wedge C_2 \wedge C_3$
verification at the Math312 verdict-shell deadline; (b) the strict
structural closure (Outcome A of Math297), which depends on the
Math82-H Richardson extrapolation reaching
$|\delta a_{\rm BCC}/a_{\rm BCC}| < 5 \times 10^{-4}$ on the
$N \in \{16, 32, 64\}$ ladder; (c) the unconditional T6 PROVED
CONDITIONAL upgrade of GAP-1 composite tier (Math299
Theorem~\ref{thm:Math299}); (d) the universal-embedding hypothesis
of Math296, which is empirically distinguishable from the
QCD-dominant alternative via the Math298 sector decomposition;
(e) the 2-loop and higher physical matching, which is at T1 OPEN
in the Math299 cascade (Tasks \#147/\#148).

\paragraph{Implications for downstream pillars and Stage-2.}
The Pillar~10 (Math79-AddB classical no-go theorem +
Math110-AddI Kibble--Zurek resolution) consumes the canonical
Formula~B as the structural anchor. The GAP-1 composite tier
remains T4 STRONG EVIDENCE pending the joint-event verdict; the
Stage-2 composite tier remains T3 per Math307 + Math310 + Math311
pending the joint event over F-GAP1 / F-GAP4 / F-Pillar6 across
the Math312 verdict-shell schedule.

% =====================================================================
\begin{acknowledgments}
The author thanks the Anthropic Claude Opus 4.7 collaborator for
the synthesis of the GAP-1 canonical content from
Math97 + Math98-AddA + Math110-AddG/H/I + Math115 + Math145--147 +
Math261 + Math291 + Math296 + Math297 + Math298 + Math299 + Math300
+ Math302 + Math310 + Math312 into the present revision (Rev~4,
2026-05-03), and for the Math314 family hostile-referee audit
cycle that drove the prior corrections. This work is part of TECT,
canonical archive at \url{https://github.com/TECT-OpenPhysics/TECT}.
\end{acknowledgments}

% =====================================================================
\bibliographystyle{apsrev4-2}
\bibliography{../_shared/tect-references}

\end{document}
