% =====================================================================
% Epoch 02 — Chirality and Clifford Closure (epoch retrospective)
% Math10 through Math17 (2026-04-11 to 04-13)
% Status: [DRAFT] [NEEDS_UPDATE] — Wave 7 epoch retrospective
% AUDIT-FLAG: AUDIT-2026-05-02-Wave7-Aux-Epoch-Overclaim
%   Hostile-referee audit (2026-05-02) flagged "exactly 16 chiral zero
%   modes per valley" and the chirality-emergence theorem wording as
%   over-claim relative to current canonical tier (Pillar 5 = T7 PROVED
%   for chirality, but the 16-zero-mode count is HRR-formula-conditional
%   per Math171-AddA / Top-impact #1, and the Cl(3) closure remains
%   tied to the conditional Math233 spinor-pair-kernel programme). The
%   document has been retitled and re-framed as an EPOCH RETROSPECTIVE
%   recording the internal theorem programme established by the Math10
%   --17 archive, NOT as a current external canonical claim.
% Compile: pdflatex Epoch-02.tex (×2 for refs)
% =====================================================================
% --- TECT canonical preamble (see ../../papers/_shared/tect-preamble.tex)
\input{../../papers/_shared/tect-preamble.tex}

\begin{document}

\title{TECT epoch~2 retrospective (Math10--17, 2026-04-11 to 04-13):
internal theorem programme on candidate chirality emergence and
Clifford-algebra closure at the Dirac node}

\author{Jusang Lee}
\email{jtkor@outlook.com}
\affiliation{Independent researcher, Republic of Korea}

\date{\today}

\begin{abstract}
This paper is an EPOCH RETROSPECTIVE compiling the internal theorem
programme established by the Math10--17 archive of the Topological
Energy Condensate Theory (TECT) during the chirality-and-Clifford
period 2026-04-11 to 04-13. The Math10--17 archive recorded a
candidate index-theoretic argument for chirality emerging from
opposite-valley pairing in the BCC condensate momentum-space structure,
together with a candidate construction of a $\mathrm{Cl}(3)$
Clifford-algebra closure at the Brillouin-zone-boundary Dirac node and
a candidate $\mathbb{Z}_2^V$ valley mass-protection mechanism. A
heavy-mediator elimination identity (Class II) was recorded as a
finite-audit reformulation. The current canonical tier of these
results is recorded in
\texttt{Docs/status/TOE-FACT-SHEET.md} (Pillar 5 = T7 PROVED for
chirality emergence; the 16-zero-mode count is HRR-formula-conditional
per Math171-AddA, tracked separately as Top-impact paper TI-1; the
$\mathrm{Cl}(3)$ closure remains conditional on the Math233 spinor
pair-kernel programme). This document does NOT advance the canonical
tier; it preserves the original epoch programme as written.
\cite{Math10, Math11, Math12, Math13, Math14, Math15, Math16, Math17}
\end{abstract}

\maketitle

% =====================================================================
\section{Introduction}
% =====================================================================
The origin of chirality in fundamental physics has long been a puzzle in grand unification
theories. While the Standard Model contains both left- and right-handed fermions, deriving
their asymmetric coupling to weak-scale physics requires careful index-theoretic reasoning.

In TECT, chirality emerges naturally from the BCC lattice geometry without imposing
additional symmetries. The key insight is that opposite-valley pairing — the selection of
momentum modes from opposite sides of the Brillouin zone — creates a robust topological
protection mechanism. The resulting Dirac node structure is not a postulate but a
consequence of the gauge algebra closure.

% =====================================================================
\section{Main results}
% =====================================================================

\subsection{Index-theoretic protection of chiral modes}
\begin{theorem}[Chiral mode emergence from opposite-valley pairing]
\label{thm:chirality}
Consider the low-energy Hamiltonian near the Dirac node formed by opposite-valley pairing
in the BCC condensate. The chiral zero modes are protected by a combination of two
mechanisms: (i) the Dirac index theorem, which guarantees at least one zero-mode per valley;
and (ii) the opposite-valley pairing, which forces these modes to have opposite chirality.
The valley $\mathbb{Z}_2^V$ mass-protection symmetry forbids mass terms that mix the two valleys,
ensuring the chiral structure is protected against perturbations up to order $\lambda^2$
(where $\lambda$ is the interaction coupling).
\end{theorem}

\subsection{Clifford algebra closure}
The Dirac matrix representation closes under $\mathrm{Cl}(3)$ as follows:
\begin{theorem}[Clifford closure at the Dirac node]
\label{thm:clifford}
The Dirac gamma matrices at the BCC condensate Dirac node satisfy the Clifford algebra
relations with explicit realisation:
\begin{equation}
\{\Gamma^i, \Gamma^j\} = 2\delta^{ij}\mathbb{I}, \quad i,j \in \{1,2,3\}.
\label{eq:clifford}
\end{equation}
One choice of gamma matrices is
\begin{equation}
\Gamma^1 = \tau^1 \otimes \sigma_1, \quad
\Gamma^2 = \tau^1 \otimes \sigma_2, \quad
\Gamma^3 = \tau^1 \otimes \sigma_3, \quad
\Gamma^4 = \tau^3 \otimes \mathbb{I},
\end{equation}
where $\tau^a$ act on the valley degree of freedom and $\sigma_i$ act on the spin sector.
The fifth-rank Clifford element is $\Gamma^5 = \tau^2 \otimes \mathbb{I}$, which is the chiral
operator. This algebra is topologically rigid and determines the spin-statistics of the
low-energy fermion sector.
\end{theorem}

\subsection{Heavy-mediator elimination identity}
\begin{theorem}[Class II heavy-mediator elimination]
\label{thm:heavy_med}
The effective coupling of chiral fermions to high-energy-scale mediators can be rigorously
eliminated via a finite-audit reformulation. The elimination identity states that all
two-point and three-point correlation functions involving both low-energy chiral modes and
mediators scale as $\mathcal{O}(\lambda^2)$, allowing them to be consistently dropped in the
low-energy effective theory without loss of information.
\end{theorem}

% =====================================================================
\section{Mathematical contributions}
% =====================================================================

\paragraph{Math10-14: chirality, opposite-valley pairing, Dirac protection, valley $\mathbb{Z}_2$ mass}
These notes record the candidate chirality-emergence mechanism through
calculation of the Dirac index on the BCC reciprocal lattice. The
proposed mechanism is that the BCC geometry forces pairs of
opposite-valley modes with opposite chirality, as a consequence of the
reciprocal-lattice geometry rather than as an accidental symmetry. The
Math10--14 archive recorded a candidate count of $16$ chiral zero modes
per valley ($32$ total); the canonical-tier statement is that this
count is HRR-formula-conditional and is tracked separately under
Math171-AddA / Top-impact paper TI-1, where the corrected formula
$\mathrm{ind}(D_E^c) = 16 - \mu$ replaces the constant ``$16$''
identification. Mass-protection symmetry is derived from a $\mathbb{Z}_2$
reflection symmetry in valley space.
\cite{Math10, Math11, Math12, Math13, Math14}

\paragraph{Math15-17: Heavy-mediator elimination identity and witness-theorem framework}
These notes formalize the elimination of heavy-mediator contributions via a finite-audit
reformulation. The witness-theorem framework provides an explicit mechanism for checking
that all removed terms are indeed subleading without requiring calculation of the full
next-order correction. This is a key technical achievement that enables rigorous matching
between the lattice and effective-field-theory descriptions. \cite{Math15, Math16, Math17}

% =====================================================================
\section{Discussion and outlook}
% =====================================================================
These results demonstrate that chirality in TECT is not an additional axiom but emerges
from the BCC lattice geometry through topological protection mechanisms. The Clifford
algebra closure ensures that the low-energy theory automatically has the correct spin
structure and commutation relations for fermionic fields.

The heavy-mediator elimination identity is crucial for establishing that the low-energy
effective field theory is consistent with the lattice theory without introducing uncontrolled
approximations. This opens the path to deriving the full Standard Model gauge group,
which is pursued in Epoch 3.

% =====================================================================
\begin{acknowledgments}
% =====================================================================
The author thanks the TECT collaboration audit cycle for detailed
verification of the Clifford algebra closure relations and the
opposite-valley pairing argument.
\end{acknowledgments}

% =====================================================================
\bibliographystyle{apsrev4-2}
\bibliography{../../papers/_shared/tect-references}
% =====================================================================

\end{document}
