% =====================================================================
% Paper 09 — EP-consistency BOUND note (NOT a Pillar-9 closure paper)
% Status: [DRAFT] [NEEDS_UPDATE]
% AUDIT-FLAG: AUDIT-2026-05-02-Wave7-Aux-Epoch-Overclaim
%   (Math314-AddD extension covering Wave 1/4/5 papers Paper-09..16).
%   Hostile-referee audit (2026-05-02): "equivalence principle
%   rigorously established" / "Pillar 9 = T7 PROVED" too strong. The
%   MPD spin-curvature bound is heuristic scaling (epsilon ~ m_s/M_P,
%   |Delta X_MPD - X_geo| <= 4 epsilon^2 R_c), NOT an exact theorem
%   for "m_grav = m_inert". Recast as
%   "EP consistency bound on spin-curvature deviation from geodesic
%   universality" --- bound the deviation, do not derive the principle.
% Canonical archive: TECT-Math_EP-rigorous-v3.1.tex.txt, Math314-AddD
% =====================================================================
% --- TECT canonical preamble (see _shared/tect-preamble.tex) ----------
\input{../_shared/tect-preamble.tex}

\begin{document}

\title{An equivalence-principle consistency bound on spin-curvature
deviation from geodesic universality in a topological condensate}

\author{Jusang Lee}
\email{jtkor@outlook.com}
\affiliation{Independent researcher, Republic of Korea}

\date{\today}

\begin{abstract}
We derive a consistency bound on the deviation of spinning-particle
trajectories from geodesic universality within the Topological Energy
Condensate Theory (TECT) framework, where gravity emerges from
phonon interactions (Pillar 3). Using the
Mathisson--Papapetrou--Dixon (MPD) equation for spinning particles
in the emergent curved background, the centre-of-mass deviation
between the MPD trajectory and the geodesic trajectory is bounded by
\[
\| \Delta \mathbf{X}_{\rm MPD} - \mathbf{X}_{\rm geo} \|
\;\lesssim\; 4 \epsilon^2 R_{\rm c},
\]
where $\epsilon \sim m_s / M_{\rm P}$ is a dimensionless small
parameter (spin-mass-to-Planck-mass ratio) and $R_{\rm c}$ is the
local curvature radius. The bound vanishes in the test-body limit
$\epsilon \to 0$, indicating consistency with geodesic universality
in this limit; it does NOT, however, constitute a derivation of the
equivalence principle as a theorem. The scaling estimate above is
heuristic: a rigorous theorem-level statement of
$m_{\rm grav} = m_{\rm inert}$ would require additional input
(microscopic identification of $m_{\rm inert}$ and $m_{\rm grav}$
from the underlying TECT phonon kinematics, plus an analytic
constant-bound theorem on the residual). The current canonical tier
of Pillar~9 is recorded in
\texttt{Docs/status/TOE-FACT-SHEET.md}; the present paper provides
a candidate consistency bound, NOT a Pillar~9 closure theorem.
\end{abstract}

\maketitle

% =====================================================================
\section{Introduction}\label{sec:intro}
% =====================================================================
The equivalence principle (EP) --- the statement that the
gravitational coupling of matter is universal in some appropriate
sense --- is one of the empirical inputs that fix general relativity
as the metric theory of gravity. Eötvös-type experiments constrain
its weak-form violation at the level $\sim 10^{-13}$.

The Topological Energy Condensate Theory (TECT) treats gravity as
emergent from collective phonon dynamics on the BCC condensate
(Pillar~3). A natural question is whether, within the present
canonical tier of TECT, the universality of the matter--condensate
coupling implies any quantitative restriction on the trajectory
deviation of a spinning test body from the geodesic of the
emergent metric.

The present paper records a \emph{consistency bound} on that
deviation. It does \emph{not} establish the equivalence principle
as a TECT theorem, and it does not derive
$m_{\mathrm{grav}} = m_{\mathrm{inert}}$ at the level of a
constant-bound theorem. Both are honest open programmes: the
former requires microscopic identifications of $m_{\mathrm{inert}}$
and $m_{\mathrm{grav}}$ in terms of the underlying TECT phonon
kinematics, plus an analytic bound; the latter is the canonical
Pillar~9 \textbf{T1 \textsc{open}} item. Within the
Mathisson--Papapetrou--Dixon (MPD) formalism for spinning test
bodies in a curved background, the present paper bounds the
centre-of-mass deviation between the MPD trajectory and the
geodesic of the emergent metric by a heuristic
$\mathcal{O}(\epsilon^2)$ scaling estimate, where
$\epsilon \sim m_s / M_{\mathrm{P}}$ is a small dimensionless ratio.
The estimate is reported as a \emph{consistency bound}, in the
order-of-magnitude sense, NOT as a rigorous-theorem closure of
Pillar~9.

% =====================================================================
\section{Setting and main result}
% =====================================================================
The Mathisson-Papapetrou-Dixon equations describe a spinning point particle of
mass $m$ and spin $\mathbf{S}$ in a curved spacetime with metric $g_{\mu\nu}$
and Riemann curvature $R_{\mu\nu\rho\sigma}$:
\begin{align}
m \frac{D u^\mu}{d\tau} &= -\frac{1}{2m} R^\mu{}_{\nu\rho\sigma} S^{\rho\sigma} u^\nu
+ f^\mu, \label{eq:mpd1} \\
\frac{D S^{\mu\nu}}{d\tau} &= u^\mu p^\nu - u^\nu p^\mu, \label{eq:mpd2}
\end{align}
where $u^\mu = \dot{x}^\mu$ is the four-velocity, $p^\mu = m u^\mu + \text{spin correction}$ is the
generalized momentum, $\tau$ is proper time, and $f^\mu$ represents external forces.

In flat spacetime ($R = 0$), Eq.~\eqref{eq:mpd1} reduces to $m u^\mu = \text{const}$
(free motion). In curved spacetime, the spin-curvature coupling term
$R^\mu{}_{\nu\rho\sigma} S^{\rho\sigma} u^\nu$ perturbs the trajectory away from a pure
geodesic.

The equivalence-principle bound is framed using two notions of "centre of mass":
\begin{itemize}
\item \textbf{Geometric (geodesic) centre}: $\mathbf{X}_{\rm geo}(\tau)$ — the point on a
  geodesic closest to the particle's instantaneous position.
\item \textbf{MPD centre}: $\mathbf{X}_{\rm MPD}(\tau)$ — the centre of mass computed from the
  MPD equations, including spin-curvature corrections.
\end{itemize}

\begin{proposition}[EP consistency bound on MPD spin-curvature
deviation from geodesic universality;
\textbf{T4 \textsc{strong evidence} (heuristic scaling estimate)}]
\label{thm:main}
Under the hypotheses
\begin{itemize}
  \item[(\textbf{H1})] the emergent gravitational field satisfies the
    Einstein equations at one-loop (Pillar~3 closure at order
    $N=1$, \textbf{T5 \textsc{closed@1-loop}});
  \item[(\textbf{H2})] every test body couples to the condensate via
    the universal phonon mechanism of Pillar~5
    (universality at the present canonical tier);
  \item[(\textbf{H3})] the spin-curvature coupling parameter
    $\epsilon \sim m_s / M_{\mathrm{P}}$ is a small dimensionless
    ratio of the spin-carrier mass $m_s$ to the Planck mass
    $M_{\mathrm{P}}$;
  \item[(\textbf{H4})] the local curvature radius $R_{\mathrm{c}}$ is
    large compared with the test-body Compton wavelength,
\end{itemize}
the centre-of-mass deviation between the MPD trajectory and the
geodesic of the emergent metric admits the order-of-magnitude
scaling estimate
\begin{equation}\label{eq:ep_bound}
\boxed{\;
  \big\|\,\Delta\mathbf{X}_{\mathrm{MPD}} - \mathbf{X}_{\mathrm{geo}}
  \,\big\| \;\lesssim\; 4\,\epsilon^2\, R_{\mathrm{c}},
\;}
\end{equation}
where ``$\lesssim$'' denotes an order-of-magnitude bound (not a
constant-bound theorem).
\end{proposition}

\begin{remark}[Honest scope --- the present result does NOT certify
the equivalence principle as a TECT theorem]\label{rmk:honest-scope}
The bound \eqref{eq:ep_bound} vanishes in the test-body limit
$\epsilon \to 0$. This is consistent with geodesic universality in
the test-body limit, but it does \emph{not} constitute a
TECT-internal derivation of the equivalence principle. A theorem-
level statement that $m_{\mathrm{grav}} = m_{\mathrm{inert}}$ would
require: (i) microscopic identification of $m_{\mathrm{inert}}$ and
$m_{\mathrm{grav}}$ in the underlying phonon kinematics; (ii) an
analytic constant-bound theorem $|\Delta\mathbf{X}| \leq
C\,\epsilon^2 R_{\mathrm{c}}$ with $C$ explicit and finite under
the four hypotheses (H1)--(H4); (iii) discharge of the implicit
``$\lesssim$''-to-``$\leq$'' promotion per the internal audit-policy
estimate-vs-theorem distinction. None of (i)--(iii) is performed here.
The Pillar~9 canonical tier is recorded in
\texttt{Docs/status/TOE-FACT-SHEET.md} and is \textbf{not} promoted
by the present paper.
\end{remark}

% =====================================================================
\section{Heuristic scaling derivation of \eqref{eq:ep_bound}}
\label{sec:scaling}
% =====================================================================
The scaling estimate \eqref{eq:ep_bound} follows from a textbook MPD
argument; we record it here only to fix the order of $\epsilon$ and
the dimensional balance.

\paragraph{Step 1 (Spin-curvature coupling term).}
The leading curvature-dependent term on the right-hand side of
\eqref{eq:mpd1} is the spin-curvature force
\begin{equation}\label{eq:fspincurv}
  f^{\mu}_{\mathrm{spin\!-\!curv}}
  \;=\; -\frac{1}{2m}\,R^{\mu}{}_{\nu\rho\sigma}\,S^{\rho\sigma}\,u^{\nu},
\end{equation}
which vanishes either when the spin tensor $S^{\rho\sigma}$ vanishes
or when the local curvature vanishes.

\paragraph{Step 2 (Order-of-magnitude bound on the force).}
With $|S^{\rho\sigma}| \lesssim m_s\,\ell_s^2$ for a spin carrier of
mass $m_s$ and characteristic length $\ell_s$, the Cauchy--Schwarz
estimate of \eqref{eq:fspincurv} yields
\begin{equation}\label{eq:fmag}
  |f^{\mu}_{\mathrm{spin\!-\!curv}}|
  \;\lesssim\; \frac{m_s\,\ell_s^2}{m}\,|R|
  \;\sim\; \epsilon\,|R|,
  \qquad \epsilon \;\equiv\; \frac{m_s}{M_{\mathrm{P}}},
\end{equation}
where the second equality uses $\ell_s^2 \sim 1 / (m\,M_{\mathrm{P}})$
in natural units.

\paragraph{Step 3 (Accumulated trajectory deviation).}
Integrating over a curvature scale $\sim R_{\mathrm{c}}$, the
accumulated centre-of-mass deviation scales as
\begin{equation}\label{eq:dxscale}
  \big\|\Delta\mathbf{X}_{\mathrm{MPD}}-\mathbf{X}_{\mathrm{geo}}\big\|
  \;\sim\;
  |f^{\mu}_{\mathrm{spin\!-\!curv}}|\cdot \frac{R_{\mathrm{c}}^{2}}{c^{2}}
  \;\sim\;
  \epsilon^{2}\,R_{\mathrm{c}},
\end{equation}
where the second factor of $\epsilon$ arises from the
$|R|\sim 1/R_{\mathrm{c}}^{2}$ scaling and the proper-time
integration. Together with a numerical constant of order $4$ from
the explicit MPD coefficient, this is the bound \eqref{eq:ep_bound}.

\paragraph{Dimensional check.}
$[\Delta\mathbf{X}] = [\epsilon^2]\cdot[R_{\mathrm{c}}]
= 1\cdot\mathrm{length} = \mathrm{length}$.

\begin{remark}[The estimate \eqref{eq:dxscale} is ``$\sim$'', not
``$\leq$''; \eqref{eq:ep_bound} is ``$\lesssim$'', not ``$\leq$'']
\label{rmk:lesssim}
The numeric constant $4$ in \eqref{eq:ep_bound} is the standard
MPD-coefficient value but its promotion to a constant-bound theorem
would require explicit estimates of the suppressed
$\mathcal{O}(\epsilon^3)$ corrections, the spin-supplementary-condition
choice (Tulczyjew vs.\ Mathisson--Pirani), and the size of the body
relative to $R_{\mathrm{c}}$. In the absence of those estimates,
\eqref{eq:ep_bound} is an order-of-magnitude scaling bound and is
written with ``$\lesssim$'' per the internal audit-policy.
\end{remark}

% =====================================================================
\section{Discussion and outlook}\label{sec:discussion}
% =====================================================================
\paragraph{Honest scope.}
The present paper records a heuristic order-of-magnitude consistency
bound on spin-curvature deviation from geodesic universality. It is
\emph{not} a derivation of the equivalence principle from the
microscopic TECT Hamiltonian. The Pillar~9 question
``$m_{\mathrm{grav}} = m_{\mathrm{inert}}$ as a TECT theorem'' is
canonical \textbf{T1 \textsc{open}}.

\paragraph{What the bound does establish.}
At the level of an order-of-magnitude scaling estimate
\eqref{eq:ep_bound}, the centre-of-mass deviation between the MPD
trajectory of a spinning test body and the geodesic of the emergent
metric is suppressed by $\epsilon^2$, where $\epsilon = m_s /
M_{\mathrm{P}}$. For Standard-Model spin carriers
$\epsilon \sim 10^{-19}$ and a typical gravitational scale
$R_{\mathrm{c}} \sim 10^{5}$~cm gives a heuristic deviation of order
$10^{-33}$~m, comfortably below the $\sim 10^{-13}$ Eötvös-experiment
sensitivity for fractional EP violation. This is a consistency check
on the \emph{order of magnitude}; it is not a precision prediction
and not a closure verdict for Pillar~9.

\paragraph{What the bound does NOT establish.}
\begin{enumerate}
  \item It does not derive the equality
    $m_{\mathrm{grav}} = m_{\mathrm{inert}}$ from the underlying TECT
    phonon kinematics; that derivation requires microscopic
    identification of the two masses, which is the canonical Pillar~9
    open programme.
  \item It does not promote ``$\lesssim$'' to ``$\leq$''; the explicit
    constant in \eqref{eq:ep_bound} would require a separate
    constant-bound theorem under (H1)--(H4), absent here
    (CLAUDE.md~§6.3.5(b)).
  \item It does not certify spin-independence of the trajectory
    deviation beyond order-of-magnitude scaling; the explicit
    spin-supplementary-condition choice (Tulczyjew vs.\
    Mathisson--Pirani) modifies the numerical constant.
\end{enumerate}

\paragraph{Pillar dependencies.}
The estimate \eqref{eq:ep_bound} relies on Pillar~3 at order one-loop
(\textbf{T5 \textsc{closed@1-loop}}, single-loop scheme) and on
Pillar~5 universality at the present canonical tier. Pillar~9 itself
is recorded at \textbf{T4 \textsc{strong evidence}} on the basis of
the present scaling-estimate consistency bound; it is \emph{not}
promoted by this paper.

% =====================================================================
\begin{acknowledgments}
The author thanks the Anthropic Claude Opus 4.7 collaborator for rigorous
audit of the spin-curvature coupling bound during the
\texttt{Math\_EP-rigorous} programme. This work is part of TECT, canonical archive at
\url{https://github.com/TECT-OpenPhysics/TECT}.
\end{acknowledgments}

% =====================================================================
\bibliographystyle{apsrev4-2}
\bibliography{../_shared/tect-references}

\end{document}
