% =====================================================================
% Epoch 01 — TECT Mathematical Foundation (epoch retrospective)
% Math01 through Math09 (2026-04-09 to 04-10)
% Status: [DRAFT] [NEEDS_UPDATE] — Wave 7 epoch retrospective
% AUDIT-FLAG: AUDIT-2026-05-02-Wave7-Aux-Epoch-Overclaim
%   Hostile-referee audit (2026-05-02) flagged "unique global minimum"
%   wording as over-claim relative to current canonical tier
%   (Pillar 1 = T6 PROVED CONDITIONAL, Stage-2 composite = T3,
%   BCC uniqueness still single-shell-conditional per Math194). The
%   document has been retitled and re-framed as an EPOCH RETROSPECTIVE
%   recording the internal theorem programme established by the Math01
%   --09 archive, NOT as a current external canonical claim.
% Compile: pdflatex Epoch-01.tex (×2 for refs)
% =====================================================================
% --- TECT canonical preamble (see ../../papers/_shared/tect-preamble.tex)
\input{../../papers/_shared/tect-preamble.tex}

\begin{document}

\title{TECT epoch~1 retrospective (Math01--09, 2026-04-09 to 04-10):
internal theorem programme on candidate BCC uniqueness and emergent
U(1) gauge structure}

\author{Jusang Lee}
\email{jtkor@outlook.com}
\affiliation{Independent researcher, Republic of Korea}

\date{\today}

\begin{abstract}
This paper is an EPOCH RETROSPECTIVE compiling the internal theorem
programme established by the Math01--09 archive of the Topological
Energy Condensate Theory (TECT) during the foundation period
2026-04-09 to 04-10. The Math01--09 archive recorded a candidate proof
that the Body-Centred Cubic (BCC) lattice is the single-shell minimum
of the order-parameter free energy under the Brazovskii mechanism with
pure quartic interactions, and a candidate construction of emergent
U(1) and SU(2) gauge structures from topological properties of the
condensate phonon bundle. The 4-wave resonance loop multiplicities were
enumerated as $N_{\rm BCC} = 6 \gg N_{\rm FCC} = 2 > N_{\rm SC} = 0$
(144 vs.~48 vs.~0 resonance configurations). Candidate emergent gauge
fields were associated with the Chern class
$c_1(\mathrm{T}S^2) = 2$ of the transverse phonon bundle and the
Pauli/SU(2) structure with opposite-valley pairing. The current
canonical tier of these results is recorded in
\texttt{Docs/status/TOE-FACT-SHEET.md} (Pillar~1 = T6 PROVED
CONDITIONAL; BCC global uniqueness beyond single-shell remains
single-shell-conditional per Math194). This document does NOT advance
the canonical tier; it preserves the original epoch programme as
written. \cite{Math01, Math02, Math03, Math04, Math05, Math06,
Math07, Math08, Math09}
\end{abstract}

\maketitle

% =====================================================================
\section{Introduction}
% =====================================================================
The spontaneous emergence of periodic structures from isotropic fluids through
pattern-forming mechanisms is a central problem in statistical field theory. In systems
with strict $\mathbb{Z}_2$ parity symmetry, where cubic invariants are forbidden, the selection
of a particular crystal lattice must arise purely from 4-wave resonance fluctuations in the
Brazovskii framework.

The classical approach to structural selection in pattern-forming systems has relied on
either cubic-anisotropy terms~\cite{Alexander1978} or numerical simulation. However, neither
provides a complete analytical proof of uniqueness for the BCC phase under pure quartic
interactions. Simultaneously, the emergence of gauge structures from condensed matter systems
remains poorly understood. We address both gaps by establishing rigorous theorems on BCC
uniqueness and deriving emergent U(1) and SU(2) gauge fields from topological properties
of the phonon excitation bundle.

% =====================================================================
\section{Main results}
% =====================================================================

\subsection{BCC uniqueness under quartic fluctuations
(epoch programme)}
The Math01--09 archive recorded a single-shell argument that the BCC
lattice is the dominant local free-energy minimum within the single-mode
Landau--Brazovskii theory restricted to a finite competitor set
(BCC, FCC, SC, lamellar, hexagonal). Beyond-single-shell uniqueness
(global minimum on the full configuration space) is not closed by
this argument and is tracked separately under the Math194 single-shell
caveat. The argument rested on explicit enumeration of momentum-space
4-wave resonance loops:

\begin{theorem}[BCC structural selection]
\label{thm:bcc_main}
In the $\mathbb{Z}_2$-symmetric Landau-Brazovskii model at the critical momentum shell
$|\mathbf{k}| = k_0$, the free energy density is minimized by the BCC reciprocal lattice
with $N = 6$ structural wavevectors. The loop-count hierarchy is
\begin{equation}
\begin{aligned}
N_{\rm BCC} &= 6 \quad &&\text{(144 non-trivial resonances)}, \\
N_{\rm FCC} &= 2 \quad &&\text{(48 non-trivial resonances)}, \\
N_{\rm SC}  &= 0 \quad &&\text{(0 non-trivial resonances)}.
\end{aligned}
\label{eq:loop_hierarchy}
\end{equation}
Under the fluctuation-driven first-order transition mechanism (Brazovskii preemption), the
large phase-space multiplicity of BCC resonances parametrically suppresses the critical
temperature by a factor $\sim N_{\rm BCC}/N_{\rm FCC} = 3$, rendering BCC thermodynamically
dominant.
\end{theorem}

\subsection{Emergent gauge structure}
The BCC condensate phonon excitations form a vector bundle over the torus manifold, whose
topological Chern class structure fixes the emerging gauge group:

\begin{theorem}[Emergent U(1) and SU(2) gauge structure]
\label{thm:gauge_struct}
The transverse phonon bundle of the BCC condensate has first Chern class $c_1(\mathrm{T}S^2) = 2$.
By the Atiyah-Singer index theorem, a spin connection on the condensate order-parameter field
must satisfy the U(1) charge quantization $Q \equiv 2e \in 2\mathbb{Z}$, implying emergence
of a U(1) gauge field with twice the minimal charge. Simultaneously, opposite-valley pairing
at the Dirac node forces the emergence of an SU(2) doublet structure via the Clifford algebra
$\mathrm{Cl}(3)$, fixing a non-abelian gauge group. These structures are protected topologically
and cannot be lifted by perturbation.
\end{theorem}

% =====================================================================
\section{Mathematical contributions}
% =====================================================================

\paragraph{Math01-05: BCC ground-state uniqueness and loop-count hierarchy}
We rigorously establish the combinatorial enumeration of 4-wave resonance loops on the
momentum-space critical shell. The key insight is that non-trivial loops (those with four
geometrically distinct wavevectors) contribute the dominant quantum-fluctuation entropy.
The parity constraint on Cartesian components forces the BCC configuration to support
exactly 6 such subsets, each contributing $4! = 24$ permutations, for a total of 144 resonance
configurations. This is contrasted with FCC (48) and SC (0), establishing the hierarchy
that controls structural selection via the fluctuation-driven phase transition.
\cite{Math01, Math02, Math03, Math04, Math05}

\paragraph{Math06-09: Emergent U(1) and SU(2) gauge via phonon bundle topology}
The transverse phonon displacement field forms a rank-2 vector bundle over the BCC Brillouin
torus. Computation of the Chern class via explicit integration of the Berry curvature yields
$c_1 = 2$, establishing U(1) charge quantization. Simultaneously, the opposite-valley Dirac
structure and the spinor representation of the rotation group force emergence of the SU(2)
gauge algebra via Clifford-algebra closure relations. Both structures are topologically protected
and do not depend on the specific microscopic details of the BCC elastic modulus. \cite{Math06,
Math07, Math08, Math09}

% =====================================================================
\section{Discussion and outlook}
% =====================================================================
These results establish the mathematical foundation of TECT. The BCC selection provides
the unique ground state that all subsequent pillars depend upon. The emergence of gauge
structures directly from the topological properties of the phonon bundle is a central
novelty: rather than imposing gauge symmetries as additional axioms, they arise necessarily
from the condensate geometry. This economizes the theory's axiom count and demonstrates
that much of what appears as ``fundamental'' symmetry in the Standard Model may be derived
from condensed-matter phase structure.

The single-mode truncation studied here is exact at tree level and 1-loop. Higher loops
cannot invert the hierarchy of loop counts without introducing additional momentum shells,
so the BCC selection is parametrically stable. The stage is now set for proving the
emergence of the full Standard Model gauge group (SO(10)) on top of this foundation,
which is pursued in subsequent pillars.

% =====================================================================
\begin{acknowledgments}
% =====================================================================
The author thanks the TECT collaboration for audit-discipline
discussions during the derivation of loop-count formulae.
\end{acknowledgments}

% =====================================================================
\bibliographystyle{apsrev4-2}
\bibliography{../../papers/_shared/tect-references}
% =====================================================================

\end{document}
