% =====================================================================
% Paper TI-1 — Spin-c Dirac index on CP^2: corrected rank-dependent formula
% Status: [DRAFT] [NEEDS_UPDATE] [REPAIRED] — Wave 2 top-impact
%   2026-05-02: REPAIRED in place. Prior version contained three
%   mutually inconsistent claims merged into one theorem (general
%   rank-r calculation, rank-1 line-bundle context, rank-16 fermion
%   specialization) and an arithmetic error in Step 3 of the proof
%   sketch. The corrected file is restructured into three separate
%   statements:
%     (i) Main theorem:    ind(D_E^c) = r - mu  (general rank r,
%                          c_1(E)=0, c_2(E) = mu H^2)
%     (ii) Corollary:      r=16 implies  ind = 16 - mu
%     (iii) Separate remark on the Picard classification
%                          Pic(CP^2) ~= Z (no hidden moduli) for
%                          U(1)_chi line bundles, NOT mixed with
%                          the index formula above.
% AUDIT-FLAG: AUDIT-2026-05-02-Wave7-Aux-Epoch-Overclaim (Math314-AddB
%   extension covering the four Top-impact TI-1..4 papers).
% Compile: pdflatex Paper-TI-1.tex (×2 for refs)
% Canonical archive: Math171-AddA, Math314-AddB
% =====================================================================
% --- TECT canonical preamble (see ../../papers/_shared/tect-preamble.tex)
\input{../../papers/_shared/tect-preamble.tex}

\begin{document}

\title{The spin-c Dirac index on $\mathbb{CP}^2$: a corrected rank-dependent
formula and the Picard classification of holomorphic line bundles}

\author{Jusang Lee}
\email{jtkor@outlook.com}
\affiliation{Independent researcher, Republic of Korea}

\date{\today}

\begin{abstract}
We correct a degree-arithmetic error in an earlier internal computation
(Math171 \S3.3) of the spin-c Dirac index on the complex projective surface
$\mathbb{CP}^2$. For a rank-$r$ holomorphic vector bundle $E$ with
$c_1(E) = 0$ and $c_2(E) = \mu H^2$ (where $H \in H^2(\mathbb{CP}^2,
\mathbb{Z})$ is the hyperplane class), the Hirzebruch--Riemann--Roch /
spin-c Dirac index is
\[
\mathrm{ind}(D_E^c) \;=\; r - \mu,
\]
which evaluates to $16 - \mu$ in the rank-$16$ specialisation relevant to
the SO(10) Standard-Model fermion sector. The general formula and its
rank-$16$ specialisation are stated as a main theorem and an explicit
corollary, respectively, to avoid conflating the two. Separately, we
collect the standard fact $\mathrm{Pic}(\mathbb{CP}^2) \cong \mathbb{Z}$
as a remark on the discrete classification of holomorphic line bundles;
this remark applies to the U$(1)_\chi$ line-bundle classification on a
$\mathbb{CP}^2$-type base and is NOT to be conflated with the rank-$16$
index formula above. The current canonical TECT realisation programme
operates on the base $\Sigma_0 = \mathbb{P}^1 \times \mathbb{P}^1$ per
Math305; the present results therefore form a foundational
algebro-geometric background note rather than a direct closure of any
present-canonical Pillar~4 sub-task.
\end{abstract}

\maketitle

% =====================================================================
\section{Introduction and scope}
% =====================================================================

The Atiyah--Singer index theorem is one of the central tools of modern
differential geometry and mathematical physics. Its spin-c variant
extends the Dirac index formula to non-spin manifolds by twisting with
a determinant line bundle. On $\mathbb{CP}^2$, a complex projective
surface of central importance in algebraic geometry and gauge theory,
the application of this formula requires careful attention to the
degree-parity decomposition.

In an earlier internal computation (Math171 \S3.3) the author wrote a
formula of the form $\mathrm{ind}(D_E^c) = 16 - \mu$ for a holomorphic
bundle $E$ with $c_1(E) = 0$ and $c_2(E) = \mu H^2$. The present note
clarifies that the correct general formula is rank-dependent, namely
$\mathrm{ind}(D_E^c) = r - \mu$, and that the formula
$16 - \mu$ is the specialisation to rank $r = 16$ (the rank relevant to
the SO(10) chiral fermion sector targeted by the TECT Pillar~4
programme). We separate the index formula from the Picard
classification of holomorphic line bundles to prevent the rank-$1$ and
rank-$16$ contexts from being conflated.

The present note is a \emph{background mathematical correction} rather
than a TECT closure paper. The current canonical Pillar~4 realisation
programme uses the base $\Sigma_0 = \mathbb{P}^1 \times \mathbb{P}^1$
per Math305, so the $\mathbb{CP}^2$ index formula derived here is
applicable to earlier $\mathbb{CP}^2$-based versions of the Pillar~4
bundle programme but does not by itself close the current
$\Sigma_0$-based realisation chain.

% =====================================================================
\section{Setting}
% =====================================================================

\subsection{Complex manifolds and spin-c structures}

Recall $\mathbb{CP}^2 = (\mathbb{C}^3 \setminus \{0\}) / \mathbb{C}^*$,
a smooth real 4-manifold and a complex 2-manifold. Its tangent bundle
$T\mathbb{CP}^2$ is a holomorphic vector bundle with first Chern class
$c_1(T\mathbb{CP}^2) = 3H$, where $H$ is the hyperplane class in
$H^2(\mathbb{CP}^2, \mathbb{Z}) \cong \mathbb{Z}$.

The manifold $\mathbb{CP}^2$ is \emph{not} spin since
$w_2(T\mathbb{CP}^2) \neq 0$, but it admits a spin-c structure. The
\emph{canonical} spin-c structure has determinant line bundle $L_{\rm
can}$ with $c_1(L_{\rm can}) = c_1(T\mathbb{CP}^2) = 3H$. Throughout
this note we use the canonical spin-c structure.

\subsection{Notation for bundles}

We consider a holomorphic vector bundle $E$ on $\mathbb{CP}^2$ of rank
$r$, with first Chern class $c_1(E) = 0$ and second Chern class
$c_2(E) = \mu H^2$ for an integer $\mu$. The Chern character is
\[
\mathrm{ch}(E) \;=\; r + c_1(E) + \tfrac{1}{2}(c_1(E)^2 - 2 c_2(E)) + \cdots
\;=\; r - \mu H^2 \pmod{H^4 \text{ vanishes on }\mathbb{CP}^2},
\]
where the $c_1(E)$ and $c_1(E)^2$ terms vanish under the
$c_1(E) = 0$ hypothesis.

% =====================================================================
\section{Main theorem (general rank $r$)}
% =====================================================================

\begin{theorem}[Spin-c Dirac index on $\mathbb{CP}^2$, general rank]
\label{thm:main}
Let $E$ be a holomorphic vector bundle on $\mathbb{CP}^2$ with
$\mathrm{rk}(E) = r$, $c_1(E) = 0$, and $c_2(E) = \mu H^2$ for some
integer $\mu \in \mathbb{Z}$ (where $H$ is the hyperplane class
generating $H^2(\mathbb{CP}^2,\mathbb{Z}) \cong \mathbb{Z}$ and the
intersection $H^2 \in H^4(\mathbb{CP}^2,\mathbb{Z}) \cong \mathbb{Z}$
satisfies $\int_{\mathbb{CP}^2} H^2 = 1$). Let
$D_E^c$ denote the spin-c Dirac operator on $\mathbb{CP}^2$ coupled to
$E$ with the canonical spin-c structure $c_1(L_{\rm can}) = 3H$. Then
\[
\boxed{\;\mathrm{ind}(D_E^c) \;=\; r - \mu \;\in\; \mathbb{Z}.\;}
\]
\end{theorem}

\begin{proof}[Proof]
By the Atiyah--Singer index theorem in spin-c form, on a complex
manifold of complex dimension 2 with the canonical spin-c structure,
the index reduces to the Hirzebruch--Riemann--Roch holomorphic Euler
characteristic:
\[
\mathrm{ind}(D_E^c) \;=\; \chi(\mathbb{CP}^2, E) \;=\;
\int_{\mathbb{CP}^2} \mathrm{td}(T\mathbb{CP}^2) \wedge \mathrm{ch}(E).
\]
The Todd class of $T\mathbb{CP}^2$ is
\[
\mathrm{td}(T\mathbb{CP}^2) \;=\; 1 \;+\; \tfrac{3}{2} H \;+\; H^2.
\]
The Chern character of $E$, under the hypotheses $c_1(E) = 0$ and
$c_2(E) = \mu H^2$, has degree-graded components
\[
[\mathrm{ch}(E)]_{(0)} = r, \qquad [\mathrm{ch}(E)]_{(2)} = 0, \qquad
[\mathrm{ch}(E)]_{(4)} = - \mu H^2.
\]
The degree-$4$ component of the wedge product
$\mathrm{td}(T\mathbb{CP}^2) \wedge \mathrm{ch}(E)$ is
\begin{align*}
[\mathrm{td} \wedge \mathrm{ch}]_{(4)} &=
[\mathrm{td}]_{(4)} \cdot [\mathrm{ch}]_{(0)} +
[\mathrm{td}]_{(2)} \cdot [\mathrm{ch}]_{(2)} +
[\mathrm{td}]_{(0)} \cdot [\mathrm{ch}]_{(4)} \\
&= H^2 \cdot r + \tfrac{3}{2} H \cdot 0 + 1 \cdot (-\mu H^2) \\
&= (r - \mu)\, H^2.
\end{align*}
With $\int_{\mathbb{CP}^2} H^2 = 1$ this integrates to $r - \mu$.
\end{proof}

% =====================================================================
\section{Corollary: rank-$16$ specialisation}
% =====================================================================

\begin{corollary}[Rank-$16$ specialisation]
\label{cor:rank16}
For the rank-$16$ specialisation $r = 16$ relevant to the SO(10)
chiral-fermion sector of the TECT Pillar~4 programme,
\[
\mathrm{ind}(D_E^c) \;=\; 16 - \mu.
\]
\end{corollary}

The rank-$16$ specialisation reproduces the formula stated in the
earlier Math171 \S3.3 derivation; the present note clarifies that the
formula is rank-dependent and that the original ``$16 - \mu$'' wording
is the $r=16$ corollary, not a general theorem.

% =====================================================================
\section{Remark: Picard classification of holomorphic line bundles
on $\mathbb{CP}^2$ (separate from the index theorem)}
% =====================================================================

\begin{remark}[Picard classification, separate from Theorem~\ref{thm:main}]
\label{rem:picard}
Independently of Theorem~\ref{thm:main}, the Picard group of
$\mathbb{CP}^2$ is
\[
\mathrm{Pic}(\mathbb{CP}^2) \;\cong\; \mathbb{Z}, \qquad
\mathrm{Pic}^0(\mathbb{CP}^2) = 0.
\]
This follows from the standard exponential sequence and from
$H^1(\mathbb{CP}^2, \mathcal{O}) = 0$ (Kodaira vanishing on
$\mathbb{CP}^2$). Consequently, every holomorphic line bundle on
$\mathbb{CP}^2$ is uniquely determined by an integer first Chern class
$k \in \mathbb{Z}$, with no continuous moduli. If a TECT realisation is
formulated on a $\mathbb{CP}^2$-type base and the U$(1)_\chi$ sector is
represented by a holomorphic line bundle, that line bundle is
classified discretely by an integer first Chern class $k_\chi$ and has
no $\mathrm{Pic}^0$-modulus.
\end{remark}

The Picard classification (Remark~\ref{rem:picard}) and the spin-c index
formula (Theorem~\ref{thm:main}) are mathematically independent
statements. They concern different bundle ranks and different invariants;
this note keeps them separated to prevent the rank-$1$ Picard context
from being conflated with the rank-$r$ index calculation.

% =====================================================================
\section{Discussion}
% =====================================================================

The corrected rank-dependent formula $\mathrm{ind}(D_E^c) = r - \mu$
removes the degree-arithmetic ambiguity in the earlier Math171 \S3.3
derivation. The rank-$16$ specialisation $16 - \mu$ is preserved as
Corollary~\ref{cor:rank16}; the rank-$1$ specialisation $1 - \mu$
applies, e.g., to a hypothetical line-bundle context with $c_2 = \mu
H^2$ (note that for an honest holomorphic line bundle with $c_1 = 0$
the second Chern class $c_2$ vanishes, so the rank-$1$ specialisation
is non-trivial only for the abstract index calculation, not for an
honest line bundle in the geometric sense).

Per the current canonical TECT bookkeeping (Math305 plus Math302
proof-rigor / realisation carve-out), the canonical Pillar~4 base is
$\Sigma_0 = \mathbb{P}^1 \times \mathbb{P}^1$ rather than
$\mathbb{CP}^2$. The index formula on $\Sigma_0$ requires a separate
calculation (different Todd class) and is not derived here. The present
note therefore serves as a background algebro-geometric clarification
of the earlier $\mathbb{CP}^2$ programme rather than as a current
canonical-tier closure.

% =====================================================================
\begin{acknowledgments}
The author thanks the internal hostile-referee audit (2026-05-02;
archived as Math314-AddB
\texttt{AUDIT-2026-05-02-Wave7-Aux-Epoch-Overclaim} extension) for
catching the degree-arithmetic / rank-conflation defect in the
original draft.
\end{acknowledgments}

% =====================================================================
\bibliographystyle{apsrev4-2}
\bibliography{../../papers/_shared/tect-references}
% =====================================================================

\end{document}
